### 2018-11-17 report/SDBProject.tex
j
j

\documentclass[a4paper,oneside]{article}
\usepackage{indentfirst}
\usepackage[top=0.7in, bottom=0.7in, left = 0.7in, right = 0.7in]{geometry}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{indentfirst}
\usepackage{cite}
\usepackage{fontspec}

\title{Term Project\\Splitter: Mining Fine-Grained Sequential Patterns in Semantic Trajectories}
\author{Fawwaz Dzaky Zakiyal (201899213)\\Tanjung Dion (201883621)\\}
\date{Stream Database (Fall 2018)}

\begin{document}
	\maketitle

	\section{Introduction}
	Semantic trajectory is a sequence of timestamped places wherein each place has information about spatial location and a semantic label. By mining fine-grained pattern that satisfy semantic consistency (consistent place id in each category), spatial compactness (compact area for each category) and temporal continuity (limited time constraint), it will give benefit such as urban planning and targeted advertising. This process of mining fine-grained pattern have been proposed by Zang et. al \cite{splitter}. For the final project we will re-implement the process of find fine-grained pattern in Java programing language.

	\section{Problem}
	\begin{itemize}
		\item How to mine the coarse patterns and their snippets? 
		\item How to effectively cluster the snippets given the fact that we do not know the correct number of clusters?
	\end{itemize}

	\section{Proposed Method}
		 \subsection{Dataset}
		 This project will use the real dataset, 4SQ that collected from Foursquare check-in sequence in New York. It consists of 48564 places that divided into 417 place categories and it stored semantic trajectories from 14909 users. 4SQ dataset provides 3 files:
		 \begin{enumerate}
		 \item \textit{Sequences}, it contains users semantic trajectories including attributes of check-in timestamp and place ID.
		 \item \textit{Places}, it contains information about the places (place ID, latitude, longitude, category ID).
		 \item \textit{Category}, it contains information of place category ID corresponding with its place category name.
		 \end{enumerate}

		 \subsection{System Design}
		 	\begin{figure}[!ht]
		 	\centering
		 	\includegraphics[width=1\linewidth]{splitter}
		 	\caption{System Design}
		 	\label{fig:systemdesign}
		 \end{figure}
		 Figure \ref{fig:systemdesign} show the process of mining fine-grained pattern in semantic trajectories. This method consist of two part: mining coarse pattern and splitting coarse pattern. Mining coarse pattern is a process to find sequential pattern that satisfy semantic consistency and temporal continuity. In the first step, we add trajectory dataset that have information about place id, movement time, group id, and spatial location to the system. This trajectory dataset will be transformed into semantic trajectory dataset by grouping place id based on category. However, we still keep the original place id in each category to prevent one trajectory from being counted repeatedly. By doing this process, our trajectory dataset will satisfy semantic consistency.

		 Then, Prefixspan algorithm will be used to mining the coarse pattern. In the Prefixspan algorithm, we include all posfixes to avoid missing pattern under the given time constrain. Output from mining coarse pattern is set of coarse pattern that will be used in the next process. The next process is finding fine-grained pattern that satisfy spatial compactness in by splitting a coarse pattern in top down manner. Set of coarse pattern from previous process will be transformed into K-dimensional point x.

		 Then, we employ mean shift clustering to extract the dense and compact snippet cluster based on the support and variance threshold. To speed up the process, the unqualified snippet cluster will be organized into several disjoint communities. By only clustering each communities, we can gradually reduce the kernel windows in clustering method to speed up the clustering process.

		\subsection{Implementation}
		We will re-implement the process of mining fine-grained pattern using java programing language. The user interface of program will be provided as shown in the Figure \ref{fig:UI}. Figure \ref{fig:javagui} shows the illustration of our program. There are an dataset input in csv format, 4 parameters input,  show button for showing graph representation like in the figure \ref{fig:graph}, and 3 button to start the process individually or start all of the process respectively.

		\begin{figure}[!h]
			\centering
			\begin{subfigure}[b]{0.4\linewidth}
				\centering
				\includegraphics[width=1\linewidth]{GUI}
				\caption{Program UI illustration}
				\label{fig:javagui}
			\end{subfigure}
				\begin{subfigure}[b]{0.4\linewidth}
				\centering
				\includegraphics[width=0.7\linewidth]{GraphRepresentation}
				\caption{Graph illustration}
				\label{fig:graph}
			\end{subfigure}
			\caption{User Interface Ilustration}
			\label{fig:UI}
		\end{figure}

	\section{Testing and Evaluation}
	For the testing and evaluation, we will conduct an experiment of mining fine-grained pattern by varying support threshold, spatial variance threshold, time movement constraint, kernel windows size, and dampening factor in the term of coverage and pattern. Coverage is the total number of trajectory in all pattern that satisfy fine-grained pattern. 
\begin{thebibliography}{1}
	\bibitem{splitter} Zhang, C., Han, J., Shou, L., Lu, J., La Porta, T. (2014).{\em Splitter: Mining fine-grained sequential patterns in semantic trajectories}. Proceedings of the VLDB Endowment, 7(9), 769-780.
\end{thebibliography}
\end{document}

### 2018-11-17 splitter_tool/code/kdtree/KDTree.java

@@ -1,0 +1,523 @@
+package kdtree;
+
+import java.lang.reflect.Array;
+import java.util.ArrayDeque;
+import java.util.Arrays;
+import java.util.Comparator;
+import java.util.Deque;
+import java.util.Iterator;
+import java.util.List;
+
+import com.google.common.base.Strings;
+import com.google.common.collect.AbstractIterator;
+import com.google.common.collect.Lists;
+import com.google.common.primitives.Doubles;
+
+import meanshift.*;
+import meanshift.DoubleVector.DoubleVectorElement;
+
+/**
+ * Implementation of a kd-tree that handles dense vectors as well as sparse
+ * vectors. It offers O(log n) best case lookup time, but can degrade to O(n) if
+ * the tree isn't balanced well. It is mostly optimized for special cases like
+ * two or three dimensional data, but it does not offer removal of tree nodes
+ * (yet).
+ * 
+ * @author thomas.jungblut
+ * 
+ */
+public final class KDTree<VALUE> implements Iterable<DoubleVector> {
+
+  private KDTreeNode root;
+  private int size;
+
+  final class KDTreeNode {
+    final int splitDimension;
+    // keyvector by the value in the split dimension
+    final DoubleVector keyVector;
+    final VALUE value;
+
+    KDTreeNode left;
+    KDTreeNode right;
+
+    public KDTreeNode(int splitDimension, DoubleVector keyVector, VALUE val) {
+      this.splitDimension = splitDimension;
+      this.keyVector = keyVector;
+      this.value = val;
+    }
+
+    @Override
+    public String toString() {
+      return "KDTreeNode [splitDimension=" + splitDimension + ", value="
+          + keyVector + "]";
+    }
+  }
+
+  // descending sorted by distance, so the head of the prio queue is always
+  // largest
+  public static final class VectorDistanceTuple<VALUE> implements
+      Comparable<VectorDistanceTuple<VALUE>> {
+
+    final DoubleVector keyVector;
+    final VALUE value;
+    final double dist;
+
+    public VectorDistanceTuple(DoubleVector keyVector, VALUE value, double dist) {
+      this.keyVector = keyVector;
+      this.value = value;
+      this.dist = dist;
+    }
+
+    public double getDistance() {
+      return dist;
+    }
+
+    public DoubleVector getVector() {
+      return keyVector;
+    }
+
[…]

### 2018-11-17 splitter_tool/code/kdtree/LimitedPriorityQueue.java

@@ -1,0 +1,99 @@
+package kdtree;
+
+import java.util.ArrayList;
+import java.util.List;
+import java.util.PriorityQueue;
+
+/**
+ * A queue that has limited capacity. Once it hits the maximum defined capacity
+ * it will drop off the one with the most cost.
+ * 
+ * @author thomas.jungblut
+ */
+public final class LimitedPriorityQueue<T> {
+
+  static class Entry<T> implements Comparable<Entry<T>> {
+    final T data;
+    final double value;
+
+    public Entry(final T data, final double value) {
+      this.data = data;
+      this.value = value;
+    }
+
+    @Override
+    public int compareTo(Entry<T> t) {
+      return Double.compare(t.value, this.value);
+    }
+
+    @Override
+    public String toString() {
+      return data.toString();
+    }
+  };
+
+  private final PriorityQueue<Entry<T>> queue;
+  private final int maxCapacity;
+
+  public LimitedPriorityQueue(int capacity) {
+    maxCapacity = capacity;
+    queue = new PriorityQueue();
+  }
+
+  public double getMaximumPriority() {
+    Entry<T> p = queue.peek();
+    return (p == null) ? Double.POSITIVE_INFINITY : p.value;
+  }
+
+  public boolean add(T element, double cost) {
+    if (isFull()) {
+      if (cost > getMaximumPriority()) {
+        return false;
+      }
+      queue.add(new Entry(element, cost));
+      queue.poll();
+    } else {
+      queue.add(new Entry(element, cost));
+    }
+    return true;
+  }
+
+  public boolean isFull() {
+    return queue.size() >= maxCapacity;
+  }
+
+  public T peek() {
+    Entry<T> p = queue.peek();
+    return (p == null) ? null : p.data;
+  }
+
+  public boolean isEmpty() {
+    return queue.size() == 0;
+  }
+
+  public int size() {
+    return queue.size();
+  }
+
+  public PriorityQueue<Entry<T>> getQueue() {
+    return this.queue;
+  }
+
+  public T poll() {
+    Entry<T> p = queue.poll();
+    return (p == null) ? null : p.data;
+  }
+
+  public List<T> toList() {
+    List<T> list = new ArrayList<T>(size());
+    for (Entry<T> entry : queue) {
+      list.add(entry.data);
+    }
+    return list;
+  }
+
+  @Override
+  public String toString() {
+    return queue.toString();
+  }
+}

### 2018-11-17 splitter_tool/code/main/Assesser.java

@@ -1,0 +1,166 @@
+package main;
+
+import java.io.BufferedWriter;
+import java.io.FileWriter;
+import java.util.ArrayList;
+import java.util.List;
+
+import prefixspan.AlgoPrefixSpan;
+import prefixspan.SequenceDatabase;
+import split.Group;
+import split.GroupSequence;
+import split.Groups;
+import split.Places;
+import split.SnippetCluster;
+import split.Splitter;
+
+public class Assesser {
+	
+	SequenceDatabase mDatabase = null;
+	int mDataSize;
+	Places mPlaces = null;
+	Groups mGroups = null;
+
+	String groupFile;
+	String patternFile;
+	
+	//statistics
+	double timeSplitterCoarse = 0;
+	double timeSplitterFine = 0;
+
+	int coverageSplitter = 0;
+
+	int patternCountSplitter = 0;
+
+	double varianceSplitter = 0;
+
+	public Assesser(String groupFile, String patternFile) throws Exception {
+		this.groupFile = groupFile;
+		this.patternFile = patternFile;
+	}
+	
+	public void loadDatabase(String dataFile) throws Exception {
+		mDatabase = new SequenceDatabase();
+		mDatabase.loadFile(dataFile);
+		mDataSize = mDatabase.size(); //database size
+	}
+	
+	public void loadPlaces(String placeFile) throws Exception {
+		mPlaces = new Places();
+		mPlaces.loadFile(placeFile);
+	}
+	
+	public int getDataSize() {
+		return mDataSize;
+	}
+	
+	public void writeStats(String statFile) throws Exception {
+		BufferedWriter bw = new BufferedWriter(new FileWriter(statFile, true)); // append
+		bw.append( timeSplitterCoarse + " " + timeSplitterFine + " "
+				 	  + patternCountSplitter + " " + coverageSplitter + " "  + "\n");
+		bw.close();
+	}
+	
+	
+
+	/*
+	 * Evaluate Splitter.
+	 */
+	public void runSplitter(double minSup, int maxInterval, double varThreshold, double tau, double initialBandwidth) throws Exception {
+		initializeGroups(1); //split by category level 1
+		List<SnippetCluster> coarsePatterns = mineCoarsePatterns(minSup, maxInterval);
+		//writePatterns(coarsePatterns);
+		List<SnippetCluster> finePatterns = refinePattern(coarsePatterns, (int)(minSup * mDataSize), varThreshold, tau, initialBandwidth);
[…]

### 2018-11-17 splitter_tool/code/main/Config.java

@@ -1,0 +1,53 @@
+package main;
+
+import org.yaml.snakeyaml.Yaml;
+import org.yaml.snakeyaml.constructor.Constructor;
+import org.yaml.snakeyaml.constructor.AbstractConstruct;
+import org.yaml.snakeyaml.nodes.Node;
+import org.yaml.snakeyaml.nodes.SequenceNode;
+import org.yaml.snakeyaml.nodes.Tag;
+
+import java.io.File;
+import java.io.FileInputStream;
+import java.util.List;
+import java.util.Map;
+
+/**
+ * Created by chao on 9/12/15.
+ * This file is used to load parameters from a YAML file.
+ */
+public class Config {
+
+    class DiceConstructor extends Constructor {
+
+        public DiceConstructor() {
+            this.yamlConstructors.put(new Tag("!join"), new ConstructDice());
+        }
+
+        private class ConstructDice extends AbstractConstruct {
+            public Object construct(Node node) {
+                List val = (List) constructSequence((SequenceNode) node);
+                String ret = "";
+                for (int i=0; i < val.size(); i++) {
+                    ret += (String) val.get(i);
+                }
+                return ret;
+            }
+        }
+
+    }
+
+    public Map load(String paraFile) throws Exception {
+        Yaml yaml = new Yaml(new DiceConstructor());
+        return (Map) yaml.load(new FileInputStream(new File(paraFile)));
+    }
+
+    /** ---------------------------------- main ---------------------------------- **/
+    public static void main(String [] args) throws Exception {
+        String paraFile = "../run/nyc_sample.yaml";
+        Config config = new Config();
+        Map para = config.load(paraFile);
+        System.out.println(para);
+    }
+
+}

### 2018-11-17 splitter_tool/code/main/Main.java

@@ -1,0 +1,60 @@
+package main;
+
+import java.util.Map;
+
+public class Main {
+
+	public static void main(String[] args) throws Exception {
+        if (args.length > 0) {
+            runWithConfig(args[0]);
+		} else {
+			run();
+		}
+	}
+
+	public static void run() throws Exception {
+		// default parameters
+		String dataFile = "./data/sequences.txt";
+		String placeFile = "./data/places.csv";
+		String groupFile = "./data/groups.txt";
+		String patternFile = "./data/patterns.txt";
+		String statFile = "./data/stats.txt";
+        int minSup = 100;
+		double varThreshold = 0.0002;
+		double tau = 0.8;
+		int maxInterval = 120;
+		double initialBandwidth = 0.02;
+		// run
+		Assesser assesser = new Assesser(groupFile, patternFile);
+		assesser.loadDatabase(dataFile);
+		assesser.loadPlaces(placeFile);
+		double sup = (double) minSup / assesser.getDataSize();
+		assesser.runSplitter(sup, maxInterval, varThreshold, tau, initialBandwidth);
+		assesser.writeStats(statFile);
+	}
+
+	public static void runWithConfig(String configFile) throws Exception {
+		// load parameters
+		Map config = new Config().load(configFile);
+		String inputDir = (String) config.get("inputDir");
+		String outputDir = (String) config.get("outputDir");
+		String dataFile = inputDir + "sequences.txt";
+		String placeFile = inputDir + "places.csv";
+		String groupFile = outputDir + "groups.txt";
+		String patternFile = outputDir + "patterns.txt";
+		String statFile = outputDir + "stats.txt";
+		int minSup = (int) config.get("minSup");
+		double varThreshold = (Double) config.get("varThreshold");
+		int maxInterval = (Integer) config.get("maxInterval");
+		double tau = (Double) config.get("tau");
+		double initialBandwidth = (Double) config.get("bandwidth");
+        // run
+		Assesser assesser = new Assesser(groupFile, patternFile);
+		assesser.loadDatabase(dataFile);
+		assesser.loadPlaces(placeFile);
+		double sup = (double) minSup / assesser.getDataSize();
+		assesser.runSplitter(sup, maxInterval, varThreshold, tau, initialBandwidth);
+		assesser.writeStats(statFile);
+	}
+
+}

### 2018-11-17 splitter_tool/code/meanshift/DenseDoubleVector.java

@@ -1,0 +1,546 @@
+package meanshift;
+
+import java.util.Arrays;
+import java.util.Iterator;
+
+import org.apache.commons.math3.util.FastMath;
+
+import com.google.common.collect.AbstractIterator;
+
+/**
+ * Dense double vector implementation.
+ */
+public final class DenseDoubleVector implements DoubleVector {
+
+  private final double[] vector;
+
+  /**
+   * Creates a new vector with the given length.
+   */
+  public DenseDoubleVector(int length) {
+    this.vector = new double[length];
+  }
+
+  /**
+   * Creates a new vector with the given length and default value.
+   * 
+   * @param length the length of the new vector.
+   * @param the value of all the vector elements.
+   */
+  public DenseDoubleVector(int length, double val) {
+    this(length);
+    Arrays.fill(vector, val);
+  }
+
+  /**
+   * Creates a new vector with the given array. This wraps a copy of the given
+   * array.
+   */
+  public DenseDoubleVector(double[] arr) {
+    this.vector = new double[arr.length];
+    System.arraycopy(arr, 0, this.vector, 0, arr.length);
+  }
+
+  /**
+   * Creates a new vector with the given array and the last value 'lastValue'.
+   * This resulting vector will be of size array.length+1.
+   * 
+   * @param array the first part of the vector.
+   * @param lastValue the element that will be at index length-1 (last position)
+   *          in the resulting vector.
+   */
+  public DenseDoubleVector(double[] array, double lastValue) {
+    this.vector = new double[array.length + 1];
+    System.arraycopy(array, 0, this.vector, 0, array.length);
+    this.vector[array.length] = lastValue;
+  }
+
+  /**
+   * Creates a new vector with the given array and the first value firstElement.
+   * 
+   * @param firstElement the element that will be at index 0 (first position) in
+   *          the resulting vector.
+   * @param array the rest of the array for the vector.
+   */
+  public DenseDoubleVector(double firstElement, double[] array) {
+    this.vector = new double[array.length + 1];
+    this.vector[0] = firstElement;
+    System.arraycopy(array, 0, this.vector, 1, array.length);
+  }
+
+  /**
[…]

### 2018-11-17 splitter_tool/code/meanshift/DistanceMeasurer.java

@@ -1,0 +1,9 @@
+package meanshift;
+
+public interface DistanceMeasurer {
+
+  public double measureDistance(double[] set1, double[] set2);
+
+  public double measureDistance(DoubleVector vec1, DoubleVector vec2);
+
+}

### 2018-11-17 splitter_tool/code/meanshift/DoubleDoubleVectorFunction.java

@@ -1,0 +1,16 @@
+package meanshift;
+
+/**
+ * A function that can be applied to two double vectors via {@link DoubleVector}
+ * #apply({@link DoubleVector} v, {@link DoubleDoubleVectorFunction} f);
+ * 
+ */
+public interface DoubleDoubleVectorFunction {
+
+  /**
+   * Calculates the result of the left and right value of two vectors at a given
+   * index.
+   */
+  public double calculate(int index, double left, double right);
+
+}

### 2018-11-17 splitter_tool/code/meanshift/DoubleVector.java

@@ -1,0 +1,333 @@
+package meanshift;
+
+import java.util.Iterator;
+
+/**
+ * Vector with doubles. Some of the operations are mutable, unlike the apply and
+ * math functions, they return a fresh instance every time.
+ * 
+ */
+public interface DoubleVector {
+
+  /**
+   * Retrieves the value at given index.
+   * 
+   * @param index the index.
+   * @return a double value at the index.
+   */
+  public double get(int index);
+
+  /**
+   * Get the length of a vector, for sparse instance it is the actual length.
+   * (not the dimension!) Always a constant time operation.
+   * 
+   * @return the length of the vector.
+   */
+  public int getLength();
+
+  /**
+   * Get the dimension of a vector, for dense instance it is the same like the
+   * length, for sparse instances it is usually not the same. Always a constant
+   * time operation.
+   * 
+   * @return the dimension of the vector.
+   */
+  public int getDimension();
+
+  /**
+   * Set a value at the given index.
+   * 
+   * @param index the index of the vector to set.
+   * @param value the value at the index of the vector to set.
+   */
+  public void set(int index, double value);
+
+  /**
+   * Apply a given {@link DoubleVectorFunction} to this vector and return a new
+   * one.
+   * 
+   * @param func the function to apply.
+   * @return a new vector with the applied function.
+   */
+  public DoubleVector apply(DoubleVectorFunction func);
+
+  /**
+   * Apply a given {@link DoubleDoubleVectorFunction} to this vector and the
+   * other given vector. Both vectors must match in dimensions.
+   * 
+   * @param other the other vector.
+   * @param func the function to apply on this and the other vector.
+   * @return a new vector with the result of the function of the two vectors.
+   */
+  public DoubleVector apply(DoubleVector other, DoubleDoubleVectorFunction func);
+
+  /**
+   * Adds the given {@link DoubleVector} to this vector.
+   * 
+   * @param v the other vector.
+   * @return a new vector with the sum of both vectors at each element index.
+   */
+  public DoubleVector add(DoubleVector v);
+
+  /**
+   * Adds the given scalar to this vector.
+   * 
+   * @param scalar the scalar.
+   * @return a new vector with the result at each element index.
+   */
+  public DoubleVector add(double scalar);
+
+  /**
+   * Subtracts this vector by the given {@link DoubleVector}.
+   * 
+   * @param v the other vector.
+   * @return a new vector with the difference of both vectors.
+   */
[…]

### 2018-11-17 splitter_tool/code/meanshift/DoubleVectorFunction.java

@@ -1,0 +1,14 @@
+package meanshift;
+
+/**
+ * A function that can be applied to a double vector via {@link DoubleVector}
+ * #apply({@link DoubleVectorFunction} f);
+ */
+public interface DoubleVectorFunction {
+
+  /**
+   * Calculates the result with a given index and value of a vector.
+   */
+  public double calculate(int index, double value);
+
+}

### 2018-11-17 splitter_tool/code/meanshift/EuclidianDistance.java

@@ -1,0 +1,40 @@
+package meanshift;
+
+import org.apache.commons.math3.util.FastMath;
+
+public final class EuclidianDistance implements DistanceMeasurer {
+
+  private static final EuclidianDistance DISTANCE = new EuclidianDistance();
+
+  @Override
+  public double measureDistance(double[] set1, double[] set2) {
+    double sum = 0;
+    int length = set1.length;
+    for (int i = 0; i < length; i++) {
+      double diff = set2[i] - set1[i];
+      // multiplication is faster than Math.pow() for ^2.
+      sum += (diff * diff);
+    }
+
+    return FastMath.sqrt(sum);
+  }
+
+  @Override
+  public double measureDistance(DoubleVector vec1, DoubleVector vec2) {
+    if (vec1.isSparse() || vec2.isSparse()) {
+      return FastMath.sqrt(vec2.subtract(vec1).pow(2).sum());
+    } else {
+      // dense vectors usually doesn't do a defensive copy, so it is faster than
+      // the implementation above.
+      return measureDistance(vec1.toArray(), vec2.toArray());
+    }
+  }
+
+  /**
+   * @return a cached euclidian distance measurer.
+   */
+  public static EuclidianDistance get() {
+    return DISTANCE;
+  }
+
+}

### 2018-11-17 splitter_tool/code/meanshift/MeanShift.java

@@ -1,0 +1,204 @@
+package meanshift;
+
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
+
+import org.apache.commons.math3.util.FastMath;
+
+public class MeanShift {
+
+	private final double SQRT_2_PI = FastMath.sqrt(2 * Math.PI);
+
+	int maxIteration = 100;
+	double bandwidth = 0.01;
+	double mergeWindow = 0.001;
+	List<Integer> weights = null; // weights of points
+	List<DoubleVector> points = null; 
+	List<DoubleVector> centers = null;
+	boolean[] converged = null;
+	int[] designation = null;
+
+	public List<DoubleVector> cluster(List<DoubleVector> points, List<Integer> weights,
+			double bandwidth, double mergeWindow, int maxIterations) {
+
+		initialize(points, weights, maxIterations, bandwidth, mergeWindow);
+
+		// now iterate over all centers
+		for (int i = 0; i < maxIterations; i++) {
+			// return the number of centers that have not converged yet
+			int remainingConvergence = meanShift();
+			// merge if centers are within the mergeWindow
+
+			if (remainingConvergence == 0) {
+				break;
+			}
+		}
+		assign();
+		return centers;
+	}
+	
+	//get clusters from designation
+	public Map<Integer, List<Integer>> getClusters() {
+		Map<Integer, List<Integer>> clusters = new HashMap<Integer, List<Integer>>(); 
+		//key:cluster id, value:list of members
+		for(int i=0; i<designation.length; i++) {
+			int clusterID = designation[i];
+			if ( clusters.containsKey(clusterID) ) {
+				clusters.get( clusterID ).add(i);
+			} else {
+				List<Integer> newCluster = new ArrayList<Integer>();
+				newCluster.add( i );
+				clusters.put( clusterID, newCluster );
+			}
+		}
+		return clusters;
+	}
+	
+	public int[] getDesignation() {
+		return designation;
+	}
+	
+	
+	/*
+	 * 
+	 * */
+	private void initialize(List<DoubleVector> points, List<Integer> weights, int maxIteration,
+			double bandwidth, double mergeWindow) {
+
+		this.maxIteration = maxIteration;
+		this.bandwidth = bandwidth;
+		this.mergeWindow = mergeWindow;
+
+		this.points = points;
+		this.weights = weights;
+		findInitialCenters();
+
[…]

### 2018-11-17 splitter_tool/code/meanshift/MeanShiftClustering.java

@@ -1,0 +1,196 @@
+package meanshift;
+
+import java.util.ArrayList;
+import java.util.BitSet;
+import java.util.List;
+
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
+import org.apache.commons.math3.util.FastMath;
+
+import kdtree.KDTree;
+import kdtree.KDTree.VectorDistanceTuple;
+
+/**
+ * Sequential Mean Shift Clustering using a gaussian kernel and euclidian
+ * distance measurement.
+ * 
+ * @author thomasjungblut
+ * 
+ */
+public final class MeanShiftClustering {
+
+  private static final Log LOG = LogFactory.getLog(MeanShiftClustering.class);
+
+  private static final double SQRT_2_PI = FastMath.sqrt(2 * Math.PI);
+
+  /**
+   * Clusters a bunch of given points using the Mean Shift algorithm. It first
+   * observes possible centers that are within the given windowSize. Once we
+   * have initial centers found, we do a meanshift step and afterwards merge
+   * centers that are within the mergeWindow of each other. This algorithm is
+   * guranteed to converge to a minimum solution.
+   * 
+   * @param points the points to cluster.
+   * @param windowSize the window size to observe points arround the center in.
+   *          This is also used to observe initial centers.
+   * @param mergeWindow the merge window size, if a pair of centers is within
+   *          this mergeWindow the centers are merged together.
+   * @param maxIterations the maximum number of iterations to do before
+   *          breaking.
+   * @param verbose if true, progress will be reported after each iteration.
+   * @return the centers of the meanshift algorithm.
+   */
+  public static List<DoubleVector> cluster(List<DoubleVector> points,
+      double windowSize, double mergeWindow, int maxIterations, boolean verbose) {
+    // initialize our lookup structure
+    KDTree<Integer> kdTree = new KDTree<Integer>();
+    // assign an index to each point
+    int index = 0;
+    for (DoubleVector v : points) {
+      kdTree.add(v, index++);
+    }
+    kdTree.balanceBySort();
+    // start observing the centers
+    List<DoubleVector> centers = observeCenters(kdTree, points, windowSize,
+        verbose);
+    // now iterate over our found centers
+    for (int i = 0; i < maxIterations; i++) {
+      int converged = meanShift(kdTree, centers, windowSize);
+      // merge if centers are within the mergeWindow
+      merge(centers, mergeWindow);
[…]

### 2018-11-17 splitter_tool/code/prefixspan/AlgoPrefixSpan.java

@@ -1,0 +1,350 @@
+package prefixspan;
+
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+import java.util.Map.Entry;
+import split.SnippetCluster;
+import split.Snippet;
+
+/*** 
+ * This is an implementation of the PrefixSpan algorithm by Pei et al. 2001
+ * This implementation is part of the SPMF framework.
+ * 
+ * This implemtation uses pseudo-projection as suggested by Pei et al. 2001
+ * @author Philippe Fournier-Viger
+ **/
+
+public class AlgoPrefixSpan{
+	
+	// The sequential patterns that are found
+	private Sequences patterns = null;
+	private List<SnippetCluster> results = null;
+	
+	// for statistics
+	private long startTime;
+	
+	// minimum support
+	private double minsup;
+	
+	private double maxInterval;
+
+	//absolute value of minimum support
+	private int minsuppRelative;
+		
+	public AlgoPrefixSpan(double minsup, double maxInterval){
+		this.minsup = minsup;
+		this.maxInterval = maxInterval;
+	}
+
+	public Sequences runAlgorithm(SequenceDatabase database) {
+		patterns = new Sequences("FREQUENT SEQUENTIAL PATTERNS");
+		results = new ArrayList<SnippetCluster>();
+		this.minsuppRelative = (int) Math.ceil(minsup* database.size());
+		if(this.minsuppRelative == 0){ // protection
+			this.minsuppRelative = 1;
+		}
+		startTime = System.currentTimeMillis();
+		prefixSpan(database);
+		return patterns;
+	}
+	
+	/**
+	 * @param contexte The initial context.
+	 */
+	private void prefixSpan(SequenceDatabase database){
+		// We have to scan the database to find all frequent patterns of size 1.
+		// We note the sequences in which these patterns appear.
+		Map<Item, Set<Integer>> mapSequenceID = findSequencesContainingItems(database);
+		
+		// WE CONVERT THE DATABASE IN A PSEUDO-DATABASE, AND REMOVE
+		// THE ITEMS OF SIZE 1 THAT ARE NOT FREQUENT, SO THAT THE ALGORITHM 
+		// WILL NOT CONSIDER THEM ANYMORE. (OPTIMIZATION : OCTOBER-08 )
+		PseudoSequenceDatabase initialContext = new PseudoSequenceDatabase();
+		for(Sequence sequence : database.getSequences()){
[…]

### 2018-11-17 splitter_tool/code/prefixspan/Item.java

@@ -1,0 +1,45 @@
+package prefixspan;
+
+public class Item{
+	
+	// group Id
+	private int id = 0;
+	
+	// raw place Id
+	private final int rawId;
+	
+	public Item(int rawId){
+		this.rawId = rawId;
+	}
+
+	public int getId() {
+		return id;
+	}
+
+	public int getRawId() {
+		return rawId;
+	}
+	
+	public void setId(int id) {
+		this.id = id;
+	}
+	
+	public String toString(){
+		return "" + getId();
+	}
+	
+	public boolean equals(Object object){
+		Item item = (Item) object;
+		if((item.getId() == this.getId())){
+			return true;
+		}
+		return false;
+	}
+	
+	public int hashCode()
+	{
+		String string = ""+getId(); // This could be improved.
+		return string.hashCode();
+	}
+	
+}

### 2018-11-17 splitter_tool/code/prefixspan/Itemset.java

@@ -1,0 +1,93 @@
+package prefixspan;
+import java.util.ArrayList;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+
+import split.Places;
+import prefixspan.Item;
+
+
+/**
+ * This class represents an itemset from a sequence from a sequence database.
+ * The itemset can thus have a timestamp.
+ * @author Philippe Fournier-Viger 
+ */
+public class Itemset{
+
+	private final List<Item> items = new ArrayList<Item>(); // ordered list.
+	
+	// a timestamp associated to this itemset
+	private double timestamp = 0; 
+	
+	public Itemset(Item item){
+		addItem(item);
+	}
+	
+	public Itemset(){
+	}
+
+	public void addItem(Item value){
+			items.add(value);
+	}
+	
+	public void setItemIds(Places places) {
+		for(Item item: items) {
+			int placeId = item.getRawId();
+			int groupId = places.getGroupIdForPlace( placeId );
+			item.setId( groupId );
+		}
+	}
+	
+	public List<Item> getItems(){
+		return items;
+	}
+	
+	public Item get(int index){
+		return items.get(index);
+	}
+	
+	public void print(){
+		System.out.print(toString());
+	}
+	
+	public String toString(){
+		StringBuffer r = new StringBuffer ();
+		for(Item attribute : items){
+			r.append(attribute.toString());
+			r.append(' ');
+		}
+		return r.toString();
+	}
+
+	
+	public int size(){
+		return items.size();
+	}
+	
+	public Itemset cloneItemSetMinusItems(Map<Item, Set<Integer>> mapSequenceID, double minsuppRelatif) {
+		Itemset itemset = new Itemset();
+		itemset.timestamp = timestamp;
+		for(Item item : items){
+			if(mapSequenceID.get(item).size() >= minsuppRelatif){
+				itemset.addItem(item);
+			}
+		}
+		return itemset;
+	}
+	
+	public Itemset cloneItemSet(){
+		Itemset itemset = new Itemset();
+		itemset.timestamp = timestamp;
+		itemset.getItems().addAll(items);
+		return itemset;
+	}
+
+	public double getTimestamp() {
+		return timestamp;
+	}
+	
+	public void setTimestamp(double timestamp) {
+		this.timestamp = timestamp;
+	}
+}

### 2018-11-17 splitter_tool/code/prefixspan/Pair.java

@@ -1,0 +1,76 @@
+package prefixspan;
+
+import java.util.HashSet;
+import java.util.Set;
+
+
+/**
+ * This class is used by PrefixSpanItemIntervals. It represents, based on Hirate & Yamana
+ * a pair of an (1) Item  and (2) a time interval. It is used for calculating the support
+ * of item in a database. It contains some other information too.
+ * @author Philippe Fournier-Viger 
+ */
+public class Pair{
+	private final boolean postfix; // is cut at left
+	private final boolean prefix; // is cut at right
+	private final Item item;
+	
+	// List of the its of all the patterns that contains this one.
+	private Set<Integer> sequencesID = new HashSet<Integer>();
+	
+	Pair(long timestamp, boolean prefix, boolean postfix, Item item){
+		this.postfix = postfix;
+		this.prefix  = prefix;
+		this.item = item;
+	}
+	
+	// for prefixspan
+	Pair( boolean prefix, boolean postfix, Item item){
+		this.postfix = postfix;
+		this.prefix = prefix;
+		this.item = item;
+	}
+	
+	public boolean equals(Object object){
+		Pair paire = (Pair) object;
+		if((paire.postfix == this.postfix) 
+				&& (paire.prefix == this.prefix)
+				&& (paire.item.equals(this.item))){
+			return true;
+		}
+		return false;
+	}
+	
+	public int hashCode()
+	{// Ex: 127333,P,X,1  127333,N,Z,2
+		StringBuffer r = new StringBuffer();
+		r.append((postfix ? 'P' : 'N')); // the letters here have no meanings. they are just used for the hashcode
+		r.append((prefix ? 'X' : 'Z')); // the letters here have no meanings. they are just used for the hashcode
+		r.append(item.getId());
+		return r.toString().hashCode();
+	}
+
+	public boolean isPostfix() {
+		return postfix;
+	}
+
+	public Item getItem() {
+		return item;
+	}
+
+	public int getCount() {
+		return sequencesID.size();
+	}		
+
+	public Set<Integer> getSequencesID() {
+		return sequencesID;
+	}
+
+	public void setSequencesID(Set<Integer> sequencesID) {
+		this.sequencesID = sequencesID;
+	}
+
+	public boolean isPrefix() {
+		return prefix;
+	}
+}

### 2018-11-17 splitter_tool/code/prefixspan/PseudoSequence.java

@@ -1,0 +1,195 @@
+package prefixspan;
+
+import java.util.ArrayList;
+import java.util.List;
+
+
+/**
+ * This class represents a sequence from a projected database (as based in PrefixSpan).
+ * Since it is a projected sequence, it makes reference to the original sequence.
+ * 
+ * This class also include several methods for calculating the maximum periods, 
+ * semi-maximum perdiods, etc. as required by the BIDE+ algorithm.
+ * @author Philippe
+ */
+
+public class PseudoSequence {
+
+	private Sequence sequence;
+	private int firstItemset;
+	private int firstItem;
+	private int lastItemset;
+	private int lastItem;
+	private double prevtimestamp;
+	private List<Itemset> previtemset = new ArrayList<Itemset>();
+	
+	public PseudoSequence(PseudoSequence sequence, int indexItemset, int indexItem, double prevtimestamp){
+
+		this.sequence = sequence.sequence;
+		this.firstItemset = indexItemset + sequence.firstItemset;
+		if(this.firstItemset == sequence.firstItemset){
+			this.firstItem = indexItem + sequence.firstItem;
+		}else{
+			this.firstItem = indexItem; // ?????????? NÉCESSAIRE??
+		}
+		// Last itemset and item (par défaut c'est le dernier item et itemset de la séquence)
+		this.lastItemset = sequence.lastItemset;
+		this.lastItem = sequence.lastItem;
+		this.prevtimestamp = prevtimestamp;
+		this.previtemset = new ArrayList<Itemset>();
+		for (Itemset copy : sequence.previtemset){
+			this.previtemset.add(copy);
+		}
+	}
+	
+	public PseudoSequence(PseudoSequence sequence, int indexItemset, int indexItem, int lastItemset, int lastItem, double prevtimestamp){
+		this.sequence = sequence.sequence;
+		this.firstItemset = indexItemset + sequence.firstItemset;
+		if(this.firstItemset == sequence.firstItemset){
+			this.firstItem = indexItem + sequence.firstItem;
+		}else{
+			this.firstItem = indexItem; // ?????????? necessary??
+		}
+		// Last itemset and item
+		this.lastItemset = lastItemset;
+		this.lastItem = lastItem;
+		this.prevtimestamp = prevtimestamp;
+		this.previtemset = new ArrayList<Itemset>();
[…]

### 2018-11-17 splitter_tool/code/prefixspan/PseudoSequenceDatabase.java

@@ -1,0 +1,55 @@
+package prefixspan;
+
+
+import java.util.ArrayList;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Set;
+
+/**
+ * This class represents a projected database.
+ * A projected database is a list of pseudoSequences (projected sequences).
+ */
+public class PseudoSequenceDatabase {
+	
+	private List<PseudoSequence> pseudoSequences = new ArrayList<PseudoSequence>();
+
+	
+	public List<PseudoSequence> getPseudoSequences(){
+		return pseudoSequences;
+	}
+	
+	//----
+	
+	public void printContext(){
+		System.out.println(toString());
+	}
+	
+	public String toString(){
+		StringBuffer r = new StringBuffer("============  CONTEXTE ==========");
+		for(PseudoSequence sequence : pseudoSequences){ // pour chaque objet
+			r.append(sequence.getId());
+			r.append(":  ");
+			r.append(sequence.toString());
+			r.append('\n');
+		}
+		return r.toString();
+	}
+	
+	public int size(){
+		return pseudoSequences.size();
+	}
+
+	public Set<Integer> getSequenceIDs() {
+		Set<Integer> ensemble = new HashSet<Integer>();
+		for(PseudoSequence sequence : getPseudoSequences()){
+			ensemble.add(sequence.getId());
+		}
+		return ensemble;
+	}
+	
+	public void addSequence(PseudoSequence newSequence) {
+		pseudoSequences.add(newSequence);
+		
+	}
+}

### 2018-11-17 splitter_tool/code/prefixspan/Sequence.java

@@ -1,0 +1,233 @@
+package prefixspan;
+
+import java.text.DecimalFormat;
+import java.util.ArrayList;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+
+import split.Places;
+import prefixspan.Itemset;
+
+
+/**
+ * Implementation of a sequence.
+ * A sequence is a list of itemsets.
+ * @author Philippe Fournier-Viger 
+ **/
+public class Sequence{
+	public long shift = 0;
+	
+	private final List<Itemset> itemsets = new ArrayList<Itemset>();
+	private int id; // id de la sequence
+	
+	// List of IDS of all patterns that contains this one.
+	private Set<Integer> sequencesID = null;
+	
+	public Sequence(int id){
+		this.id = id;
+	}
+	
+	public String getRelativeSupportFormated(int transactionCount) {
+		double frequence = ((double)sequencesID.size()) / ((double) transactionCount);
+		// pretty formating :
+		DecimalFormat format = new DecimalFormat();
+		format.setMinimumFractionDigits(0); 
+		format.setMaximumFractionDigits(2); 
+		return format.format(frequence);
+	}
+	
+	public int getAbsoluteSupport(){
+		return sequencesID.size();
+	}
+
+	public void addItemset(Itemset itemset) {
+		itemsets.add(itemset);
+	}
+	
+	public Sequence cloneSequence(){
+		Sequence sequence = new Sequence(getId());
+		for(Itemset itemset : itemsets){
+			sequence.addItemset(itemset.cloneItemSet());
+		}
+		return sequence;
+	}
+	
+	public void setItemIds(Places places) {
+		for(Itemset itemset: itemsets) {
+			itemset.setItemIds(places);
+		}
+	}
+
+	public void print() {
+		System.out.print(toString());
+	}
+	
+	public String toString() {
+		// create string buffer
+		StringBuffer r = new StringBuffer("");
+		// for each itemset
+		for(Itemset itemset : itemsets){
+			// append each item from this itemset
+			for(Item item : itemset.getItems()){
+				String string = item.toString();
+				r.append(string);
+				r.append(' ');
+			}
+		}
+		//  print the list of IDs  of sequences that contains this pattern.
+/*		if(getSequencesID() != null){
+			r.append("  Sequence ID: ");
+			for(Integer id : getSequencesID()){
+				r.append(id);
+				r.append(' ');
+			}
+		}
+		*/
[…]

### 2018-11-17 splitter_tool/code/prefixspan/SequenceDatabase.java

@@ -1,0 +1,182 @@
+package prefixspan;
+import java.io.BufferedReader;
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileReader;
+import java.io.IOException;
+import java.io.InputStreamReader;
+import java.util.ArrayList;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Scanner;
+import java.util.Set;
+import java.util.StringTokenizer;
+
+import split.Places;
+import prefixspan.Item;
+import prefixspan.Itemset;
+import prefixspan.Sequence;
+
+/**
+ * Implementation of a sequence database.
+ * Each sequence should have a unique id.
+ * See examples in /test/ directory for the format of input files.
+ * @author Philippe Fournier-Viger 
+ **/
+public class SequenceDatabase{
+
+	 /** <p>
+	   * Represents the number of customers available in the database
+	   * </p>
+	   */
+	private int nbCustomers;
+	
+	// List of sequences
+	private final List<Sequence> sequences = new ArrayList<Sequence>();
+	
+	public void loadFile(String path) throws IOException {
+/*		BufferedReader br = new BufferedReader( new FileReader(path) );
+        while(true)  {
+            String line = br.readLine();
+            if(line == null)
+            	break;
+            addSequence(line.split(" "));
+        }
+        br.close();*/
+		
+		// we will read line by line
+		String thisLine;
+		BufferedReader myInput = null;
+		try {
+			FileInputStream fin = new FileInputStream(new File(path));
+			myInput = new BufferedReader(new InputStreamReader(fin));
+			// For each line (sequence) until end of file
+			while ((thisLine = myInput.readLine()) != null) {
+				// if the line is  a comment, is  empty or is a
+				// kind of metadata
+				if (thisLine.isEmpty() == true ||
+						thisLine.charAt(0) == '#' || thisLine.charAt(0) == '%'
+								|| thisLine.charAt(0) == '@') {
+					continue;
+				}
+				
+				// process this line (sequence) splitted into tokens
+				processSequence(thisLine.split(" "));		
+			}
+		} catch (Exception e) {
+			e.printStackTrace();
+		}finally {
+			// Close the input file
+			if(myInput != null){
+				myInput.close();
+			}
+	    }
+	}
+	
+	/**
+	 * Process a line from the input file, splitted into tokens.
+	 * @param tokens  a list of tokens (String).
+	 */
+	void processSequence(String[] tokens) {	//
[…]

### 2018-11-17 splitter_tool/code/prefixspan/Sequences.java

@@ -1,0 +1,90 @@
+package prefixspan;
+
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.List;
+
+/**
+ * Implementation of a set of sequences, grouped by their size (how many items they have).
+ * This class is used to store all the frequent sequential patterns.
+ * @author Philippe Fournier-Viger 
+ */
+public class Sequences {
+	public final List<List<Sequence>> levels = new ArrayList<List<Sequence>>();  // itemset classified by size
+	public int sequenceCount=0;
+	
+	private final String name;
+	
+	public Sequences(String name){
+		this.name = name;
+		levels.add(new ArrayList<Sequence>()); // we created zero empty by default.
+	}
+	
+	public void printSequencesFrequentes(int nbObject){
+		System.out.println(toString(nbObject));
+	}
+	
+	public String toString(int nbObject){
+		StringBuffer r = new StringBuffer(200);
+		r.append(" ----------");
+		r.append(name);
+		r.append(" -------\n");
+		int levelCount=0;
+		for(List<Sequence> level : levels){
+			r.append("  L");
+			r.append(levelCount);
+			r.append(" \n");
+			for(Sequence sequence : level){
+				r.append("  pattern ");
+				r.append(sequence.getId());
+				r.append(":  ");
+				r.append(sequence.toString());
+				r.append("support :  ");
+				r.append(sequence.getRelativeSupportFormated(nbObject));
+				r.append(" (" );
+				r.append(sequence.getAbsoluteSupport());
+				r.append('/');
+				r.append(nbObject);
+				r.append(") \n");
+			}
+			levelCount++;
+		}
+		r.append(" -------------------------------- Patterns count : ");
+		r.append(sequenceCount + "\n");
+		return r.toString();
+	}
+	
+	public HashMap<List<List<Integer>>, Integer> toStatistics(int nbObject){
+		HashMap<List<List<Integer>>, Integer> results = new HashMap<List<List<Integer>>, Integer>();
+		int levelCount=0;
+		for(List<Sequence> level : levels){
+			//levelCount;
+			for(Sequence sequence : level){
+				results.put(sequence.toStatistics(),sequence.getAbsoluteSupport());
+				System.out.println(sequence.getRelativeSupportFormated(nbObject));
+			}
+			levelCount++;
+		}
+		return results;
+	}
+	
+	public void addSequence(Sequence sequence, int k){
[…]

### 2018-11-17 splitter_tool/code/split/Clusterer.java

@@ -1,0 +1,22 @@
+package split;
+
+public abstract class Clusterer {
+
+	int nCluster;
+	int nIteration;
+	Places places;
+	
+	public Clusterer(Places places, int nCluster, int nIteration) {
+		this.places = places;
+		this.nCluster = nCluster;
+		this.nIteration = nIteration;
+		
+	}
+	
+	public int getClusterNum() {
+		return nCluster;
+	}
+	
+	public abstract Group[] cluster(Group group);
+	
+}

### 2018-11-17 splitter_tool/code/split/GridDensity.java

@@ -1,0 +1,30 @@
+package split;
+
+public class GridDensity {
+	private int row;
+	private int col;
+	private double density;
+	public GridDensity(int row, int col, double density){
+		this.setRow(row);
+		this.setCol(col);
+		this.setDensity(density);
+	}
+	public int getRow() {
+		return row;
+	}
+	public void setRow(int row) {
+		this.row = row;
+	}
+	public int getCol() {
+		return col;
+	}
+	public void setCol(int col) {
+		this.col = col;
+	}
+	public double getDensity() {
+		return density;
+	}
+	public void setDensity(double density) {
+		this.density = density;
+	}
+}

### 2018-11-17 splitter_tool/code/split/Group.java

@@ -1,0 +1,230 @@
+package split;
+
+import java.util.*;
+
+/*
+ * A group of places.
+ * */
+public class Group {
+
+	int id; // group id, starting from 0
+
+	static int mToAssignGroupId = 0;
+	
+	List<Integer> placeIds = null;
+
+	public Group() {
+		this.id = mToAssignGroupId++;
+		this.placeIds = new ArrayList<Integer>();
+	}
+
+	public Group(List<Integer> places) {
+		this.id = mToAssignGroupId++;
+		this.placeIds = places;
+	}
+	
+	public Group(int groupId) {
+		this.id = groupId;
+		this.placeIds = new ArrayList<Integer>();
+	}
+	
+	public Group(int groupId, List<Integer> places) {
+		this.id = groupId;
+		this.placeIds = places;
+	}
+
+	public int size() {
+		return placeIds.size();
+	}
+
+	public int getId() {
+		return id;
+	}
+
+	public List<Integer> getPlaceIds() {
+		return placeIds;
+	}
+
+	public void addPlace(int placeId) {
+		placeIds.add(placeId);
+	}
+
+	public void clear() {
+		placeIds = new ArrayList<Integer>();
+	}
+
+	/*
+	 * Split all groups by the categories of places.
+	 */
+	public List<Group> splitByCategory(Places places, int level) {
+
+		Map<Integer, Group> subgroups = new HashMap<Integer, Group>();
+
+		for (Integer placeId : placeIds) {
+
+			Place place = places.getPlace(placeId);
+			int categoryId = getCategoryId(place, level);
+
+			if (subgroups.containsKey(categoryId)) {
+				subgroups.get(categoryId).addPlace(placeId);
+			} else {
+				Group newGroup = new Group();
+				newGroup.addPlace(placeId);
+				subgroups.put(categoryId, newGroup);
+			}
+		}
+
+		return convertToList(subgroups);
+	}
+
+	private int getCategoryId(Place place, int level) {
+		int maxLevel = place.getMaxCategoryLevel();
+		int possibleLevel = level < maxLevel ? level : maxLevel;
+		return place.getCategory(possibleLevel);
+	}
+
+	private List<Group> convertToList(Map<Integer, Group> map) {
+		List<Group> result = new ArrayList<Group>();
+		Iterator iter = map.entrySet().iterator();
+		while (iter.hasNext()) {
+			Map.Entry entry = (Map.Entry) iter.next();
+			result.add((Group) entry.getValue());
+		}
[…]

### 2018-11-17 splitter_tool/code/split/GroupSequence.java

@@ -1,0 +1,38 @@
+package split;
+
+import java.io.BufferedWriter;
+import java.io.FileWriter;
+import java.util.ArrayList;
+import java.util.List;
+
+import split.Group;
+
+public class GroupSequence {
+	
+	List<Group> mGroups = new ArrayList<Group>();
+	int mSupport; //support: number of visitors
+	
+	public GroupSequence() {
+	}
+	
+	public void addGroup(Group g) {
+		mGroups.add( g );
+	}
+	
+	public void setSupport(int support) {
+		mSupport = support;
+	}
+	
+	public void write(String groupFile, String patternFile) throws Exception {
+		BufferedWriter bwGroup = new BufferedWriter(new FileWriter(groupFile, true)); // append
+		for(Group g: mGroups)
+			bwGroup.append( g.toString() + "\n" );
+		bwGroup.close();
+
+		BufferedWriter bwPattern = new BufferedWriter(new FileWriter(patternFile, true));
+		for(Group g: mGroups)
+			bwPattern.append( g.getId() + " ");
+		bwPattern.append( "Support:" + mSupport + "\n");
+		bwPattern.close();
+	}
+}

### 2018-11-17 splitter_tool/code/split/Groups.java

@@ -1,0 +1,361 @@
+package split;
+
+import java.io.BufferedWriter;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.Collections;
+import java.util.Comparator;
+import java.util.List;
+import java.util.Set;
+
+import prefixspan.Sequence;
+import prefixspan.SequenceDatabase;
+
+public class Groups {
+
+	List<Group> groups = null;
+
+	public Groups() {
+		this.groups = new ArrayList<Group>();
+	}
+
+	public Groups(List<Group> groups) {
+		this.groups = groups;
+	}
+
+	public void addGroup(Group p) {
+		groups.add(p);
+	}
+
+	public List<Group> getGroups() {
+		return groups;
+	}
+
+	// current level when drilling down the category tree
+	public void splitByCategory(Places places, int level) {
+		List<Group> newGroups = new ArrayList<Group>();
+		int groupNum = groups.size(); // original number of groups.
+		for (int i = 0; i < groupNum; i++) {
+			Group group = groups.get(i);
+			List<Group> subgroups = group.splitByCategory(places, level);
+			newGroups.addAll(subgroups);
+		}
+		this.groups = newGroups;
+	}
+
+	public void splitByGrid(Places places, double minDensity, double gridSize) {
+		final int rownum = (int) ((41.0 - 40.4) / gridSize) + 1;
+		final int colnum = (int) ((-73.7 + 74.3) / gridSize) + 1;
+		int groupNum = groups.size(); // original number of groups.
+		List<Group> newGroups = new ArrayList<Group>();
+		for (int i = 0; i < groupNum; i++) {
+			Group group = groups.get(i);
+			double density[][] = new double[rownum][colnum];
+			int used[][] = new int[rownum][colnum];
+			for (int j = 0; j < rownum; j++) {
+				for (int k = 0; k < colnum; k++) {
+					density[j][k] = 0.0;
+					used[j][k] = -1;
+				}
+			}
+			for (Integer placeId : group.placeIds) {
+				Place place = places.getPlace(placeId);
+				int row = (int) ((place.getLat() - 40.4) / gridSize);
+				int col = (int) ((place.getLng() + 74.3) / gridSize);
+				density[row][col] = density[row][col] + 1;
+			}
+			ArrayList<GridDensity> mydensitylist = new ArrayList<GridDensity>();
[…]

### 2018-11-17 splitter_tool/code/split/KMeans.java

@@ -1,0 +1,123 @@
+package split;
+
+import java.util.List;
+import java.util.Random;
+
+public class KMeans extends Clusterer {
+
+	Random r = new Random();
+	Place[] previousMean = null;
+	Place[] mean = null;
+	Group group = null;
+	Group[] clusters = null;
+	
+	public KMeans(Places places, int nCluster, int nIteration) {
+		super(places, nCluster, nIteration);
+	}
+
+	public Group[] cluster(Group group) {
+		int originalClusterNum = this.nCluster;
+		if(group.size() < originalClusterNum)
+			this.nCluster = group.size();
+		
+		initialize(group);
+		for (int iteration = 0; iteration < nIteration; iteration++) {
+			computeMean();
+			if( !hasMeanChanged() )
+				break;
+			assignToClusters();
+		}
+		
+		this.nCluster = originalClusterNum;
+		return clusters;
+	}
+
+	private void initialize(Group g) {
+		this.group = g;
+		previousMean = new Place[ nCluster ];
+		mean = getRandomMean();
+		clusters = new Group[ nCluster ];
+		for(int i=0; i<nCluster; i++)
+			clusters[i] = new Group();
+		assignToClusters();
+	}
+	
+	private Place[] getRandomMean() {
+		Place[] mean = new Place[ nCluster ];
+		List<Integer> placeIds = group.getPlaceIds();
+		int [] kRandomNumbers = genKRandomNumbers(placeIds.size(), nCluster);
+		for(int i=0; i<nCluster; i++) {
+			Place p = places.getPlace( placeIds.get( kRandomNumbers[i]) );
+			mean[i] = new Place(p.getLat(), p.getLng()); //a pseudo place
+		}
+		return mean;
+	}
+	
+	//Generate K distinct random numbers in [0,n-1]
+	private int[] genKRandomNumbers(int n, int k) {
+		
+		int[] completeArray = new int[n];
+		for(int i=0; i<n; i++) {
+			completeArray[i] = i;
+		}
+		
+		int[] result = new int[k];
+		int bound = n;
+		for(int i=0; i<k; i++) {
+			int randNum = r.nextInt( bound ); //generate a random integer between 0~bound-1
+			result[i] = completeArray[ randNum ];
+			completeArray[randNum] = completeArray[ bound-1 ];
+			completeArray[bound-1] = result[i];
+			bound --;
+		}
+		return result;
+	}
+	
[…]

### 2018-11-17 splitter_tool/code/split/Place.java

@@ -1,0 +1,61 @@
+package split;
+
+import java.util.List;
+
+public class Place {
+	
+	private final int id;
+	private int groupId = 0;
+	private final double lat;
+	private final double lng;
+	private List<Integer> categories = null;
+	
+	public Place(double lat, double lng) {
+		this.id = -1;
+		this.lat = lat;
+		this.lng = lng;
+	}
+	
+	public Place(int id, double lat, double lng, List<Integer> categories) {
+		this.id = id;
+		this.lat = lat;
+		this.lng = lng;
+		this.categories = categories;
+	}
+	
+	public int getId() {
+		return id;
+	}
+	
+	public int getGroupId() {
+		return groupId;
+	}
+	
+	public void setGroupId(int groupId) {
+		this.groupId = groupId;
+	}
+	
+	public double getLat() {
+		return lat;
+	}
+	
+	public double getLng() {
+		return lng;
+	}
+	
+	public double getDistanceTo(Place p) {
+		double latDiff = this.lat - p.getLat();
+		double lngDiff = this.lng - p.getLng();
+		return Math.sqrt( latDiff*latDiff + lngDiff*lngDiff );
+	}
+	
+	// Get the category for requested level, level starts from 0
+	public int getCategory(int level) {
+		return categories.get( level );
+	}
+	
+	public int getMaxCategoryLevel() {
+		return categories.size() - 1;
+	}
+	
+}

### 2018-11-17 splitter_tool/code/split/Places.java

@@ -1,0 +1,70 @@
+package split;
+
+import java.io.BufferedReader;
+import java.io.FileReader;
+import java.util.ArrayList;
+import java.util.List;
+import java.util.Set;
+
+public class Places {
+
+	List<Place> places = new ArrayList<Place>();
+	
+	/*
+	 * Load Places from data file
+	 * */
+	public void loadFile(String filename) throws Exception {
+		BufferedReader br = new BufferedReader( new FileReader(filename) );
+        while(true)  {
+            String line = br.readLine();
+            if(line == null)
+            	break;
+            addPlace(line.split(","));
+        }
+        br.close();
+	}
+	
+	public void addPlace(String[] placeAttributes) {
+		
+		int id = Integer.parseInt( placeAttributes[0] ); //place id
+		double lat = Double.parseDouble( placeAttributes[1] );
+		double lng = Double.parseDouble( placeAttributes[2] );
+		
+		List<Integer> categories = new ArrayList<Integer>();
+		String[] integers = placeAttributes[placeAttributes.length - 1].split(" ");
+		for(String s : integers) {
+			int categoryId = Integer.parseInt( s );
+			categories.add( categoryId );
+		}
+		
+		Place place = new Place(id, lat, lng, categories);
+		
+		this.places.add(place);
+	}
+
+	public Place getPlace(int placeId) {
+		return places.get( placeId );
+	}
+	
+	public int getTotalPlaceNum() {
+		return places.size();
+	}
+	
+	public void setPlaceGroupIds(Groups groups) {
+		for( Group group: groups.getGroups() ) {
+			int groupId = group.getId();
+			List<Integer> placeIds = group.getPlaceIds();
+			for(Integer placeId: placeIds) {
+				places.get(placeId).setGroupId(groupId);
+			}
+		}
+	}
+	
+	/*
+	 * Get the group id a place belongs to.
+	 * */
+	public int getGroupIdForPlace(int placeId) {
+		return places.get(placeId).getGroupId();
+	}
+	
+}

### 2018-11-17 splitter_tool/code/split/Snippet.java

@@ -1,0 +1,52 @@
+package split;
+
+import java.util.ArrayList;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Set;
+
+import meanshift.DenseDoubleVector;
+import meanshift.DoubleVector;
+
+public class Snippet {
+	
+	List<Integer> mPlaceSequence = new ArrayList<Integer>();
+	Set<Integer> mVisitors= new HashSet<Integer>();
+	int mLength;
+	int mWeight; //number of visitors
+	
+	public Snippet(List<Integer> places, Set<Integer> visitors) {
+		mPlaceSequence = places;
+		mVisitors = visitors;
+		mLength = mPlaceSequence.size();
+		mWeight = mVisitors.size() ;
+	} 
+	
+	public int getPlace(int position) {
+		return mPlaceSequence.get( position );
+	}
+	
+	public List<Integer> getPlaceSequence(){
+		return mPlaceSequence;
+	}
+	
+	public Set<Integer> getVisitors() {
+		return mVisitors;
+	}
+	
+	public int getWeight() {
+		return mWeight;
+	}
+
+	public DoubleVector toDoubleVector(Places places) {
+		double[] coordinates = new double[ 2 * mLength ];
+		for(int i=0; i<mPlaceSequence.size(); i++) {
+			int placeId = mPlaceSequence.get( i );
+			Place place = places.getPlace( placeId );
+			coordinates[ 2*i ] = place.getLat();
+			coordinates[ 2*i+1 ] = place.getLng();
+		}
+		return new DenseDoubleVector( coordinates );
+	}
+
+}

### 2018-11-17 splitter_tool/code/split/SnippetCluster.java

@@ -1,0 +1,104 @@
+package split;
+
+import java.io.BufferedWriter;
+import java.io.FileWriter;
+import java.util.ArrayList;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Set;
+
+//import meanshift.GroupSequence;
+
+public class SnippetCluster {
+
+	int mSnippetLength; //snippetLength
+	List<Snippet> mSnippets; //all the snippets must have the same length
+	List<Integer> mGroupSequence; //a sequence of group ID, the coarse pattern
+	
+	public SnippetCluster(int snippetLength) {
+		mSnippetLength = snippetLength;
+		mSnippets = new ArrayList<Snippet>();
+		mGroupSequence = new ArrayList<Integer>();
+	}
+	
+	public void addGroupID(Integer groupId) {
+		mGroupSequence.add( groupId );
+	}
+	
+	public List<Integer> getPlaceSequence() {
+		return mGroupSequence;
+	}
+	
+	public void addSnippet(Snippet snippet) {
+		mSnippets.add( snippet );
+	}
+	
+	public List<Snippet> getSnippets() {
+		return mSnippets;
+	}
+	
+	public int getSnippetLength() {
+		return mSnippetLength;
+	}
+	
+	public String toString(){
+		StringBuffer r = new StringBuffer(200);
+		r.append("mGroupSequence: ");
+		for (Integer place : mGroupSequence){
+			r.append(place);
+			r.append(" ");
+		}
+		r.append("\n");
+		for (Snippet mySnippet : mSnippets){
+			r.append("Place Sequence: ");
+			for (Integer myplace : mySnippet.getPlaceSequence()){
+				r.append(myplace);
+				r.append(" ");
+			}
+			r.append("\n");
+			r.append("Sequence ID: ");
+			for (Integer myID : mySnippet.getVisitors()){
+				r.append(myID);
+				r.append(" ");
+			}
+			r.append("\n");
+		}
+		return r.toString();
+	}
+	
+	//transform a snippet cluster into a group sequence
+	public GroupSequence toGroupSequence() {
+		GroupSequence gs = new GroupSequence();
+		for(int i=0; i<mSnippetLength; i++) {
+			Group g = constructGroup( i );
+			gs.addGroup( g );
+		}
+		gs.setSupport( computeSuppport() );
+		return gs;
+	}
+	
+	//support of snippets
+	public int computeSuppport() {
+		Set<Integer> visitors = new HashSet<Integer>();
[…]

### 2018-11-17 splitter_tool/code/split/Splitter.java

@@ -1,0 +1,184 @@
+package split;
+
+import java.io.BufferedWriter;
+import java.io.FileWriter;
+import java.util.ArrayList;
+import java.util.Iterator;
+import java.util.List;
+import java.util.Map;
+
+import meanshift.DoubleVector;
+import meanshift.MeanShift;
+
+public class Splitter {
+	
+	double mSupThreshold = 10; //support threshold
+	double mVarThreshold = 1.0; //variance threshold
+	double mTau = 0.8; //dampening factor
+	double mMergeWindow = 2e-3;
+	int mMaxIter = 100; // max iteration for mean shift
+	
+	int mSnippetLength = 1;
+	Places mPlaces = null; // places
+	List<SnippetCluster> patternList = null; //result sequential patterns
+	
+	public Splitter(int supThreshold, double varThreshold, double tau, Places places) {
+		this.mSupThreshold = supThreshold;
+		this.mVarThreshold = varThreshold;
+		this.mTau = tau;
+		mPlaces = places;
+	}
+	
+	public void minePatterns(int snippetLength, List<Snippet> snippets, double bandwidth ) throws Exception {
+		patternList = new ArrayList<SnippetCluster>();
+		mSnippetLength = snippetLength;
+		mMergeWindow = computeDimensionInvariant(snippetLength, mMergeWindow);
+		double dimensionInvariantBandwidth = computeDimensionInvariant(snippetLength, bandwidth);
+		//splitPattern(snippets, dimensionInvariantBandwidth);
+		splitPatternWithPruning(snippets, dimensionInvariantBandwidth);
+		//splitPatternVis(snippets, dimensionInvariantBandwidth);
+	}
+	
+	public List<SnippetCluster> getPatterns() {
+		return patternList;
+	}
+	
+	
+	//k: snippet length
+	private double computeDimensionInvariant(int k, double value) {
+		if(k==1) 
+			return value;
+		return value;
+		/*
+		int factorial = 1;
+		for(int i=1; i<=k; i++)
+			factorial *= i;
+		return pow( factorial*value*value * pow(PI, (1-k) ), 0.5/k);
+		*/
+	}
+	
+	private void splitPattern(List<Snippet> snippets, double bandwidth ) {
+		
+		if(bandwidth < 5e-4) 
+			return;
+		
+		List<SnippetCluster> snippetClusters = cluster(snippets, bandwidth);
+		
[…]

### 2018-11-17 splitter_tool/tool/run-4sq.sh

@@ -1,0 +1,1 @@
+java -jar -Xmx4G splitter.jar 4sq.yaml

### 2018-12-21 paper.tex
dd
ee

--- 2018-11-17 report/SDBProject.tex
@@
-\documentclass[a4paper,oneside]{article}
-\usepackage{indentfirst}
-\usepackage[top=0.7in, bottom=0.7in, left = 0.7in, right = 0.7in]{geometry}
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
 \usepackage{graphicx}
-\usepackage{subcaption}
-\usepackage{indentfirst}
-\usepackage{cite}
-\usepackage{fontspec}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 
-\title{Term Project\\Splitter: Mining Fine-Grained Sequential Patterns in Semantic Trajectories}
-\author{Fawwaz Dzaky Zakiyal (201899213)\\Tanjung Dion (201883621)\\}
-\date{Stream Database (Fall 2018)}
+\makeatletter
+\def\endthebibliography{%
+  \def\@noitemerr{\@latex@warning{Empty `thebibliography' environment}}%
+  \endlist
+}
+\makeatother
 
 \begin{document}
+
+\title{Building GUI Application of Splitter (Mining Fine-Grained Sequential Patterns in Semantic)
+Trajectories\\
+%\thanks{* Corresponding Author}
+}
+
+\author{\IEEEauthorblockN{Tanjung Dion, Fawwaz Dzaky Zakiyal}
+\IEEEauthorblockA{\textit{Department of Electrical and Computer Engineering} \\
+\textit{Pusan National University}\\
+Busan, Republic of Korea \\
+\{tanjung.dn, dzakybd\}@gmail.com}}
+
 \maketitle
 
-	\section{Introduction}
+\begin{abstract}
 Semantic trajectory is a sequence of timestamped places wherein each place has information about spatial location and a semantic label.
@@
 This process of mining fine-grained pattern have been proposed by Zang et.
-al \cite{splitter}.
+al.
 For the final project we will re-implement the process of find fine-grained pattern in Java programing language.
+\end{abstract}
 
-	\section{Problem}
-	\begin{itemize}
-		\item How to mine the coarse patterns and their snippets? 
-		\item How to effectively cluster the snippets given the fact that we do not know the correct number of clusters?
-	\end{itemize}
+\begin{IEEEkeywords}
+component, formatting
+\end{IEEEkeywords}
 
-	\section{Proposed Method}
-		 \subsection{Dataset}
-		 This project will use the real dataset, 4SQ that collected from Foursquare check-in sequence in New York.
-It consists of 48564 places that divided into 417 place categories and it stored semantic trajectories from 14909 users.
-4SQ dataset provides 3 files:
-		 \begin{enumerate}
-		 \item \textit{Sequences}, it contains users semantic trajectories including attributes of check-in timestamp and place ID.
-		 \item \textit{Places}, it contains information about the places (place ID, latitude, longitude, category ID).
-		 \item \textit{Category}, it contains information of place category ID corresponding with its place category name.
-		 \end{enumerate}
+\section{Introduction}
+How to mine the coarse patterns and their snippets?
+How to effectively cluster the snippets given the fact that we do not know the correct number of clusters?
 
+\section{Implementation}
 \subsection{System Design}
@@
 By doing this process, our trajectory dataset will satisfy semantic consistency.
-
+\par
 Then, Prefixspan algorithm will be used to mining the coarse pattern.
@@
 Set of coarse pattern from previous process will be transformed into K-dimensional point x.
-
+\par
 Then, we employ mean shift clustering to extract the dense and compact snippet cluster based on the support and variance threshold.
@@
 
-		\subsection{Implementation}
+\subsection{Key technologies in Splitter}
+Stateful Authentication has drawback that server needs to find that session and deserialize it on every request, because user data is stored on the specific server.
+Thus, it hard to scale, cause the server needs to create a session for a user and persist it somewhere on the server.
+If we have a distributed system, we have to make sure that session is shared between multiple nodes.
+
+So, we proposed Stateless/Token Authentication where the server don't maintain the state of a user, user needs to store that token and send on every request to a restricted resource in the Authorization header.
+Thus, it easy to scale, cause the token contains all the information to identify the user, eliminating the need for the session state.
+We can pass the user to any server, instead of being bound to the same server we logged in on.
+It can support high-speed mobile users, such as users in cars, users on trains, and vehicular computing.
+In our environment, the cloud become the auth server.
+Based on assumption it can guarantee the security to generate the token.
+
+\section{Demonstration}
+This document is a
+
+\subsection{Dataset}
+This project will use the real dataset, 4SQ that collected from Foursquare check-in sequence in New York.
+It consists of 48564 places that divided into 417 place categories and it stored semantic trajectories from 14909 users.
+4SQ dataset provides 3 files:
+\begin{enumerate}
+\item \textit{Sequences}, it contains users semantic trajectories including attributes of check-in timestamp and place ID.
+\item \textit{Places}, it contains information about the places (place ID, latitude, longitude, category ID).
+\item \textit{Category}, it contains information of place category ID corresponding with its place category name.
+\end{enumerate}
+
+\subsection{Result}
 We will re-implement the process of mining fine-grained pattern using java programing language.
@@
 
-		\begin{figure}[!h]
+\begin{figure}[!ht]
 \centering
-			\begin{subfigure}[b]{0.4\linewidth}
+\includegraphics[width=0.5\linewidth]{GraphRepresentation}
+\caption{Graph illustration}
+\label{fig:graph}
+\end{figure}
+
+\begin{figure}[!ht]
 \centering
-				\includegraphics[width=1\linewidth]{GUI}
+\includegraphics[width=0.5\linewidth]{GUI}
 \caption{Program UI illustration}
 \label{fig:javagui}
-			\end{subfigure}
-				\begin{subfigure}[b]{0.4\linewidth}
-				\centering
-				\includegraphics[width=0.7\linewidth]{GraphRepresentation}
-				\caption{Graph illustration}
-				\label{fig:graph}
-			\end{subfigure}
-			\caption{User Interface Ilustration}
-			\label{fig:UI}
 \end{figure}
 
-	\section{Testing and Evaluation}
-	For the testing and evaluation, we will conduct an experiment of mining fine-grained pattern by varying support threshold, spatial variance threshold, time movement constraint, kernel windows size, and dampening factor in the term of coverage and pattern.
-Coverage is the total number of trajectory in all pattern that satisfy fine-grained pattern.
-\begin{thebibliography}{1}
-	\bibitem{splitter} Zhang, C., Han, J., Shou, L., Lu, J., La Porta, T.
-(2014).{\em Splitter: Mining fine-grained sequential patterns in semantic trajectories}.
-Proceedings of the VLDB Endowment, 7(9), 769-780.
-\end{thebibliography}
+This document is a \cite{sdbproject}
+
+\section{Conclusion}
+This document is a \cite{zhang2014splitter}
+
+\section*{Acknowledgment}
+This paper is submitted to fulfill term project task from Stream Database class (Fall 2018), Pusan National University.
+
+\bibliographystyle{IEEEtran}
+\bibliography{refs}
+
 \end{document}

### 2018-12-23 paper copy.tex
rr
rtt

--- 2018-12-21 paper.tex
@@
 
-\title{Building GUI Application of Splitter (Mining Fine-Grained Sequential Patterns in Semantic)
-Trajectories\\
-%\thanks{* Corresponding Author}
+\title{SplitterGUI\\
+{\large GUI Application of Mining Fine-Grained Sequential Patterns in Semantic Trajectories}
+%\thanks{Identify applicable funding agency here. If none, delete this.}
 }
@@
 Semantic trajectory is a sequence of timestamped places wherein each place has information about spatial location and a semantic label.
-By mining fine-grained pattern that satisfy semantic consistency (consistent place id in each category), spatial compactness (compact area for each category) and temporal continuity (limited time constraint), it will give benefit such as urban planning and targeted advertising.
-This process of mining fine-grained pattern have been proposed by Zang et.
-al.
-For the final project we will re-implement the process of find fine-grained pattern in Java programing language.
+By mining fine-grained pattern that satisfy semantic consistency, spatial compactness and temporal continuity, it will give benefit such as urban planning and targeted advertising.
+One of the state-the-art method to mine the fine-grained pattern is Splitter algorithm.
+Firstly, it find set of coarse patterns and their snippets by using PrefixSpan, and then find the set of fine-grained patterns using mean shift method.
+In this project we build, SplitterGUI, GUI application to visualize the process of the Splitter algorithm.
+We also discuss the key techniques in Splitter and conduct an experiment using 4SQ dataset to demontrate the result of SplitterGUI.
+
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting
+fine-grained pattern, semantic trajectories, GUI application.
 \end{IEEEkeywords}
@@
 \section{Introduction}
-How to mine the coarse patterns and their snippets?
-How to effectively cluster the snippets given the fact that we do not know the correct number of clusters?
+
+The sequential patterns can be found in a trajectory dataset, if it properly extracted.
+It become benefit for targeted advertising, urban planning, location prediction, etc.
+In other hand, classic sequential pattern mining algorithms cannot work effectively in semantic trajectories, a sequence of time-stamped places wherein each place has information about spatial location and a semantic label.
+Because of the places in the continuous space cannot be regarded as independent items, so independent place cannot be used to find the frequent sequences.
+Instead, semantic label need to be grouped to form frequent sequential patterns.
+But, there is also a challenge to get fine-grained sequential patterns, that it must fulfill requirements of spatial compactness (compact area for each place category), semantic consistency (consistent place ID in each place category) and temporal continuity (limited time constraint).
+\par
+The process of mining fine-grained pattern have been proposed by Zang et.
+al \cite{zhang2014splitter}.
+They provide two-step approach to obtain fine-grained sequential patterns.
+First-step, obtain the coarse patterns from the semantic trajectory data using the full projection method to modify PrefixSpan.
+The result patterns will fullfil the semantic and temporal constraints.
+Second-step, splitting each coarse patterns into fine-grained patterns that fulfill the spatial constraint through top-down pattern discovery process using weighted snippet shift by Epanechnikov kernel.
+\par
+In this project, aiming at implementing the mining fine-grained pattern method proposed by Zang et.
+al \cite{zhang2014splitter} and build the GUI application to visualize the process of the Splitter algorithm, called SplitterGUI.
+It make the dataset, course patterns and fine-grained patterns into a visualized map by determined Splitter algoritm's parameters.
+Afterwards, we discuss the key techniques in Splitter and conduct an experiment using 4SQ dataset to demontrate the result of SplitterGUI.
 

### 2018-12-23 paper.tex
rr
rtt

@@
 
-\title{Building GUI Application of Splitter (Mining Fine-Grained Sequential Patterns in Semantic)
-Trajectories\\
-%\thanks{* Corresponding Author}
+\title{SplitterGUI\\
+{\large GUI Application of Mining Fine-Grained Sequential Patterns in Semantic Trajectories}
+\thanks{The SplitterGUI project files can be downloaded at
+$github.com/dzakybd/Datastream-project$}
 }
@@
 Semantic trajectory is a sequence of timestamped places wherein each place has information about spatial location and a semantic label.
-By mining fine-grained pattern that satisfy semantic consistency (consistent place id in each category), spatial compactness (compact area for each category) and temporal continuity (limited time constraint), it will give benefit such as urban planning and targeted advertising.
-This process of mining fine-grained pattern have been proposed by Zang et.
-al.
-For the final project we will re-implement the process of find fine-grained pattern in Java programing language.
+By mining fine-grained pattern that satisfy semantic consistency, spatial compactness and temporal continuity, it will give benefit such as urban planning and targeted advertising.
+One of the state-the-art method to mine the fine-grained pattern is Splitter algorithm.
+Firstly, it find set of coarse patterns and their snippets by using PrefixSpan, and then find the set of fine-grained patterns using mean shift method.
+In this project we build, SplitterGUI, GUI application to visualize the process of the Splitter algorithm.
+We also discuss the key techniques in Splitter and conduct an experiment using 4SQ database to demontrate the result of SplitterGUI.
+
 \end{abstract}
@@
 \section{Introduction}
-How to mine the coarse patterns and their snippets?
-How to effectively cluster the snippets given the fact that we do not know the correct number of clusters?
+The sequential patterns can be found in a trajectory database, if it properly extracted.
+It become benefit for targeted advertising, urban planning, location prediction, etc.
+In other hand, classic sequential pattern mining algorithms cannot work effectively in semantic trajectories, a sequence of time-stamped places wherein each place has information about spatial location and a semantic label.
+Because of the places in the continuous space cannot be regarded as independent items, so independent place cannot be used to find the frequent sequences.
+Instead, semantic label need to be grouped to form frequent sequential patterns.
+But, there is also a challenge to get fine-grained sequential patterns, that it must fulfill requirements of spatial compactness (compact area for each place category), semantic consistency (consistent place ID in each place category) and temporal continuity (limited time constraint).
+\par
+The process of mining fine-grained pattern have been proposed by Zang et.
+al \cite{zhang2014splitter}.
+They provide two-step approach to obtain fine-grained sequential patterns.
+First-step, obtain the coarse patterns from the semantic trajectory data using the full projection method to modify PrefixSpan.
+The result patterns will fullfil the semantic and temporal constraints.
+Second-step, splitting each coarse patterns into fine-grained patterns that fulfill the spatial constraint through top-down pattern discovery process using weighted snippet shift by Epanechnikov kernel.
+\par
+In this project, aiming at implementing the mining fine-grained pattern method proposed by Zang et.
+al \cite{zhang2014splitter} and build the GUI application to visualize the process of the Splitter algorithm, called SplitterGUI.
+It make the database, course patterns and fine-grained patterns into a visualized map by determined Splitter algoritm's parameters.
+Afterwards, we discuss the key techniques in Splitter and conduct an experiment using 4SQ database to demontrate the result of SplitterGUI.
 
@@
 \centering
-\includegraphics[width=1\linewidth]{splitter}
+\includegraphics[width=0.55\linewidth]{splitter}
 \caption{System Design}
@@
 Mining coarse pattern is a process to find sequential pattern that satisfy semantic consistency and temporal continuity.
-In the first step, we add trajectory dataset that have information about place id, movement time, group id, and spatial location to the system.
-This trajectory dataset will be transformed into semantic trajectory dataset by grouping place id based on category.
+In the first step, we add trajectory database that have information about place id, movement time, group id, and spatial location to the system.
+This trajectory database will be transformed into semantic trajectory database by grouping place id based on category.
 However, we still keep the original place id in each category to prevent one trajectory from being counted repeatedly.
-By doing this process, our trajectory dataset will satisfy semantic consistency.
+By doing this process, our trajectory database will satisfy semantic consistency.
 \par
-Then, Prefixspan algorithm will be used to mining the coarse pattern.
-In the Prefixspan algorithm, we include all posfixes to avoid missing pattern under the given time constrain.
+Then, PrefixSpan algorithm will be used to mining the coarse pattern.
+In the PrefixSpan algorithm, we include all post-fixes to avoid missing pattern under the given time constrain.
 Output from mining coarse pattern is set of coarse pattern that will be used in the next process.
@@
 
-\subsection{Key technologies in Splitter}
-Stateful Authentication has drawback that server needs to find that session and deserialize it on every request, because user data is stored on the specific server.
-Thus, it hard to scale, cause the server needs to create a session for a user and persist it somewhere on the server.
-If we have a distributed system, we have to make sure that session is shared between multiple nodes.
+\subsection{Key techniques in Splitter}
+\subsubsection{Mining Coarse Pattern}
+Before mining coarse pattern, trajectory database D should be transformed to semantic trajectory by grouping each place based on its category.
+The purpose is to find any frequent sequences that have similar categories.
+For example, Fig.
+\ref{fig:transformed-database} shows database transformation with office $=G_{1}$, shop $=G_{2}$, restaurant $=G_{3}$.
 
-So, we proposed Stateless/Token Authentication where the server don't maintain the state of a user, user needs to store that token and send on every request to a restricted resource in the Authorization header.
-Thus, it easy to scale, cause the token contains all the information to identify the user, eliminating the need for the session state.
-We can pass the user to any server, instead of being bound to the same server we logged in on.
-It can support high-speed mobile users, such as users in cars, users on trains, and vehicular computing.
-In our environment, the cloud become the auth server.
-Based on assumption it can guarantee the security to generate the token.
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=1\linewidth]{transformed_database}
+	\caption{Semantic trajectory database}
+	\label{fig:transformed-database}
+\end{figure}
+
+After transformation, we mining sequential pattern that satisfy support threshold $\sigma$ and time constraint $\Delta t$ using PrefixSPan algorithm.
+PrefixSpan algorithm use frequent item as short pattern and prefixes to build projected database then grow the short pattern by searching local frequent item in projected database.
+However, PrefixSpan algorithm should be modified to satisfy our coarse pattern.
+\ref{fig:mining-coarse-pattern} shows the modified prefix span algorithm.
+First, we extract all frequent item at least $\sigma$ in semantic trajectory D.
+Then for each item we build item-projected database as S using full projection.
+Full projection means that we extract all pattern that occurred in database.
+For example, object 0 in \ref{fig:transformed-database} has 2 pattern $P_{3}\rightarrow P_{7}\rightarrow P_{9}$ and $P_{1}\rightarrow P_{7}\rightarrow P_{9}$.
+\par
+Output this item as our short pattern and then grow this pattern by calling PrefixSpan function.
+This function has similar procedure with initial projection function.
+However, we check time constraint when searching frequent item in projected database.
+We also call this PrefixSpan function recursively to grow the pattern until the pattern cannot be grown anymore.
+Output of this algorithm is list of coarse pattern with its snippet (i.e.
+$P_{1}\rightarrow P_{7}\rightarrow P_{9}$), group (i.e.
+$G_{1}\rightarrow G_{2}\rightarrow G_{3}$), and pattern length (i.e.
+3).
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=1.0\linewidth]{mining_coarse_pattern}
+	\caption{Mining coarse pattern algorithm}
+	\label{fig:mining-coarse-pattern}
+\end{figure}
+
+\subsubsection{Finding Fine-Grained Pattern}
+The result of coarse pattern has satisfy support threshold $\sigma$ and time constraint $\Delta t$.
+Next step is checking the spatial variance of place in each group category.
+For example, graph representation of coarse pattern is shown in Fig.
+\ref{fig:graph-coarse-pattern}.
+Spatial location of place $P_{5}$ with other place in group $G_{1}$ is to far.
+Therefore, we have to prune pattern $P_{5}\rightarrow P_{4}\rightarrow P_{6}$ from fine-grained pattern.
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=0.7\linewidth]{graph_coarse_pattern}
+	\caption{Graph representation of coarse pattern result}
+	\label{fig:graph-coarse-pattern}
+\end{figure}
+For finding fine-grained pattern, mean shift clustering algorithm is used because it does not need any prior knowledge and only use one parameter called bandwidth.
+Bandwidth parameter is used to limit the area of clustering.
+The main idea of mean shift algorithm is choosing random point as the center and use bandwidth to limit the coverage area of clustering.
+Then calculate mean shift vector to shift the center point toward new point that more dense than previous point.
 
 \section{Demonstration}
-This document is a
 
-\subsection{Dataset}
-This project will use the real dataset, 4SQ that collected from Foursquare check-in sequence in New York.
+\subsection{Database}
+This project will use the real database, 4SQ that collected from Foursquare check-in sequence in New York.
 It consists of 48564 places that divided into 417 place categories and it stored semantic trajectories from 14909 users.
-4SQ dataset provides 3 files:
+4SQ database provides 3 files:
 \begin{enumerate}
-\item \textit{Sequences}, it contains users semantic trajectories including attributes of check-in timestamp and place ID.
+\item \textit{Sequences}, it contains users semantic trajectories including attributes of check-in time-stamp and place ID.
 \item \textit{Places}, it contains information about the places (place ID, latitude, longitude, category ID).
@@
 We will re-implement the process of mining fine-grained pattern using java programing language.
-The user interface of program will be provided as shown in the Figure \ref{fig:UI}.
-Figure \ref{fig:javagui} shows the illustration of our program.
-There are an dataset input in csv format, 4 parameters input,  show button for showing graph representation like in the figure \ref{fig:graph}, and 3 button to start the process individually or start all of the process respectively.
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.5\linewidth]{GraphRepresentation}
-\caption{Graph illustration}
-\label{fig:graph}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.5\linewidth]{GUI}
-\caption{Program UI illustration}
-\label{fig:javagui}
-\end{figure}
-
-This document is a \cite{sdbproject}
-
-\section{Conclusion}
-This document is a \cite{zhang2014splitter}
+The user interface of program will be provided as shown in the Figure.
+Figure shows the illustration of our program.
+There are an database input in csv format, 4 parameters input,  show button for showing graph representation like in the figure, and 3 button to start the process individually or start all of the process respectively.
 

### 2018-12-24 paper.tex
paper progress 24

@@
 \usepackage{xcolor}
+\usepackage{subcaption}
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 	\includegraphics[width=1.0\linewidth]{mining_coarse_pattern}
-	\caption{Mining coarse pattern algorithm}
+	\caption{Mining coarse pattern algorithm \cite{zhang2014splitter}}
 	\label{fig:mining-coarse-pattern}
@@
 Therefore, we have to prune pattern $P_{5}\rightarrow P_{4}\rightarrow P_{6}$ from fine-grained pattern.
-\begin{figure}[!ht]
+
+\begin{figure}[!h]
 	\centering
@@
 \end{figure}
+
 For finding fine-grained pattern, mean shift clustering algorithm is used because it does not need any prior knowledge and only use one parameter called bandwidth.
@@
 Then calculate mean shift vector to shift the center point toward new point that more dense than previous point.
+For windows kernel, we use Epanechnikov kernel.
+\par
+Before clustering, we transform snippet in each coarse pattern into a 2k-dimensional point x by assembling the coordinates of each snippet.
+Then, the number of visitors is added to x as weight.
+Algorithm 2 shows how to cluster point using mean shift algorithm.
+Output of this algorithm is set of cluster.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=1.0\linewidth]{"algorithm weighted snippet"}
+	\caption{Weighted snippet shift algorithm \cite{zhang2014splitter}}
+	\label{fig:algorithm-weighted-snippet}
+\end{figure}
+Specify the best bandwidth size is not an easy task.
+If bandwidth is small, there will be many small snippet cluster that not exceed support threshold $\sigma$.
+On the other hand, large bandwidth make the large cluster that cannot satisfy variance threshold $rho$.
+Therefore, we have to start with large bandwidth then dampen it until no more pattern exist.
+For this problem, notion of $\gamma$-community is presented to reduce the cost of repeating the process in large cluster.
+$\gamma$-community can be defined as connected component between two cluster.
+Two cluster can be connected if distance between two cluster no more than $\gamma$.
+Fig.
+\ref{fig:lamda-community} shows the example of $\gamma$-community.
+\begin{figure}[!h]
+	\centering
+	\begin{subfigure}[b]{0.4\linewidth}
+		\includegraphics[width=\linewidth]{"cluster example"}
+		\caption{Snippet cluster}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.4\linewidth}
+		\includegraphics[width=\linewidth]{"lamda community"}
+		\caption{$\gamma$-community}
+	\end{subfigure}
+	\caption{Example of $\gamma$-community}
+	\label{fig:lamda-community}
+\end{figure}
+
+Algorithm 3 shows refine coarse pattern algorithm.
+First, we cluster snippet using weighted snippet shift with bandwidth h.
+For each cluster we check if the support is at least $sigma$ and the variance is no more than $rho$ then report as fine grained pattern and remove from cluster set.
+Set $\gamma$ as root 2 multiply by dampening factor and current bandwidth.
+Then construct set of $\gamma$-community from cluster S that are not reported as fine grained pattern.
+For each $\gamma$-community, check if the support is at least $sigma$ then repeat the process of refine coarse pattern algorithm.
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{"refine coarse"}
+	\caption{Refine coarse pattern algorithm \cite{zhang2014splitter}}
+	\label{fig:refine-coarse}
+\end{figure}
 
@@
 This project will use the real database, 4SQ that collected from Foursquare check-in sequence in New York.
-It consists of 48564 places that divided into 417 place categories and it stored semantic trajectories from 14909 users.
+It consists of 48564 places that divided into 417 place with list of categories and it stored semantic trajectories from 14909 users.
 4SQ database provides 3 files:
@@
 \item \textit{Sequences}, it contains users semantic trajectories including attributes of check-in time-stamp and place ID.
-\item \textit{Places}, it contains information about the places (place ID, latitude, longitude, category ID).
+\item \textit{Places}, it contains information about the places (place ID, latitude, longitude, list of category ID).
 \item \textit{Category}, it contains information of place category ID corresponding with its place category name.
@@
 
-\subsection{Result}
-We will re-implement the process of mining fine-grained pattern using java programing language.
-The user interface of program will be provided as shown in the Figure.
-Figure shows the illustration of our program.
-There are an database input in csv format, 4 parameters input,  show button for showing graph representation like in the figure, and 3 button to start the process individually or start all of the process respectively.
+\subsection{Implementation detail}
+We will re-implement the process of mining fine-grained pattern using Java programing language.
+For improving GUI performance, we use G4P library (http://www.lagers.org.uk/g4p/) that based on OpenGL and JavaFX rendering engines.
+The other purpose is to support geographical map visualization from unfolding library (http://unfoldingmaps.org/) that use OpenGL rendering engines.
+We also using other libraries such as apache commons (http://commons.apache.org) to support our program.
+\par 
+Input of our program is database file that will be used to build graph representation as our database in the system.
+This graph representation is based on adjacency list that is shown in \ref{fig:adjacency}.
+There are 4 object: database, trajectory, place, and category.
+Database object has list of trajectory that have id to represent people and have list of sequence to represent the movement.
+Each movement is a list of timestamped place that has information of place id, position, and category.
+In the next step, we implement mining coarse pattern algorithm and refine coarse pattern algorithm for finding fine-grained pattern from the database.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=0.7\linewidth]{adjacency}
+	\caption{Structure of database in adjacency list representation}
+	\label{fig:adjacency}
+\end{figure}
+
+The user interface of program will be provided as shown in the Fig.
+\ref{fig:visual}.
+The figure shows the illustration of our program.
+There are 3 database input in .csv format for category and place and .txt format for the sequence data.
+There are also have 6 input parameters in the configuration.
+Support threshold, pattern length, and time limit for mining coarse pattern, and variance threshold, dampening factor for refine the coarse pattern.
+In the first step, we have to create the database.
+After that,we can mine coarse first then perform refine coarse pattern or do both coarse pattern and refine coarse pattern respectively.
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=1\linewidth]{visual}
+	\caption{Visualization}
+	\label{fig:visual}
+\end{figure}
 

### 2018-12-24 GrainedPattern/src/Database/Item.java
first code

@@ -1,0 +1,45 @@
+package Database;
+
+
+public class Item {
+	// group Id
+	public int id = 0;
+
+	// raw place Id
+	private final int rawId;
+	public Place place;
+
+	public Item(int rawId) {
+		this.rawId = rawId;
+	}
+
+	public int getId() {
+		return id;
+	}
+
+	public int getRawId() {
+		return rawId;
+	}
+
+	public void setId(int id) {
+		this.id = id;
+	}
+	
+	public void view() {
+		System.out.print(",Gid:"+id+",Pid:"+rawId+")-");
+	}
+	
+	public int hashCode()
+	{
+		String string = ""+getId(); // This could be improved.
+		return string.hashCode();
+	}
+	
+	public boolean equals(Object object){
+		Item item = (Item) object;
+		if((item.getId() == this.getId())){
+			return true;
+		}
+		return false;
+	}
+}

### 2018-12-24 GrainedPattern/src/Database/Itemset.java

@@ -1,0 +1,94 @@
+package Database;
+
+import java.util.ArrayList;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+
+public class Itemset {
+	public final List<Item> items = new ArrayList<Item>(); // ordered list.
+
+	// a timestamp associated to this itemset
+	public double timestamp = 0;
+	
+	//=========================COnstructor=====================================
+	public Itemset(Item item){
+		addItem(item);
+	}
+	
+	public Itemset(){
+	}
+	
+	//=========================SeterGetter=====================================
+
+	public void addItem(Item value){
+			items.add(value);
+	}
+	
+	public void setItemIds(Places places) {
+		for(Item item: items) {
+			
+			int placeId = item.getRawId();
+			item.place = places.getPlace(placeId);
+			int groupId = places.getGroupIdForPlace( placeId );
+			item.setId( groupId );
+		}
+	}
+	
+//	public List<Item> getItems(){
+//		return items;
+//	}
+//	
+//	public Item get(int index){
+//		return items.get(index);
+//	}
+	
+	public void view() {
+		System.out.print("(t:"+timestamp);
+		for(Item t:items) {
+			t.view();
+//			System.out.print();
+		}
+	}
+	
+	public List<Item> getItems(){
+		return items;
+	}
+	
+	public int size(){
+		return items.size();
+	}
+
+	 
+	//coarse pattern
+	public Itemset cloneItemSetMinusItems(Map<Item, Set<Integer>> mapSequenceID, double minsuppRelatif) {
+		Itemset itemset = new Itemset();
+		itemset.timestamp = timestamp;
+		for(Item item : this.items){
+//			if(mapSequenceID.get(item)!=null) {
+				if(mapSequenceID.get(item).size() >= minsuppRelatif){
+					itemset.addItem(item);
+				}
+//			}
+
+		}
+		return itemset;
+	}
+	
+	//use by projected
+	public Item get(int index){
+		return items.get(index);
+	}
+	
+	public double getTimestamp() {
+		return timestamp;
+	}
+	
+	public Itemset cloneItemSet(){
+		Itemset itemset = new Itemset();
+		itemset.timestamp = timestamp;
+		itemset.getItems().addAll(items);
+		return itemset;
+	}
+	
+}

### 2018-12-24 GrainedPattern/src/Database/Place.java

@@ -1,0 +1,72 @@
+package Database;
+
+import java.util.List;
+
+public class Place {
+	private final int id;
+	private int groupId = 0;
+	private final double lat;
+	private final double lng;
+	private List<Integer> categories = null;
+	
+	public Place(int id, double lat, double lng, List<Integer> categories) {
+		this.id = id;
+		this.lat = lat;
+		this.lng = lng;
+		this.categories = categories;
+	}
+	
+	public int getGroupId() {
+		return groupId;
+	}
+	
+	public void setGroupId(int groupId) {
+		this.groupId = groupId;
+	}
+	
+	public int getMaxCategoryLevel() {
+		return categories.size() - 1;
+	}
+	
+	
+	public void view() {
+		System.out.print("("+id+","+groupId+","+lat+","+lng+"<");
+		for(Integer i:categories) {
+			System.out.print(i+"-");
+		}
+		System.out.print(">");
+	}
+	
+	// Get the category for requested level, level starts from 0
+	public int getCategory(int level) {
+		return categories.get( level );
+	}
+	
+	public List<Integer> getCategories() {
+		return categories;
+	}
+
+	public int getId() {
+		return id;
+	}
+
+	public double getLat() {
+		return lat;
+	}
+
+	public double getLng() {
+		return lng;
+	}
+
+	public void setCategories(List<Integer> categories) {
+		this.categories = categories;
+	}
+	
+	////////////////////////////////////////////////////////////////
+	public Place(double lat, double lng) {
+		this.id = -1;
+		this.lat = lat;
+		this.lng = lng;
+	}
+	
+}

### 2018-12-24 GrainedPattern/src/Database/Places.java

@@ -1,0 +1,79 @@
+package Database;
+
+import java.io.BufferedReader;
+import java.io.FileReader;
+import java.util.ArrayList;
+import java.util.List;
+
+public class Places {
+	public List<Place> places = new ArrayList<Place>();
+
+	/*
+	 * Load Places from data file
+	 */
+	
+	
+	public void loadFile(String filename) throws Exception {
+		BufferedReader br = new BufferedReader(new FileReader(filename));
+		while (true) {
+			String line = br.readLine();
+			if (line == null)
+				break;
+			addPlace(line.split(","));
+		}
+		br.close();
+	}
+	
+	
+	
+	public void addPlace(String[] placeAttributes) {
+		int id = Integer.parseInt(placeAttributes[0]); // place id
+		double lat = Double.parseDouble(placeAttributes[1]);
+		double lng = Double.parseDouble(placeAttributes[2]);
+
+		List<Integer> categories = new ArrayList<Integer>();
+		String[] integers = placeAttributes[placeAttributes.length - 1].split(" ");
+		for (String s : integers) {
+			int categoryId = Integer.parseInt(s);
+			categories.add(categoryId);
+		}
+
+		Place place = new Place(id, lat, lng, categories);
+
+		this.places.add(place);
+	}
+
+	public Place getPlace(int placeId) {
+		return places.get(placeId);
+	}
+	
+	/*
+	 * Get the group id a place belongs to.
+	 * */
+	public int getGroupIdForPlace(int placeId) {
+		return places.get(placeId).getGroupId();
+	}
+	
+	
+	public List<Place> getPlaces() {
+		return places;
+	}
+	
+	public void setPlaceGroupIds(Groups groups) {
+		for( Group group: groups.getGroups() ) {
+			int groupId = group.getId();
+			List<Integer> placeIds = group.getPlaceIds();
+			for(Integer placeId: placeIds) {
+				places.get(placeId).setGroupId(groupId);
+			}
+		}
+	}
+
+
+	public void view() {
+		for(Place c:places) {
+			c.view();
+			System.out.println();
+		}
+	}
+}

### 2018-12-24 GrainedPattern/src/Database/Sequence.java

@@ -1,0 +1,81 @@
+package Database;
+
+import java.util.ArrayList;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+
+public class Sequence {
+	public long shift = 0;
+	
+	public final List<Itemset> itemsets = new ArrayList<Itemset>();
+	public int id; // id de la sequence
+	
+//	// List of IDS of all patterns that contains this one.
+//	public Set<Integer> sequencesID = null;
+	// List of IDS of all patterns that contains this one. =====projected
+		private Set<Integer> sequencesID = null;
+	public Sequence(int id){
+		this.id = id;
+	}
+	
+	public void setItemIds(Places places) {
+		for(Itemset itemset: itemsets) {
+			itemset.setItemIds(places);
+		}
+	}
+	
+	public int getId() {
+		return id;
+	}
+	
+	public int size(){
+		return itemsets.size();
+	}
+	
+	public List<Itemset> getItemsets() {
+		return itemsets;
+	}
+	
+
+	public Sequence cloneSequenceMinusItems(Map<Item, Set<Integer>> mapSequenceID, double relativeMinSup) {
+		Sequence sequence = new Sequence(getId());
+		for(Itemset itemset : itemsets){
+			Itemset newItemset = itemset.cloneItemSetMinusItems(mapSequenceID, relativeMinSup);
+			if(newItemset.size() !=0){ 
+				sequence.itemsets.add(newItemset);
+			}
+		}
+		return sequence;
+	}
+	
+
+	public void addItemset(Itemset itemset) {
+		itemsets.add(itemset);
+	}
+	
+	
+	public void setSequencesID(Set<Integer> sequencesID) {
+		this.sequencesID = sequencesID;
+	}
+	
+	public void view() {
+		System.out.print("S id: " + id +" = ");
+		for(Itemset ts:itemsets) {
+			ts.view();
+		}
+	}
+	
+	//use by projectedDatabase
+	public Itemset get(int index) {
+		return itemsets.get(index);
+	}
+
+	public Sequence cloneSequence(){
+		Sequence sequence = new Sequence(getId());
+		for(Itemset itemset : itemsets){
+			sequence.addItemset(itemset.cloneItemSet());
+		}
+		return sequence;
+	}
+}

### 2018-12-24 GrainedPattern/src/NDatabase/NCategory.java

@@ -1,0 +1,31 @@
+package NDatabase;
+
+public class NCategory {
+	public int categoryId;
+	public String categoryName;
+	
+	
+	public NCategory(int categoryId, String categoryName) {
+		super();
+		this.categoryId = categoryId;
+		this.categoryName = categoryName;
+	}
+	
+	public int getCategoryId() {
+		return categoryId;
+	}
+	public void setCategoryId(int categoryId) {
+		this.categoryId = categoryId;
+	}
+	public String getCategoryName() {
+		return categoryName;
+	}
+	public void setCategoryName(String categoryName) {
+		this.categoryName = categoryName;
+	}
+	
+	public void view() {
+		System.out.print("Gid:"+ categoryId);
+		
+	}
+}

### 2018-12-24 GrainedPattern/src/NDatabase/NDatabase.java

@@ -1,0 +1,209 @@
+package NDatabase;
+
+import java.awt.CheckboxGroup;
+import java.io.BufferedReader;
+import java.io.FileReader;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.HashMap;
+import java.util.LinkedHashSet;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+import java.util.stream.Collectors;
+import java.util.Map.Entry;
+
+public class NDatabase {
+
+	public List<NTrajectory> trajectories = new ArrayList<NTrajectory>();
+	// temporal
+	Map<Integer, String> tempCategory = new HashMap<Integer, String>();
+	Map<Integer, NPlace> tempPlace = new HashMap<Integer, NPlace>();
+	Map<Integer, List<Integer>> group = new HashMap<Integer, List<Integer>>();
+	public List<String> groupName = new ArrayList<String>();
+	public List<NTrajectory> getTrajectories() {
+		return trajectories;
+	}
+
+	public void createDatabase(String category, String place, String sequence) throws IOException {
+		readCategory(category);
+		readPlace(place);
+		readSequence(sequence);
+//		this.view();
+	}
+
+	// ==================================READ
+	// CATEGORY=====================================
+	// Read from csv file
+	public void readCategory(String category) throws IOException {
+		BufferedReader br = new BufferedReader(new FileReader(category));
+		try {
+			String line = br.readLine();
+			while (true) {
+				// note that csv file is separated by comma
+				processCategory(line.split(","));
+				line = br.readLine();
+				if (line == null)
+					break;
+			}
+		} finally {
+			br.close();
+		}
+	}
+
+	// set array value in variable tempCategory
+	public void processCategory(String[] category) {
+		// read first column as category id;
+		int categoryid = Integer.parseInt(category[0]);
+		// read second column as category name;
+		String categoryName = category[1];
+		tempCategory.put(categoryid, categoryName);
+	}
+
+	// =======================================READ
+	// PLACE================================
+	// read csv file
+	public void readPlace(String place) throws IOException {
+		BufferedReader br = new BufferedReader(new FileReader(place));
+		try {
+			String line = br.readLine();
+			while (true) {
+				// note that csv file is separated by comma
[…]

### 2018-12-24 GrainedPattern/src/NDatabase/NPlace.java

@@ -1,0 +1,64 @@
+package NDatabase;
+
+
+public class NPlace {
+	public int placeId;
+	public double lat;
+	public double lng;
+	public NCategory category;
+	
+	public NPlace(int placeId, double lat, double lng, NCategory category) {
+		super();
+		this.placeId = placeId;
+		this.lat = lat;
+		this.lng = lng;
+		this.category = category;
+	}
+	
+	public int getPlaceId() {
+		return placeId;
+	}
+	public void setPlaceId(int placeId) {
+		this.placeId = placeId;
+	}
+	public double getLat() {
+		return lat;
+	}
+	public void setLat(double lat) {
+		this.lat = lat;
+	}
+	public double getLng() {
+		return lng;
+	}
+	public void setLng(double lng) {
+		this.lng = lng;
+	}
+
+	public NCategory getCategory() {
+		return category;
+	}
+	public void setCategory(NCategory category) {
+		this.category = category;
+	}
+	
+	public void view() {
+		System.out.print("Pid:"+ this.placeId+",");
+		this.category.view();
+	}
+	
+	/////////////////////////////////
+	public NPlace(double lat, double lng) {
+		this.placeId = -1;
+		this.lat = lat;
+		this.lng = lng;
+	}
+	
+	@Override 
+	public boolean equals(Object object){
+		NPlace item = (NPlace) object;
+		if((item.placeId==placeId)){
+			return true;
+		}
+		return false;
+	}
+}

### 2018-12-24 GrainedPattern/src/NMeanshift/NDoubleDoubleVectorFunction.java

@@ -1,0 +1,16 @@
+package NMeanshift;
+
+/**
+ * A function that can be applied to two double vectors via {@link NDoubleVector}
+ * #apply({@link NDoubleVector} v, {@link NDoubleDoubleVectorFunction} f);
+ * 
+ */
+public interface NDoubleDoubleVectorFunction {
+
+  /**
+   * Calculates the result of the left and right value of two vectors at a given
+   * index.
+   */
+  public double calculate(int index, double left, double right);
+
+}

### 2018-12-24 GrainedPattern/src/NMeanshift/NDoubleVectorFunction.java

@@ -1,0 +1,14 @@
+package NMeanshift;
+
+/**
+ * A function that can be applied to a double vector via {@link NDoubleVector}
+ * #apply({@link NDoubleVectorFunction} f);
+ */
+public interface NDoubleVectorFunction {
+
+  /**
+   * Calculates the result with a given index and value of a vector.
+   */
+  public double calculate(int index, double value);
+
+}

### 2018-12-24 GrainedPattern/src/NMeanshift/NEuclidianDistance.java

@@ -1,0 +1,40 @@
+package NMeanshift;
+
+import org.apache.commons.math3.util.FastMath;
+
+public final class NEuclidianDistance implements NDistanceMeasurer {
+
+  private static final NEuclidianDistance DISTANCE = new NEuclidianDistance();
+
+  @Override
+  public double measureDistance(double[] set1, double[] set2) {
+    double sum = 0;
+    int length = set1.length;
+    for (int i = 0; i < length; i++) {
+      double diff = set2[i] - set1[i];
+      // multiplication is faster than Math.pow() for ^2.
+      sum += (diff * diff);
+    }
+
+    return FastMath.sqrt(sum);
+  }
+
+  @Override
+  public double measureDistance(NDoubleVector vec1, NDoubleVector vec2) {
+    if (vec1.isSparse() || vec2.isSparse()) {
+      return FastMath.sqrt(vec2.subtract(vec1).pow(2).sum());
+    } else {
+      // dense vectors usually doesn't do a defensive copy, so it is faster than
+      // the implementation above.
+      return measureDistance(vec1.toArray(), vec2.toArray());
+    }
+  }
+
+  /**
+   * @return a cached euclidian distance measurer.
+   */
+  public static NEuclidianDistance get() {
+    return DISTANCE;
+  }
+
+}

### 2018-12-24 GrainedPattern/src/NMeanshift/NGroupSequence.java

@@ -1,0 +1,27 @@
+package NMeanshift;
+
+import java.util.ArrayList;
+import java.util.List;
+
+
+public class NGroupSequence {
+	List<NGroup> mGroups = new ArrayList<NGroup>();
+	int mSupport; //support: number of visitors
+	
+	public NGroupSequence() {
+	}
+	
+	public void addGroup(NGroup g) {
+		mGroups.add( g );
+	}
+	
+	public void setSupport(int support) {
+		mSupport = support;
+	}
+	
+	public void view() {
+		for (NGroup p:mGroups) {
+			p.view();
+		}
+	}
+}

### 2018-12-24 GrainedPattern/src/NMeanshift/NMeanShift.java

@@ -1,0 +1,204 @@
+package NMeanshift;
+
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
+
+import org.apache.commons.math3.util.FastMath;
+
+public class NMeanShift {
+
+	private final double SQRT_2_PI = FastMath.sqrt(2 * Math.PI);
+
+	int maxIteration = 100;
+	double bandwidth = 0.01;
+	double mergeWindow = 0.001;
+	List<Integer> weights = null; // weights of points
+	List<NDoubleVector> points = null; 
+	List<NDoubleVector> centers = null;
+	boolean[] converged = null;
+	int[] designation = null;
+
+	public List<NDoubleVector> cluster(List<NDoubleVector> points, List<Integer> weights,
+			double bandwidth, double mergeWindow, int maxIterations) {
+
+		initialize(points, weights, maxIterations, bandwidth, mergeWindow);
+
+		// now iterate over all centers
+		for (int i = 0; i < maxIterations; i++) {
+			// return the number of centers that have not converged yet
+			int remainingConvergence = meanShift();
+			// merge if centers are within the mergeWindow
+
+			if (remainingConvergence == 0) {
+				break;
+			}
+		}
+		assign();
+		return centers;
+	}
+	
+	//get clusters from designation
+	public Map<Integer, List<Integer>> getClusters() {
+		Map<Integer, List<Integer>> clusters = new HashMap<Integer, List<Integer>>(); 
+		//key:cluster id, value:list of members
+		for(int i=0; i<designation.length; i++) {
+			int clusterID = designation[i];
+			if ( clusters.containsKey(clusterID) ) {
+				clusters.get( clusterID ).add(i);
+			} else {
+				List<Integer> newCluster = new ArrayList<Integer>();
+				newCluster.add( i );
+				clusters.put( clusterID, newCluster );
+			}
+		}
+		return clusters;
+	}
+	
+	public int[] getDesignation() {
+		return designation;
+	}
+	
+	
+	/*
+	 * 
+	 * */
+	private void initialize(List<NDoubleVector> points, List<Integer> weights, int maxIteration,
+			double bandwidth, double mergeWindow) {
+
+		this.maxIteration = maxIteration;
+		this.bandwidth = bandwidth;
+		this.mergeWindow = mergeWindow;
+
+		this.points = points;
+		this.weights = weights;
+		findInitialCenters();
+
+		this.converged = new boolean[points.size()];
[…]

### 2018-12-24 GrainedPattern/src/NMeanshift/NMeanshiftAlgo.java

@@ -1,0 +1,146 @@
+package NMeanshift;
+
+import java.util.ArrayList;
+import java.util.Iterator;
+import java.util.List;
+import java.util.Map;
+
+import NDatabase.NDatabase;
+import NDatabase.NPlace;
+import NPrefixspan.NSnippet;
+import NPrefixspan.NSnippetCluster;
+import Refine.MeanShift;
+import coarsepattern.Snippet;
+import coarsepattern.SnippetCluster;
+
+public class NMeanshiftAlgo {
+	double mSupThreshold; // support threshold
+	double mVarThreshold; // variance threshold
+	double mTau; // dampening factor
+	double bandwidth;
+
+	double mMergeWindow = 2e-3;
+	int mMaxIter = 100; // max iteration for mean shift
+
+	int mSnippetLength = 1;
+	NDatabase database = null;
+	List<NSnippetCluster> patternList = null; // result sequential patterns
+
+	public List<NSnippetCluster> getPatterns() {
+		return patternList;
+	}
+	
+	
+	public NMeanshiftAlgo(double mSupThreshold, double mVarThreshold, double mTau, double bandwidth, NDatabase d) {
+		super();
+		this.mSupThreshold = mSupThreshold;
+		this.mVarThreshold = mVarThreshold;
+		this.mTau = mTau;
+		this.bandwidth = bandwidth;
+		this.database = d;
+	}
+
+	public void minePatterns(int snippetLength, List<NSnippet> snippets) {
+		patternList = new ArrayList<NSnippetCluster>();
+		mSnippetLength = snippetLength;
+		mMergeWindow = computeDimensionInvariant(snippetLength, mMergeWindow);
+		double dimensionInvariantBandwidth = computeDimensionInvariant(snippetLength, bandwidth);
+//		System.out.println(mSnippetLength);
+//		System.out.println(mMergeWindow);
+//		System.out.println(dimensionInvariantBandwidth);
+		splitPatternWithPruning(snippets,dimensionInvariantBandwidth);
+	}
+
+	private void splitPatternWithPruning(List<NSnippet> snippets,double bandwidth) {
+		if (bandwidth < 1e-3)
+			return;
+
+		List<NSnippetCluster> snippetClusters = cluster(snippets,bandwidth);
+
+		
+		for (NSnippetCluster sc : snippetClusters) {
+			if (sc.computeSuppport() >= mSupThreshold && sc.computeVariance(database) <= mVarThreshold) {
+				patternList.add(sc);
[…]

### 2018-12-24 GrainedPattern/src/NPrefixspan/NPrefixspanAlgo.java

@@ -1,0 +1,228 @@
+package NPrefixspan;
+
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+import java.util.Map.Entry;
+
+import Database.Item;
+import Database.Itemset;
+import NDatabase.NDatabase;
+import NDatabase.NPlace;
+import NDatabase.NSequence;
+import NDatabase.NTrajectory;
+import coarsepattern.ProjectedSequence;
+import coarsepattern.Snippet;
+import coarsepattern.SnippetCluster;
+
+public class NPrefixspanAlgo {
+	// The sequential patterns that are found
+//	private NSequence patterns = null;
+	private List<NSnippetCluster> results = null;
+	int patternlength;
+
+	// minimum support
+	private double minsup;
+	private int maxInterval;
+	// absolute value of minimum support
+	private int minsuppRelative;
+
+	public NPrefixspanAlgo(double minsup, int maxInterval,int patternlength) {
+		this.minsup = minsup;
+		this.maxInterval = maxInterval;
+		this.patternlength = patternlength;
+	}
+
+	public void runAlgorithm(NDatabase database) {
+//		patterns = new Sequences("FREQUENT SEQUENTIAL PATTERNS");
+		results = new ArrayList<NSnippetCluster>();
+		this.minsuppRelative = (int) minsup;
+		if (this.minsuppRelative == 0) { // protection
+			this.minsuppRelative = 1;
+		}
+
+		InitialProjection(database);
+	}
+
+	public void InitialProjection(NDatabase d) {
+		Map<NSequence, Set<Integer>> frequent = getFrequentItem(d);
+//		for(Entry<NSequence, Set<Integer>> entry : frequent.entrySet()){
+//			entry.getKey().view();
+//			System.out.println();
+//		}
+//		
+		for(Entry<NSequence, Set<Integer>> entry : frequent.entrySet()){
+			if(entry.getValue().size() >= this.minsuppRelative){
+				// build the projected context
+				NSequence item = entry.getKey();
+				NSequence newItem = new NSequence();
+				newItem.place=item.place;
+				newItem.time=item.time;
+				newItem.pattern.add(item.place);
+				NProjectedDatabase S = new NProjectedDatabase();
[…]

### 2018-12-24 GrainedPattern/src/NPrefixspan/NSnippetCluster.java

@@ -1,0 +1,96 @@
+package NPrefixspan;
+
+import java.util.ArrayList;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Set;
+
+import Database.Group;
+import Database.Place;
+import Database.Places;
+import NDatabase.NDatabase;
+import NMeanshift.NGroup;
+import NMeanshift.NGroupSequence;
+import coarsepattern.GroupSequence;
+import coarsepattern.Snippet;
+
+public class NSnippetCluster {
+	int mSnippetLength; //snippetLength
+	List<NSnippet> mSnippets; // all the snippets must have the same length
+	public List<Integer> mGroupSequence; // a sequence of group ID, the coarse pattern
+
+	public NSnippetCluster() {
+		mSnippets = new ArrayList<NSnippet>();
+		mGroupSequence = new ArrayList<Integer>();
+	}
+
+	public int getSnippetLength() {
+		return mGroupSequence.size();
+	}
+
+	public List<NSnippet> getSnippet() {
+		return mSnippets;
+	}
+
+	public void view() {
+//		System.out.println("Snipptet ");
+		for (NSnippet s : mSnippets) {
+			s.view();
+		}
+		System.out.print("MGroub ");
+		for (Integer i : mGroupSequence) {
+			System.out.print(i + " - ");
+		}
+//		System.out.println();
+		System.out.println();
+	}
+
+	////////////////////////////////////////////////////
+
+	// transform a snippet cluster into a group sequence
+	public NGroupSequence toGroupSequence() {
+		NGroupSequence gs = new NGroupSequence();
+		for (int i = 0; i <mSnippetLength; i++) {
+			NGroup g = constructGroup(i);
+			gs.addGroup(g);
+		}
+		gs.setSupport( computeSuppport() );
+		return gs;
+	}
+
+	private NGroup constructGroup(int position) {
+		NGroup group = new NGroup(); // group id: -1, a pseudo group
+		for (NSnippet snippet : mSnippets)
+			group.placeIds.add(snippet.mPlaceSequence.get(position).placeId);
+		return group;
+	}
+
+	public void addSnippet(NSnippet snippet) {
+		mSnippets.add(snippet);
+	}
+
+	// support of snippets
+	public int computeSuppport() {
+		Set<Integer> visitors = new HashSet<Integer>();
+		for (NSnippet snippet : mSnippets)
+			visitors.addAll(snippet.mVisitors);
[…]

### 2018-12-24 GrainedPattern/src/Refine/DoubleVectorFunction.java

@@ -1,0 +1,14 @@
+package Refine;
+
+/**
+ * A function that can be applied to a double vector via {@link DoubleVector}
+ * #apply({@link DoubleVectorFunction} f);
+ */
+public interface DoubleVectorFunction {
+
+  /**
+   * Calculates the result with a given index and value of a vector.
+   */
+  public double calculate(int index, double value);
+
+}

### 2018-12-24 GrainedPattern/src/Refine/MeanShift.java

@@ -1,0 +1,204 @@
+package Refine;
+
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.HashMap;
+import java.util.List;
+import java.util.Map;
+
+import org.apache.commons.math3.util.FastMath;
+
+public class MeanShift {
+
+	private final double SQRT_2_PI = FastMath.sqrt(2 * Math.PI);
+
+	int maxIteration = 100;
+	double bandwidth = 0.01;
+	double mergeWindow = 0.001;
+	List<Integer> weights = null; // weights of points
+	List<DoubleVector> points = null; 
+	List<DoubleVector> centers = null;
+	boolean[] converged = null;
+	int[] designation = null;
+
+	public List<DoubleVector> cluster(List<DoubleVector> points, List<Integer> weights,
+			double bandwidth, double mergeWindow, int maxIterations) {
+
+		initialize(points, weights, maxIterations, bandwidth, mergeWindow);
+
+		// now iterate over all centers
+		for (int i = 0; i < maxIterations; i++) {
+			// return the number of centers that have not converged yet
+			int remainingConvergence = meanShift();
+			// merge if centers are within the mergeWindow
+
+			if (remainingConvergence == 0) {
+				break;
+			}
+		}
+		assign();
+		return centers;
+	}
+	
+	//get clusters from designation
+	public Map<Integer, List<Integer>> getClusters() {
+		Map<Integer, List<Integer>> clusters = new HashMap<Integer, List<Integer>>(); 
+		//key:cluster id, value:list of members
+		for(int i=0; i<designation.length; i++) {
+			int clusterID = designation[i];
+			if ( clusters.containsKey(clusterID) ) {
+				clusters.get( clusterID ).add(i);
+			} else {
+				List<Integer> newCluster = new ArrayList<Integer>();
+				newCluster.add( i );
+				clusters.put( clusterID, newCluster );
+			}
+		}
+		return clusters;
+	}
+	
+	public int[] getDesignation() {
+		return designation;
+	}
+	
+	
+	/*
+	 * 
+	 * */
+	private void initialize(List<DoubleVector> points, List<Integer> weights, int maxIteration,
+			double bandwidth, double mergeWindow) {
+
+		this.maxIteration = maxIteration;
+		this.bandwidth = bandwidth;
+		this.mergeWindow = mergeWindow;
+
+		this.points = points;
+		this.weights = weights;
+		findInitialCenters();
+
+		this.converged = new boolean[points.size()];
+		Arrays.fill(this.converged, false);
+
[…]

### 2018-12-24 GrainedPattern/src/coarsepattern/ProjectedDatabase.java

@@ -1,0 +1,26 @@
+package coarsepattern;
+
+import java.util.ArrayList;
+import java.util.List;
+
+public class ProjectedDatabase {
+	private List<ProjectedSequence> pseudoSequences = new ArrayList<ProjectedSequence>();
+
+	
+	public List<ProjectedSequence> getPseudoSequences(){
+		return pseudoSequences;
+	}
+	
+	
+	public void addSequence(ProjectedSequence newSequence) {
+		pseudoSequences.add(newSequence);
+		
+	}
+	
+	public void view() {
+		for (ProjectedSequence r:pseudoSequences) {
+			r.view();
+			System.out.println();
+		}
+	}
+}

### 2018-12-24 GrainedPattern/src/coarsepattern/ProjectedSequence.java

@@ -1,0 +1,118 @@
+package coarsepattern;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import Database.Item;
+import Database.Itemset;
+import Database.Sequence;
+
+public class ProjectedSequence {
+	private Sequence sequence;
+	private int firstItemset;
+	private int firstItem;
+	private int lastItemset;
+	private int lastItem;
+	private double prevtimestamp;
+	private List<Itemset> previtemset = new ArrayList<Itemset>();
+	
+	public void view() {
+		sequence.view();
+		System.out.print(firstItemset+","+firstItem+","+lastItemset+","+lastItem+","+prevtimestamp);
+	}
+	
+	public  ProjectedSequence(long decalageTemps, Sequence sequence, int indexItemset, int indexItem, double prevtimestamp){
+		this.sequence = sequence;
+		this.firstItemset = indexItemset;
+		this.firstItem = indexItem;
+		// Last itemset and item  (by default, this is the last item & itemset of the sequence.
+		this.lastItemset = sequence.itemsets.size()-1;
+		this.lastItem = sequence.getItemsets().get(lastItemset).items.size()-1;
+		this.prevtimestamp = prevtimestamp;
+		this.previtemset = new ArrayList<Itemset>();
+	}
+	
+	
+	public ProjectedSequence(ProjectedSequence sequence, int indexItemset, int indexItem, double prevtimestamp){
+
+		this.sequence = sequence.sequence;
+		this.firstItemset = indexItemset + sequence.firstItemset;
+		if(this.firstItemset == sequence.firstItemset){
+			this.firstItem = indexItem + sequence.firstItem;
+		}else{
+			this.firstItem = indexItem; // 
+		}
+		this.lastItemset = sequence.lastItemset;
+		this.lastItem = sequence.lastItem;
+		this.prevtimestamp = prevtimestamp;
+		this.previtemset = new ArrayList<Itemset>();
+		for (Itemset copy : sequence.previtemset){
+			this.previtemset.add(copy);
+		}
+	}
+	
+	public int size(){
+		int size = sequence.size() - firstItemset - ((sequence.size()-1) - lastItemset);
+		if(size == 1 && sequence.getItemsets().get(firstItemset).size() == 0){
+			return 0;
+		}
+		return size;
+	}
+	
+	public int indexOf(int indexItemset, int idItem) {
[…]

### 2018-12-24 GrainedPattern/src/coarsepattern/Snippet.java

@@ -1,0 +1,66 @@
+package coarsepattern;
+
+import java.util.ArrayList;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Set;
+
+import Database.Place;
+import Database.Places;
+import Refine.DenseDoubleVector;
+import Refine.DoubleVector;
+
+public class Snippet {
+	private List<Integer> mPlaceSequence = new ArrayList<Integer>();
+	private Set<Integer> mVisitors= new HashSet<Integer>();
+	private int mLength;
+	private int mWeight; //number of visitors
+	
+	public Snippet(List<Integer> places, Set<Integer> visitors) {
+		mPlaceSequence = places;
+		mVisitors = visitors;
+		mLength = mPlaceSequence.size();
+		mWeight = mVisitors.size() ;
+	} 
+	
+	public int getPlace(int position) {
+		return mPlaceSequence.get( position );
+	}
+	
+	public List<Integer> getPlaceSequence(){
+		return mPlaceSequence;
+	}
+	
+	public Set<Integer> getVisitors() {
+		return mVisitors;
+	}
+	
+	public int getWeight() {
+		return mWeight;
+	}
+	
+	public void view() {
+		System.out.print("mPlaceSeq : ");
+		for(Integer i : mPlaceSequence) {
+			System.out.print(i +" - ");
+		}
+		System.out.println();
+		System.out.print("mVisitor : ");
+		for(Integer i : mVisitors) {
+			System.out.print(i +" - ");
+		}
+		System.out.println();
+	}
+	
+	//////////////////////////////////////////////////////////////
+	public DoubleVector toDoubleVector(Places places) {
+		double[] coordinates = new double[ 2 * mLength ];
+		for(int i=0; i<mPlaceSequence.size(); i++) {
+			int placeId = mPlaceSequence.get( i );
+			Place place = places.getPlace( placeId );
+			coordinates[ 2*i ] = place.getLat();
+			coordinates[ 2*i+1 ] = place.getLng();
+		}
+		return new DenseDoubleVector( coordinates );
+	}
+}

### 2018-12-24 paper.tex
Fix Code

@@
 
+\subsection{Experiment}
+Experiment is conducted in windows 10 Pro 64-bit running on Processor Intel Core I5 7500 @3.40GHz, 4GB of RAM, and Intel HD Graphics 630.
+First, we choose database file and fill the input parameters support threshold 100, variance threshold 0.0004, time constraint 120, dampening factor 0.8, Bandwidth 0.02, and minimum pattern length 2.
+In this application, minimum pattern length is used to set the minimum length of pattern when mining coarse pattern.
+Secondly, We create the database by pushing create database button.
+Before, pushing the button, we decided to uncheck show trajectory radio button because it decrease the performance when creating line marker in map.
+In this function, it also searching the number of category that exist in the database.
+From 48.564 of distinct places, we get 15 categories.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.7\linewidth]{mapDatabase}
+	\caption{}
+	\label{fig:mapdatabase}
+\end{figure}
+
+After creating database, we run prefix span algorithm for mining coarse pattern.
+In this process, we get places that occurs in the coarse pattern is 23264.
+It means that we reduce places up to half of places from the original database.
+The running time of mining coarse pattern is 3.685 seconds.
+Therefore, prefixspan algorithm is fast enough to finding a pattern in a database.
+Coarse pattern found from the database is 127 which consist of pattern length 2 (109 patterns) and pattern length 3 (18 patterns).
+The highest support or number of trajectory that using this pattern in the length of 2 is shop -> food which contains 2905 of trajectory.
+For the pattern length of 3, the highest support is food -> shop -> food which used by 299 of trajectory.
+From this result we can assume that a lot of people like to go the food area then go shopping then go to the another food area.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{mapCoarse}
+	\caption{}
+	\label{fig:mapcoarse}
+\end{figure}
+
 \section*{Acknowledgment}

### 2018-12-24 GrainedPattern/src/Database/Group.java

@@ -1,102 +1,0 @@
-package Database;
-
-import java.util.ArrayList;
-import java.util.HashMap;
-import java.util.Iterator;
-import java.util.List;
-import java.util.Map;
-
-public class Group {
-	private int id; // group id, starting from 0
-
-	static int mToAssignGroupId = 0;
-	
-	private List<Integer> placeIds = null;
-	
-	public Group() {
-		this.id = mToAssignGroupId++;
-		this.placeIds = new ArrayList<Integer>();
-	}
-	
-	public void addPlace(int i) {
-		this.placeIds.add(i);
-	}
-	
-	public int getId() {
-		return id;
-	}
-
-	public List<Integer> getPlaceIds() {
-		return placeIds;
-	}
-	
-	/*
-	 * Split all groups by the categories of places.
-	 */
-	public List<Group> splitByCategory(Places places, int level) {
-		Map<Integer, Group> subgroups = new HashMap<Integer, Group>();
-		for (Integer placeId : placeIds) {
-			Place place = places.getPlace(placeId);
-			int categoryId = getCategoryId(place, level);
-			if (subgroups.containsKey(categoryId)) {
-				subgroups.get(categoryId).addPlace(placeId);
-			} else {
-				Group newGroup = new Group();
-				newGroup.addPlace(placeId);
-				subgroups.put(categoryId, newGroup);
-			}
-		}
-		return new ArrayList<Group>(subgroups.values());
-//		return convertToList(subgroups);
-	}
-	
-	private List<Group> convertToList(Map<Integer, Group> map) {
-		List<Group> result = new ArrayList<Group>();
-		Iterator iter = map.entrySet().iterator();
-		while (iter.hasNext()) {
-			Map.Entry entry = (Map.Entry) iter.next();
-			result.add((Group) entry.getValue());
-		}
-		return result;
-	}
-	
-	private int getCategoryId(Place place, int level) {
-		int maxLevel = place.getMaxCategoryLevel();
-		int possibleLevel = level < maxLevel ? level : maxLevel;
-		return place.getCategory(possibleLevel);
-	}
-	
-	public void view() {
-		System.out.println();
-		System.out.println("Id : "+this.id);
-		System.out.println(this.mToAssignGroupId);
-		for(Integer i:this.placeIds) {
-			System.out.print(i);
-		}
-	}
-	
-	//////////////////////////////////////////////////////////////////
-	public double getVariance(Places places) {
[…]

### 2018-12-24 GrainedPattern/src/Database/Groups.java

@@ -1,43 +1,0 @@
-package Database;
-
-import java.util.ArrayList;
-import java.util.List;
-
-public class Groups {
-	List<Group> groups = null;
-
-	public Groups() {
-		this.groups = new ArrayList<Group>();
-	}
-
-	public Groups(List<Group> groups) {
-		this.groups = groups;
-	}
-
-	public void addGroup(Group p) {
-		groups.add(p);
-	}
-
-	public List<Group> getGroups() {
-		return groups;
-	}
-	
-	// current level when drilling down the category tree
-	public void splitByCategory(Places places, int level) {
-		List<Group> newGroups = new ArrayList<Group>();
-		int groupNum = groups.size(); // original number of groups.
-		for (int i = 0; i < groupNum; i++) {
-			Group group = groups.get(i);
-			List<Group> subgroups = group.splitByCategory(places, level);
-			newGroups.addAll(subgroups);
-		}
-		this.groups = newGroups;
-
-	}
-	
-	public void view() {
-		for(Group g:this.groups) {
-			g.view();
-		}
-	}
-}

### 2018-12-24 GrainedPattern/src/Database/Item.java

@@ -1,45 +1,0 @@
-package Database;
-
-
-public class Item {
-	// group Id
-	public int id = 0;
-
-	// raw place Id
-	private final int rawId;
-	public Place place;
-
-	public Item(int rawId) {
-		this.rawId = rawId;
-	}
-
-	public int getId() {
-		return id;
-	}
-
-	public int getRawId() {
-		return rawId;
-	}
-
-	public void setId(int id) {
-		this.id = id;
-	}
-	
-	public void view() {
-		System.out.print(",Gid:"+id+",Pid:"+rawId+")-");
-	}
-	
-	public int hashCode()
-	{
-		String string = ""+getId(); // This could be improved.
-		return string.hashCode();
-	}
-	
-	public boolean equals(Object object){
-		Item item = (Item) object;
-		if((item.getId() == this.getId())){
-			return true;
-		}
-		return false;
-	}
-}

### 2018-12-24 GrainedPattern/src/Database/Itemset.java

@@ -1,94 +1,0 @@
-package Database;
-
-import java.util.ArrayList;
-import java.util.List;
-import java.util.Map;
-import java.util.Set;
-
-public class Itemset {
-	public final List<Item> items = new ArrayList<Item>(); // ordered list.
-
-	// a timestamp associated to this itemset
-	public double timestamp = 0;
-	
-	//=========================COnstructor=====================================
-	public Itemset(Item item){
-		addItem(item);
-	}
-	
-	public Itemset(){
-	}
-	
-	//=========================SeterGetter=====================================
-
-	public void addItem(Item value){
-			items.add(value);
-	}
-	
-	public void setItemIds(Places places) {
-		for(Item item: items) {
-			
-			int placeId = item.getRawId();
-			item.place = places.getPlace(placeId);
-			int groupId = places.getGroupIdForPlace( placeId );
-			item.setId( groupId );
-		}
-	}
-	
-//	public List<Item> getItems(){
-//		return items;
-//	}
-//	
-//	public Item get(int index){
-//		return items.get(index);
-//	}
-	
-	public void view() {
-		System.out.print("(t:"+timestamp);
-		for(Item t:items) {
-			t.view();
-//			System.out.print();
-		}
-	}
-	
-	public List<Item> getItems(){
-		return items;
-	}
-	
-	public int size(){
-		return items.size();
-	}
-
-	 
-	//coarse pattern
-	public Itemset cloneItemSetMinusItems(Map<Item, Set<Integer>> mapSequenceID, double minsuppRelatif) {
-		Itemset itemset = new Itemset();
-		itemset.timestamp = timestamp;
-		for(Item item : this.items){
-//			if(mapSequenceID.get(item)!=null) {
-				if(mapSequenceID.get(item).size() >= minsuppRelatif){
-					itemset.addItem(item);
-				}
-//			}
-
-		}
-		return itemset;
-	}
-	
-	//use by projected
-	public Item get(int index){
-		return items.get(index);
-	}
-	
-	public double getTimestamp() {
-		return timestamp;
-	}
-	
-	public Itemset cloneItemSet(){
-		Itemset itemset = new Itemset();
-		itemset.timestamp = timestamp;
-		itemset.getItems().addAll(items);
-		return itemset;
-	}
-	
-}

### 2018-12-24 GrainedPattern/src/Database/Place.java

@@ -1,72 +1,0 @@
-package Database;
-
-import java.util.List;
-
-public class Place {
-	private final int id;
-	private int groupId = 0;
-	private final double lat;
-	private final double lng;
-	private List<Integer> categories = null;
-	
-	public Place(int id, double lat, double lng, List<Integer> categories) {
-		this.id = id;
-		this.lat = lat;
-		this.lng = lng;
-		this.categories = categories;
-	}
-	
-	public int getGroupId() {
-		return groupId;
-	}
-	
-	public void setGroupId(int groupId) {
-		this.groupId = groupId;
-	}
-	
-	public int getMaxCategoryLevel() {
-		return categories.size() - 1;
-	}
-	
-	
-	public void view() {
-		System.out.print("("+id+","+groupId+","+lat+","+lng+"<");
-		for(Integer i:categories) {
-			System.out.print(i+"-");
-		}
-		System.out.print(">");
-	}
-	
-	// Get the category for requested level, level starts from 0
-	public int getCategory(int level) {
-		return categories.get( level );
-	}
-	
-	public List<Integer> getCategories() {
-		return categories;
-	}
-
-	public int getId() {
-		return id;
-	}
-
-	public double getLat() {
-		return lat;
-	}
-
-	public double getLng() {
-		return lng;
-	}
-
-	public void setCategories(List<Integer> categories) {
-		this.categories = categories;
-	}
-	
-	////////////////////////////////////////////////////////////////
-	public Place(double lat, double lng) {
-		this.id = -1;
-		this.lat = lat;
-		this.lng = lng;
-	}
-	
-}

### 2018-12-24 GrainedPattern/src/Database/Places.java

@@ -1,79 +1,0 @@
-package Database;
-
-import java.io.BufferedReader;
-import java.io.FileReader;
-import java.util.ArrayList;
-import java.util.List;
-
-public class Places {
-	public List<Place> places = new ArrayList<Place>();
-
-	/*
-	 * Load Places from data file
-	 */
-	
-	
-	public void loadFile(String filename) throws Exception {
-		BufferedReader br = new BufferedReader(new FileReader(filename));
-		while (true) {
-			String line = br.readLine();
-			if (line == null)
-				break;
-			addPlace(line.split(","));
-		}
-		br.close();
-	}
-	
-	
-	
-	public void addPlace(String[] placeAttributes) {
-		int id = Integer.parseInt(placeAttributes[0]); // place id
-		double lat = Double.parseDouble(placeAttributes[1]);
-		double lng = Double.parseDouble(placeAttributes[2]);
-
-		List<Integer> categories = new ArrayList<Integer>();
-		String[] integers = placeAttributes[placeAttributes.length - 1].split(" ");
-		for (String s : integers) {
-			int categoryId = Integer.parseInt(s);
-			categories.add(categoryId);
-		}
-
-		Place place = new Place(id, lat, lng, categories);
-
-		this.places.add(place);
-	}
-
-	public Place getPlace(int placeId) {
-		return places.get(placeId);
-	}
-	
-	/*
-	 * Get the group id a place belongs to.
-	 * */
-	public int getGroupIdForPlace(int placeId) {
-		return places.get(placeId).getGroupId();
-	}
-	
-	
-	public List<Place> getPlaces() {
-		return places;
-	}
-	
-	public void setPlaceGroupIds(Groups groups) {
-		for( Group group: groups.getGroups() ) {
-			int groupId = group.getId();
-			List<Integer> placeIds = group.getPlaceIds();
-			for(Integer placeId: placeIds) {
-				places.get(placeId).setGroupId(groupId);
-			}
-		}
-	}
-
-
-	public void view() {
-		for(Place c:places) {
-			c.view();
-			System.out.println();
-		}
-	}
-}

### 2018-12-24 GrainedPattern/src/Database/Sequence.java

@@ -1,81 +1,0 @@
-package Database;
-
-import java.util.ArrayList;
-import java.util.List;
-import java.util.Map;
-import java.util.Set;
-
-public class Sequence {
-	public long shift = 0;
-	
-	public final List<Itemset> itemsets = new ArrayList<Itemset>();
-	public int id; // id de la sequence
-	
-//	// List of IDS of all patterns that contains this one.
-//	public Set<Integer> sequencesID = null;
-	// List of IDS of all patterns that contains this one. =====projected
-		private Set<Integer> sequencesID = null;
-	public Sequence(int id){
-		this.id = id;
-	}
-	
-	public void setItemIds(Places places) {
-		for(Itemset itemset: itemsets) {
-			itemset.setItemIds(places);
-		}
-	}
-	
-	public int getId() {
-		return id;
-	}
-	
-	public int size(){
-		return itemsets.size();
-	}
-	
-	public List<Itemset> getItemsets() {
-		return itemsets;
-	}
-	
-
-	public Sequence cloneSequenceMinusItems(Map<Item, Set<Integer>> mapSequenceID, double relativeMinSup) {
-		Sequence sequence = new Sequence(getId());
-		for(Itemset itemset : itemsets){
-			Itemset newItemset = itemset.cloneItemSetMinusItems(mapSequenceID, relativeMinSup);
-			if(newItemset.size() !=0){ 
-				sequence.itemsets.add(newItemset);
-			}
-		}
-		return sequence;
-	}
-	
-
-	public void addItemset(Itemset itemset) {
-		itemsets.add(itemset);
-	}
-	
-	
-	public void setSequencesID(Set<Integer> sequencesID) {
-		this.sequencesID = sequencesID;
-	}
-	
-	public void view() {
-		System.out.print("S id: " + id +" = ");
-		for(Itemset ts:itemsets) {
-			ts.view();
-		}
-	}
-	
-	//use by projectedDatabase
-	public Itemset get(int index) {
-		return itemsets.get(index);
-	}
-
-	public Sequence cloneSequence(){
-		Sequence sequence = new Sequence(getId());
-		for(Itemset itemset : itemsets){
-			sequence.addItemset(itemset.cloneItemSet());
-		}
-		return sequence;
-	}
-}

### 2018-12-24 GrainedPattern/src/Database/SequenceDatabase.java

@@ -1,95 +1,0 @@
-package Database;
-
-import java.io.BufferedReader;
-import java.io.FileReader;
-import java.io.IOException;
-import java.util.ArrayList;
-import java.util.List;
-
-public class SequenceDatabase {
-	// List of sequences
-	private final List<Sequence> sequences = new ArrayList<Sequence>();
-
-	public List<Sequence> getSequences() {
-		return sequences;
-	}
-	
-	public void setItemIds(Places places) {
-		for(Sequence s: sequences) {
-			s.setItemIds(places);
-		}
-	}
-
-	public void loadFile(String path) throws IOException {
-
-		String thisLine;
-		BufferedReader br = new BufferedReader(new FileReader(path));
-		try {
-			String line = br.readLine();
-			while (line != null) {
-				// note that sequence file is separated by empty string
-				processSequence(line.split(" "));
-				line = br.readLine();
-			}
-		} finally {
-			br.close();
-		}
-	}
-
-	/**
-	 * Process a line from the input file, splitted into tokens.
-	 * 
-	 * @param tokens a list of tokens (String).
-	 */
-	void processSequence(String[] tokens) { //
-		// create a new Sequence
-		Sequence sequence = new Sequence(sequences.size());
-		// Create an itemset that will be used to store items
-		// from the first itemset and eventually the next itemsets.
-		Itemset itemset = new Itemset();
-		// for each tokens
-		for (String integer : tokens) {
-			// if this token is a timestamp
-			if (integer.codePointAt(0) == '<') {
-				// we extract the timestamp and set it as the timestamp
-				// of the current itemset
-				String value = integer.substring(1, integer.length() - 1);
-//				System.out.println(value);
-				itemset.timestamp = Long.parseLong(value);
-			} else if (integer.equals("-1")) {
-				// If -1, this indicate the end of the current itemset,
-				// so we add the itemset to the sequence, and
-				// create a new itemset.
-				sequence.itemsets.add(itemset);
-				itemset = new Itemset();
-			} else if (integer.equals("-2")) {
-				// If -2, it indicates the end of a sequence
-				// If the last itemset is not empty, it means
-				// that a -1 was missing.
-				if (itemset.items.size() > 0) {
-					// in this case we add the current itemset to the sequence
-					// because it is not empty
-					sequence.itemsets.add(itemset);
-					itemset = new Itemset();
-				}
-				// finally, we add the sequence to the sequence database
[…]

### 2018-12-24 GrainedPattern/src/NDatabase/NCategory.java

@@ -3,29 +3,31 @@ package NDatabase;
 public class NCategory {
 	public int categoryId;
 	public String categoryName;
-	
-	
+
 	public NCategory(int categoryId, String categoryName) {
 		super();
 		this.categoryId = categoryId;
 		this.categoryName = categoryName;
 	}
-	
+
 	public int getCategoryId() {
 		return categoryId;
 	}
+
 	public void setCategoryId(int categoryId) {
 		this.categoryId = categoryId;
 	}
+
 	public String getCategoryName() {
 		return categoryName;
 	}
+
 	public void setCategoryName(String categoryName) {
 		this.categoryName = categoryName;
 	}
-	
+
 	public void view() {
-		System.out.print("Gid:"+ categoryId);
-		
+		System.out.print("Gid:" + categoryId);
+
 	}
 }

### 2018-12-24 GrainedPattern/src/NDatabase/NDatabase.java

@@ -17,11 +17,11 @@ import java.util.Map.Entry;
 public class NDatabase {
 
 	public List<NTrajectory> trajectories = new ArrayList<NTrajectory>();
-	// temporal
 	Map<Integer, String> tempCategory = new HashMap<Integer, String>();
 	Map<Integer, NPlace> tempPlace = new HashMap<Integer, NPlace>();
 	Map<Integer, List<Integer>> group = new HashMap<Integer, List<Integer>>();
 	public List<String> groupName = new ArrayList<String>();
+
 	public List<NTrajectory> getTrajectories() {
 		return trajectories;
 	}
@@ -30,7 +30,6 @@ public class NDatabase {
 		readCategory(category);
 		readPlace(place);
 		readSequence(sequence);
-//		this.view();
 	}
 
 	// ==================================READ
@@ -94,15 +93,15 @@ public class NDatabase {
 		// for each place
 		String[] integers = place[place.length - 1].split(" ");
 		int i = 0;
-		
+
 		List<Integer> temp = new ArrayList<Integer>();
-		int index=-1;
+		int index = -1;
 		for (String chr : integers) {
 			int cId = Integer.parseInt(chr);
 			if (i > 0) {
 				temp.add(cId);
-				if(index==-1) {
-					index=checkinGroup(cId);
+				if (index == -1) {
+					index = checkinGroup(cId);
 				}
 			}
 			i++;
@@ -110,39 +109,32 @@ public class NDatabase {
 		NPlace p = new NPlace(placeId, lat, lng, groupByCategory(index, temp));
 		tempPlace.put(placeId, p);
 	}
-	
+
 	public NCategory groupByCategory(int index, List<Integer> temp) {
 		List<Integer> test = new ArrayList<Integer>();
 		test.add(temp.get(0));
 		NCategory category = null;
-		if(index==-1) {
-			group.put(group.size()+1, test);
+		if (index == -1) {
+			group.put(group.size() + 1, test);
 			groupName.add(tempCategory.get(temp.get(0)));
 			category = new NCategory(group.size(), tempCategory.get(temp.get(0)));
 
-		}else {
-//			temp.addAll(group.get(index));
-//			List<Integer> newList = temp.stream() 
-//                    .distinct() 
-//                    .collect(Collectors.toList()); 
-//			group.get(index).clear();
-//			group.get(index).addAll(newList);
+		} else {
[…]

### 2018-12-24 GrainedPattern/src/NDatabase/NPlace.java

@@ -46,7 +46,8 @@ public class NPlace {
 		this.category.view();
 	}
 	
-	/////////////////////////////////
+	
+	///////////////Splitter//////////////////
 	public NPlace(double lat, double lng) {
 		this.placeId = -1;
 		this.lat = lat;

### 2018-12-24 GrainedPattern/src/NDatabase/NSequence.java

@@ -3,7 +3,6 @@ package NDatabase;
 import java.util.ArrayList;
 import java.util.List;
 
-import Database.Item;
 
 public class NSequence {
 	public int time;

### 2018-12-24 GrainedPattern/src/NDatabase/NTrajectory.java

@@ -3,17 +3,14 @@ package NDatabase;
 import java.util.ArrayList;
 import java.util.List;
 
-
 public class NTrajectory {
 	public int trajectoryId;
-	//for prefixspan
+	// for prefixspan
 	public List<NSequence> baseline = new ArrayList<NSequence>();
 	public List<NSequence> trajectory = new ArrayList<NSequence>();
 
-	
 	public NTrajectory() {
 	}
-
 
 	public List<NSequence> getTrajectory() {
 		return trajectory;
@@ -22,17 +19,17 @@ public class NTrajectory {
 	public void setTrajectory(List<NSequence> trajectory) {
 		this.trajectory = trajectory;
 	}
-	
+
 	public void view() {
-		System.out.print("ID "+ this.trajectoryId +" : ");
-		for (NSequence s: trajectory) {
+		System.out.print("ID " + this.trajectoryId + " : ");
+		for (NSequence s : trajectory) {
 			s.view();
 		}
 	}
-	
+
 	public void viewB() {
-		System.out.print("ID "+ this.trajectoryId +" : ");
-		for (NSequence s: baseline) {
+		System.out.print("ID " + this.trajectoryId + " : ");
+		for (NSequence s : baseline) {
 			s.view();
 		}
 	}

### 2018-12-24 GrainedPattern/src/NMeanshift/NMeanShift.java

@@ -12,26 +12,21 @@ public class NMeanShift {
 
 	private final double SQRT_2_PI = FastMath.sqrt(2 * Math.PI);
 
-	int maxIteration = 100;
-	double bandwidth = 0.01;
-	double mergeWindow = 0.001;
-	List<Integer> weights = null; // weights of points
-	List<NDoubleVector> points = null; 
-	List<NDoubleVector> centers = null;
-	boolean[] converged = null;
-	int[] designation = null;
+	private int maxIteration = 100;
+	private double bandwidth = 0.01;
+	private double mergeWindow = 0.001;
+	private List<Integer> weights = null; // weights of points
+	private List<NDoubleVector> points = null; 
+	private List<NDoubleVector> centers = null;
+	private boolean[] converged = null;
+	private int[] designation = null;
 
 	public List<NDoubleVector> cluster(List<NDoubleVector> points, List<Integer> weights,
 			double bandwidth, double mergeWindow, int maxIterations) {
-
 		initialize(points, weights, maxIterations, bandwidth, mergeWindow);
-
-		// now iterate over all centers
 		for (int i = 0; i < maxIterations; i++) {
-			// return the number of centers that have not converged yet
 			int remainingConvergence = meanShift();
 			// merge if centers are within the mergeWindow
-
 			if (remainingConvergence == 0) {
 				break;
 			}
@@ -43,7 +38,6 @@ public class NMeanShift {
 	//get clusters from designation
 	public Map<Integer, List<Integer>> getClusters() {
 		Map<Integer, List<Integer>> clusters = new HashMap<Integer, List<Integer>>(); 
-		//key:cluster id, value:list of members
 		for(int i=0; i<designation.length; i++) {
 			int clusterID = designation[i];
 			if ( clusters.containsKey(clusterID) ) {
@@ -61,10 +55,6 @@ public class NMeanShift {
 		return designation;
 	}
 	
-	
-	/*
-	 * 
-	 * */
 	private void initialize(List<NDoubleVector> points, List<Integer> weights, int maxIteration,
 			double bandwidth, double mergeWindow) {
 
@@ -140,7 +130,6 @@ public class NMeanShift {
 
 	private double gaussianGradient(double dist) {
 		return -1;
-		//return - FastMath.exp(-(dist * dist) / 2d) * dist / SQRT_2_PI ;
 	}
 	
 	private void assign() {

### 2018-12-24 GrainedPattern/src/NMeanshift/NMeanshiftAlgo.java

@@ -9,27 +9,21 @@ import NDatabase.NDatabase;
 import NDatabase.NPlace;
 import NPrefixspan.NSnippet;
 import NPrefixspan.NSnippetCluster;
-import Refine.MeanShift;
-import coarsepattern.Snippet;
-import coarsepattern.SnippetCluster;
 
 public class NMeanshiftAlgo {
-	double mSupThreshold; // support threshold
-	double mVarThreshold; // variance threshold
-	double mTau; // dampening factor
-	double bandwidth;
-
-	double mMergeWindow = 2e-3;
-	int mMaxIter = 100; // max iteration for mean shift
-
-	int mSnippetLength = 1;
-	NDatabase database = null;
-	List<NSnippetCluster> patternList = null; // result sequential patterns
+	private double mSupThreshold;
+	private double mVarThreshold; 
+	private double mTau; 
+	private double bandwidth;
+	private double mMergeWindow = 2e-3;
+	private int mMaxIter = 100; // max iteration for mean shift
+	private int mSnippetLength = 1;
+	private NDatabase database = null;
+	private List<NSnippetCluster> patternList = null; // 
 
 	public List<NSnippetCluster> getPatterns() {
 		return patternList;
 	}
-	
 	
 	public NMeanshiftAlgo(double mSupThreshold, double mVarThreshold, double mTau, double bandwidth, NDatabase d) {
 		super();
@@ -45,9 +39,6 @@ public class NMeanshiftAlgo {
 		mSnippetLength = snippetLength;
 		mMergeWindow = computeDimensionInvariant(snippetLength, mMergeWindow);
 		double dimensionInvariantBandwidth = computeDimensionInvariant(snippetLength, bandwidth);
-//		System.out.println(mSnippetLength);
-//		System.out.println(mMergeWindow);
-//		System.out.println(dimensionInvariantBandwidth);
 		splitPatternWithPruning(snippets,dimensionInvariantBandwidth);
 	}
 
@@ -57,7 +48,6 @@ public class NMeanshiftAlgo {
 
 		List<NSnippetCluster> snippetClusters = cluster(snippets,bandwidth);
 
-		
 		for (NSnippetCluster sc : snippetClusters) {
 			if (sc.computeSuppport() >= mSupThreshold && sc.computeVariance(database) <= mVarThreshold) {
 				patternList.add(sc);
@@ -72,16 +62,10 @@ public class NMeanshiftAlgo {
 	// cluster a set of snippets using weighted mean shift
[…]

### 2018-12-24 GrainedPattern/src/NPrefixspan/NPrefixspanAlgo.java

@@ -8,19 +8,12 @@ import java.util.Map;
 import java.util.Set;
 import java.util.Map.Entry;
 
-import Database.Item;
-import Database.Itemset;
 import NDatabase.NDatabase;
 import NDatabase.NPlace;
 import NDatabase.NSequence;
 import NDatabase.NTrajectory;
-import coarsepattern.ProjectedSequence;
-import coarsepattern.Snippet;
-import coarsepattern.SnippetCluster;
 
 public class NPrefixspanAlgo {
-	// The sequential patterns that are found
-//	private NSequence patterns = null;
 	private List<NSnippetCluster> results = null;
 	int patternlength;
 
@@ -37,7 +30,6 @@ public class NPrefixspanAlgo {
 	}
 
 	public void runAlgorithm(NDatabase database) {
-//		patterns = new Sequences("FREQUENT SEQUENTIAL PATTERNS");
 		results = new ArrayList<NSnippetCluster>();
 		this.minsuppRelative = (int) minsup;
 		if (this.minsuppRelative == 0) { // protection
@@ -49,11 +41,7 @@ public class NPrefixspanAlgo {
 
 	public void InitialProjection(NDatabase d) {
 		Map<NSequence, Set<Integer>> frequent = getFrequentItem(d);
-//		for(Entry<NSequence, Set<Integer>> entry : frequent.entrySet()){
-//			entry.getKey().view();
-//			System.out.println();
-//		}
-//		
+	
 		for(Entry<NSequence, Set<Integer>> entry : frequent.entrySet()){
 			if(entry.getValue().size() >= this.minsuppRelative){
 				// build the projected context
@@ -67,15 +55,13 @@ public class NPrefixspanAlgo {
 				createCluster(newItem,cluster);
 				prefixSpan(newItem,2, S, this.maxInterval);
 			}
-//			break;
 		}
 		
 	}
 	
 	public void prefixSpan(NSequence seq, int level, NProjectedDatabase S, int time) {
 		Map<NSequence, Set<Integer>> frequent = getFrequentPair(S,time);
-//		if(frequent.values().size()>=this.minsuppRelative) {
-			for(Entry<NSequence, Set<Integer>> entry : frequent.entrySet()){
+		for(Entry<NSequence, Set<Integer>> entry : frequent.entrySet()){
 				if(entry.getValue().size() >= this.minsuppRelative){
[…]

### 2018-12-24 GrainedPattern/src/NPrefixspan/NProjectedDatabase.java

@@ -7,14 +7,12 @@ import java.util.List;
 import java.util.Map;
 import java.util.Set;
 
-import Database.Sequence;
 import NDatabase.NDatabase;
 import NDatabase.NPlace;
 import NDatabase.NSequence;
 import NDatabase.NTrajectory;
 
 public class NProjectedDatabase {
-//	private List<NProjectedSequence> pseudoSequences = new ArrayList<NProjectedSequence>();
 	public List<NTrajectory> trajectories = new ArrayList<NTrajectory>();
 
 	public Map<NPlace, List<Integer>> projection(NDatabase d, NSequence item) {
@@ -78,7 +76,6 @@ public class NProjectedDatabase {
 			for (NSequence sc : t.trajectory) {
 				sc.view();
 			}
-//			t.view();
 			System.out.println();
 		}
 	}

### 2018-12-24 GrainedPattern/src/NPrefixspan/NSnippet.java

@@ -24,26 +24,18 @@ public class NSnippet {
 	}
 
 	public void view() {
-//		System.out.println("Length : "+mLength);
-//		System.out.println("mWeight : "+ mWeight);
 		System.out.print("mPlaceSeq : ");
 		for (NPlace i : mPlaceSequence) {
 			System.out.print(i.placeId + " - ");
 		}
-//		System.out.println();
-//		System.out.print("mVisitor : ");
-//		for (Integer i : mVisitors) {
-//			System.out.print(i + " - ");
-//		}
 		System.out.println();
 	}
 	
 	
-	//////////////////////////////////////////
+	///////////////////Splitter///////////////////////
 	public NDoubleVector toDoubleVector(NSnippet s, NDatabase N) {
 		double[] coordinates = new double[ 2 * s.mLength ];
 		for(int i=0; i<s.mPlaceSequence.size(); i++) {
-//			int placeId = s.mPlaceSequence.get( i );
 			NPlace place = s.mPlaceSequence.get(i);
 			coordinates[ 2*i ] = place.getLat();
 			coordinates[ 2*i+1 ] = place.getLng();

### 2018-12-24 GrainedPattern/src/NPrefixspan/NSnippetCluster.java

@@ -5,19 +5,14 @@ import java.util.HashSet;
 import java.util.List;
 import java.util.Set;
 
-import Database.Group;
-import Database.Place;
-import Database.Places;
 import NDatabase.NDatabase;
 import NMeanshift.NGroup;
 import NMeanshift.NGroupSequence;
-import coarsepattern.GroupSequence;
-import coarsepattern.Snippet;
 
 public class NSnippetCluster {
-	int mSnippetLength; //snippetLength
-	List<NSnippet> mSnippets; // all the snippets must have the same length
-	public List<Integer> mGroupSequence; // a sequence of group ID, the coarse pattern
+	int mSnippetLength; 
+	List<NSnippet> mSnippets; 
+	public List<Integer> mGroupSequence; 
 
 	public NSnippetCluster() {
 		mSnippets = new ArrayList<NSnippet>();
@@ -33,7 +28,6 @@ public class NSnippetCluster {
 	}
 
 	public void view() {
-//		System.out.println("Snipptet ");
 		for (NSnippet s : mSnippets) {
 			s.view();
 		}
@@ -41,11 +35,11 @@ public class NSnippetCluster {
 		for (Integer i : mGroupSequence) {
 			System.out.print(i + " - ");
 		}
-//		System.out.println();
 		System.out.println();
 	}
+	
 
-	////////////////////////////////////////////////////
+	//////////////////////Splitter//////////////////////////////
 
 	// transform a snippet cluster into a group sequence
 	public NGroupSequence toGroupSequence() {

### 2018-12-24 GrainedPattern/src/Refine/DenseDoubleVector.java

@@ -1,546 +1,0 @@
-package Refine;
-
-import java.util.Arrays;
-import java.util.Iterator;
-
-import org.apache.commons.math3.util.FastMath;
-
-import com.google.common.collect.AbstractIterator;
-
-/**
- * Dense double vector implementation.
- */
-public final class DenseDoubleVector implements DoubleVector {
-
-  private final double[] vector;
-
-  /**
-   * Creates a new vector with the given length.
-   */
-  public DenseDoubleVector(int length) {
-    this.vector = new double[length];
-  }
-
-  /**
-   * Creates a new vector with the given length and default value.
-   * 
-   * @param length the length of the new vector.
-   * @param the value of all the vector elements.
-   */
-  public DenseDoubleVector(int length, double val) {
-    this(length);
-    Arrays.fill(vector, val);
-  }
-
-  /**
-   * Creates a new vector with the given array. This wraps a copy of the given
-   * array.
-   */
-  public DenseDoubleVector(double[] arr) {
-    this.vector = new double[arr.length];
-    System.arraycopy(arr, 0, this.vector, 0, arr.length);
-  }
-
-  /**
-   * Creates a new vector with the given array and the last value 'lastValue'.
-   * This resulting vector will be of size array.length+1.
-   * 
-   * @param array the first part of the vector.
-   * @param lastValue the element that will be at index length-1 (last position)
-   *          in the resulting vector.
-   */
-  public DenseDoubleVector(double[] array, double lastValue) {
-    this.vector = new double[array.length + 1];
-    System.arraycopy(array, 0, this.vector, 0, array.length);
-    this.vector[array.length] = lastValue;
-  }
-
-  /**
-   * Creates a new vector with the given array and the first value firstElement.
-   * 
-   * @param firstElement the element that will be at index 0 (first position) in
-   *          the resulting vector.
-   * @param array the rest of the array for the vector.
-   */
-  public DenseDoubleVector(double firstElement, double[] array) {
-    this.vector = new double[array.length + 1];
-    this.vector[0] = firstElement;
-    System.arraycopy(array, 0, this.vector, 1, array.length);
-  }
-
-  /**
-   * Transforms the given vector into this vector.
[…]

### 2018-12-24 GrainedPattern/src/Refine/DistanceMeasurer.java

@@ -1,9 +1,0 @@
-package Refine;
-
-public interface DistanceMeasurer {
-
-  public double measureDistance(double[] set1, double[] set2);
-
-  public double measureDistance(DoubleVector vec1, DoubleVector vec2);
-
-}

### 2018-12-24 GrainedPattern/src/Refine/DoubleDoubleVectorFunction.java

@@ -1,16 +1,0 @@
-package Refine;
-
-/**
- * A function that can be applied to two double vectors via {@link DoubleVector}
- * #apply({@link DoubleVector} v, {@link DoubleDoubleVectorFunction} f);
- * 
- */
-public interface DoubleDoubleVectorFunction {
-
-  /**
-   * Calculates the result of the left and right value of two vectors at a given
-   * index.
-   */
-  public double calculate(int index, double left, double right);
-
-}

### 2018-12-24 GrainedPattern/src/Refine/DoubleVector.java

@@ -1,333 +1,0 @@
-package Refine;
-
-import java.util.Iterator;
-
-/**
- * Vector with doubles. Some of the operations are mutable, unlike the apply and
- * math functions, they return a fresh instance every time.
- * 
- */
-public interface DoubleVector {
-
-  /**
-   * Retrieves the value at given index.
-   * 
-   * @param index the index.
-   * @return a double value at the index.
-   */
-  public double get(int index);
-
-  /**
-   * Get the length of a vector, for sparse instance it is the actual length.
-   * (not the dimension!) Always a constant time operation.
-   * 
-   * @return the length of the vector.
-   */
-  public int getLength();
-
-  /**
-   * Get the dimension of a vector, for dense instance it is the same like the
-   * length, for sparse instances it is usually not the same. Always a constant
-   * time operation.
-   * 
-   * @return the dimension of the vector.
-   */
-  public int getDimension();
-
-  /**
-   * Set a value at the given index.
-   * 
-   * @param index the index of the vector to set.
-   * @param value the value at the index of the vector to set.
-   */
-  public void set(int index, double value);
-
-  /**
-   * Apply a given {@link DoubleVectorFunction} to this vector and return a new
-   * one.
-   * 
-   * @param func the function to apply.
-   * @return a new vector with the applied function.
-   */
-  public DoubleVector apply(DoubleVectorFunction func);
-
-  /**
-   * Apply a given {@link DoubleDoubleVectorFunction} to this vector and the
-   * other given vector. Both vectors must match in dimensions.
-   * 
-   * @param other the other vector.
-   * @param func the function to apply on this and the other vector.
-   * @return a new vector with the result of the function of the two vectors.
-   */
-  public DoubleVector apply(DoubleVector other, DoubleDoubleVectorFunction func);
-
-  /**
-   * Adds the given {@link DoubleVector} to this vector.
-   * 
-   * @param v the other vector.
-   * @return a new vector with the sum of both vectors at each element index.
-   */
-  public DoubleVector add(DoubleVector v);
-
-  /**
-   * Adds the given scalar to this vector.
-   * 
-   * @param scalar the scalar.
-   * @return a new vector with the result at each element index.
-   */
-  public DoubleVector add(double scalar);
-
-  /**
-   * Subtracts this vector by the given {@link DoubleVector}.
-   * 
-   * @param v the other vector.
-   * @return a new vector with the difference of both vectors.
-   */
[…]

### 2018-12-24 GrainedPattern/src/Refine/DoubleVectorFunction.java

@@ -1,14 +1,0 @@
-package Refine;
-
-/**
- * A function that can be applied to a double vector via {@link DoubleVector}
- * #apply({@link DoubleVectorFunction} f);
- */
-public interface DoubleVectorFunction {
-
-  /**
-   * Calculates the result with a given index and value of a vector.
-   */
-  public double calculate(int index, double value);
-
-}

### 2018-12-24 GrainedPattern/src/Refine/EuclidianDistance.java

@@ -1,40 +1,0 @@
-package Refine;
-
-import org.apache.commons.math3.util.FastMath;
-
-public final class EuclidianDistance implements DistanceMeasurer {
-
-  private static final EuclidianDistance DISTANCE = new EuclidianDistance();
-
-  @Override
-  public double measureDistance(double[] set1, double[] set2) {
-    double sum = 0;
-    int length = set1.length;
-    for (int i = 0; i < length; i++) {
-      double diff = set2[i] - set1[i];
-      // multiplication is faster than Math.pow() for ^2.
-      sum += (diff * diff);
-    }
-
-    return FastMath.sqrt(sum);
-  }
-
-  @Override
-  public double measureDistance(DoubleVector vec1, DoubleVector vec2) {
-    if (vec1.isSparse() || vec2.isSparse()) {
-      return FastMath.sqrt(vec2.subtract(vec1).pow(2).sum());
-    } else {
-      // dense vectors usually doesn't do a defensive copy, so it is faster than
-      // the implementation above.
-      return measureDistance(vec1.toArray(), vec2.toArray());
-    }
-  }
-
-  /**
-   * @return a cached euclidian distance measurer.
-   */
-  public static EuclidianDistance get() {
-    return DISTANCE;
-  }
-
-}

### 2018-12-24 GrainedPattern/src/Refine/MeanShift.java

@@ -1,204 +1,0 @@
-package Refine;
-
-import java.util.ArrayList;
-import java.util.Arrays;
-import java.util.HashMap;
-import java.util.List;
-import java.util.Map;
-
-import org.apache.commons.math3.util.FastMath;
-
-public class MeanShift {
-
-	private final double SQRT_2_PI = FastMath.sqrt(2 * Math.PI);
-
-	int maxIteration = 100;
-	double bandwidth = 0.01;
-	double mergeWindow = 0.001;
-	List<Integer> weights = null; // weights of points
-	List<DoubleVector> points = null; 
-	List<DoubleVector> centers = null;
-	boolean[] converged = null;
-	int[] designation = null;
-
-	public List<DoubleVector> cluster(List<DoubleVector> points, List<Integer> weights,
-			double bandwidth, double mergeWindow, int maxIterations) {
-
-		initialize(points, weights, maxIterations, bandwidth, mergeWindow);
-
-		// now iterate over all centers
-		for (int i = 0; i < maxIterations; i++) {
-			// return the number of centers that have not converged yet
-			int remainingConvergence = meanShift();
-			// merge if centers are within the mergeWindow
-
-			if (remainingConvergence == 0) {
-				break;
-			}
-		}
-		assign();
-		return centers;
-	}
-	
-	//get clusters from designation
-	public Map<Integer, List<Integer>> getClusters() {
-		Map<Integer, List<Integer>> clusters = new HashMap<Integer, List<Integer>>(); 
-		//key:cluster id, value:list of members
-		for(int i=0; i<designation.length; i++) {
-			int clusterID = designation[i];
-			if ( clusters.containsKey(clusterID) ) {
-				clusters.get( clusterID ).add(i);
-			} else {
-				List<Integer> newCluster = new ArrayList<Integer>();
-				newCluster.add( i );
-				clusters.put( clusterID, newCluster );
-			}
-		}
-		return clusters;
-	}
-	
-	public int[] getDesignation() {
-		return designation;
-	}
-	
-	
-	/*
-	 * 
-	 * */
-	private void initialize(List<DoubleVector> points, List<Integer> weights, int maxIteration,
-			double bandwidth, double mergeWindow) {
-
-		this.maxIteration = maxIteration;
-		this.bandwidth = bandwidth;
-		this.mergeWindow = mergeWindow;
-
-		this.points = points;
-		this.weights = weights;
-		findInitialCenters();
-
-		this.converged = new boolean[points.size()];
-		Arrays.fill(this.converged, false);
-
[…]

### 2018-12-24 GrainedPattern/src/Refine/MeanShiftClustering.java

@@ -1,196 +1,0 @@
-package Refine;
-
-import java.util.ArrayList;
-import java.util.BitSet;
-import java.util.List;
-
-import org.apache.commons.logging.Log;
-import org.apache.commons.logging.LogFactory;
-import org.apache.commons.math3.util.FastMath;
-
-import kdtree.KDTree;
-import kdtree.KDTree.VectorDistanceTuple;
-
-/**
- * Sequential Mean Shift Clustering using a gaussian kernel and euclidian
- * distance measurement.
- * 
- * @author thomasjungblut
- * 
- */
-public final class MeanShiftClustering {
-
-  private static final Log LOG = LogFactory.getLog(MeanShiftClustering.class);
-
-  private static final double SQRT_2_PI = FastMath.sqrt(2 * Math.PI);
-
-  /**
-   * Clusters a bunch of given points using the Mean Shift algorithm. It first
-   * observes possible centers that are within the given windowSize. Once we
-   * have initial centers found, we do a meanshift step and afterwards merge
-   * centers that are within the mergeWindow of each other. This algorithm is
-   * guranteed to converge to a minimum solution.
-   * 
-   * @param points the points to cluster.
-   * @param windowSize the window size to observe points arround the center in.
-   *          This is also used to observe initial centers.
-   * @param mergeWindow the merge window size, if a pair of centers is within
-   *          this mergeWindow the centers are merged together.
-   * @param maxIterations the maximum number of iterations to do before
-   *          breaking.
-   * @param verbose if true, progress will be reported after each iteration.
-   * @return the centers of the meanshift algorithm.
-   */
-  public static List<DoubleVector> cluster(List<DoubleVector> points,
-      double windowSize, double mergeWindow, int maxIterations, boolean verbose) {
-    // initialize our lookup structure
-    KDTree<Integer> kdTree = new KDTree<Integer>();
-    // assign an index to each point
-    int index = 0;
-    for (DoubleVector v : points) {
-      kdTree.add(v, index++);
-    }
-    kdTree.balanceBySort();
-    // start observing the centers
-    List<DoubleVector> centers = observeCenters(kdTree, points, windowSize,
-        verbose);
-    // now iterate over our found centers
-    for (int i = 0; i < maxIterations; i++) {
-      int converged = meanShift(kdTree, centers, windowSize);
-      // merge if centers are within the mergeWindow
-      merge(centers, mergeWindow);
-      if (verbose) {
[…]

### 2018-12-24 GrainedPattern/src/Refine/Splitter.java

@@ -1,201 +1,0 @@
-package Refine;
-
-import java.io.BufferedWriter;
-import java.io.FileWriter;
-import java.util.ArrayList;
-import java.util.Iterator;
-import java.util.List;
-import java.util.Map;
-
-import Database.Places;
-import coarsepattern.Snippet;
-import coarsepattern.SnippetCluster;
-
-public class Splitter {
-	
-	double mSupThreshold = 10; //support threshold
-	double mVarThreshold = 1.0; //variance threshold
-	double mTau = 0.8; //dampening factor
-	double mMergeWindow = 2e-3;
-	int mMaxIter = 100; // max iteration for mean shift
-	
-	int mSnippetLength = 1;
-	Places mPlaces = null; // places
-	List<SnippetCluster> patternList = null; //result sequential patterns
-	
-	public Splitter(int supThreshold, double varThreshold, double tau, Places places) {
-		this.mSupThreshold = supThreshold;
-		this.mVarThreshold = varThreshold;
-		this.mTau = tau;
-		mPlaces = places;
-	}
-	
-	public void minePatterns(int snippetLength, List<Snippet> snippets, double bandwidth ) throws Exception {
-		patternList = new ArrayList<SnippetCluster>();
-		mSnippetLength = snippetLength;
-		mMergeWindow = computeDimensionInvariant(snippetLength, mMergeWindow);
-		double dimensionInvariantBandwidth = computeDimensionInvariant(snippetLength, bandwidth);
-//		System.out.println(mSnippetLength);
-//		System.out.println(mMergeWindow);
-//		System.out.println(dimensionInvariantBandwidth);
-		splitPatternWithPruning(snippets, dimensionInvariantBandwidth);
-			}
-	
-	public List<SnippetCluster> getPatterns() {
-		return patternList;
-	}
-	
-	
-	//k: snippet length
-	private double computeDimensionInvariant(int k, double value) {
-		if(k==1) 
-			return value;
-		return value;
-		/*
-		int factorial = 1;
-		for(int i=1; i<=k; i++)
-			factorial *= i;
-		return pow( factorial*value*value * pow(PI, (1-k) ), 0.5/k);
-		*/
-	}
-	
-	private void splitPattern(List<Snippet> snippets, double bandwidth ) {
-		
-		if(bandwidth < 5e-4) 
-			return;
-		
-		List<SnippetCluster> snippetClusters = cluster(snippets, bandwidth);
-		
[…]

### 2018-12-24 GrainedPattern/src/Spade/Spade.java

@@ -1,304 +1,304 @@
-package Spade;
-
-import java.io.IOException;
-
-import java.util.ArrayList;
-import java.util.Collection;
-import java.util.HashMap;
-import java.util.HashSet;
-import java.util.LinkedHashSet;
-import java.util.List;
-import java.util.Map;
-import java.util.Set;
-
-import Database.Item;
-import Database.Itemset;
-import Database.Sequence;
-import Database.SequenceDatabase;
-import coarsepattern.Sequences;
-
-public class Spade {
-	// The sequential patterns that are found
-	private Sequences patterns = null;
-	
-	private final List<Sequence> sequences = new ArrayList<Sequence>();
-	
-	private List<SpadeGroups> tempDatabase = new ArrayList<SpadeGroups>();
-	
-	
-	private int intersectionCounter = 0;
-	/**
-	 * the minimum support threshold
-	 */
-	protected double minSupRelative;
-	/**
-	 * The absolute minimum support threshold, i.e. the minimum number of sequences
-	 * where the patterns have to be
-	 */
-	public double minSupAbsolute;
-	/**
-	 * Flag indicating if we want a depth-first search when true. Otherwise we say
-	 * that we want a breadth-first search
-	 */
-	protected boolean dfs;
-
-	/**
-	 * Saver variable to decide where the user want to save the results, if it the
-	 * case
-	 */
-
-	public Spade(double support, boolean dfs) {
-
-		this.minSupRelative = support;
-		this.dfs = dfs;
-	}
-
-	public void runAlgorithm(SequenceDatabase database, int time) throws IOException {
-		// If we do no have any file path
-
-//		this.minSupAbsolute = (int) Math.ceil(minSupRelative * database.getSequences().size());
-		this.minSupAbsolute = minSupRelative;
-		if (this.minSupAbsolute == 0) { // protection
-			this.minSupAbsolute = 1;
-		}
-//		runSPADE(database);
-//           // reset the stats about memory usage 
-//           MemoryLogger.getInstance().reset(); 
-//           //keeping the starting time 
-//           start = System.currentTimeMillis(); 
-//           //We run SPADE algorithm 
-		convertVertically(database,(int) this.minSupAbsolute);
[…]

### 2018-12-24 GrainedPattern/src/Spade/SpadeGroups.java

@@ -1,15 +1,15 @@
-package Spade;
-
-import java.util.ArrayList;
-import java.util.List;
-
-public class SpadeGroups {
-	public List<SpadeTable> groups = new ArrayList<SpadeTable>();
-
-	public SpadeGroups(SpadeTable sG) {
-		super();
-		this.groups.add(sG);
-	}
-	
-	
-}
+//package Spade;
+//
+//import java.util.ArrayList;
+//import java.util.List;
+//
+//public class SpadeGroups {
+//	public List<SpadeTable> groups = new ArrayList<SpadeTable>();
+//
+//	public SpadeGroups(SpadeTable sG) {
+//		super();
+//		this.groups.add(sG);
+//	}
+//	
+//	
+//}

### 2018-12-24 GrainedPattern/src/Spade/SpadeItem.java

@@ -1,24 +1,24 @@
-package Spade;
-
-import java.util.ArrayList;
-import java.util.List;
-
-import Database.Item;
-import Database.Itemset;
-import Database.Place;
-import Database.Sequence;
-
-public class SpadeItem {
-	public int EID;
-	public double time;
-	public Item item;
-	public SpadeItem(int eID, double time, Item item) {
-		super();
-		EID = eID;
-		this.time = time;
-		this.item = item;
-	}
-	
-
-
-}
+//package Spade;
+//
+//import java.util.ArrayList;
+//import java.util.List;
+//
+//import Database.Item;
+//import Database.Itemset;
+//import Database.Place;
+//import Database.Sequence;
+//
+//public class SpadeItem {
+//	public int EID;
+//	public double time;
+//	public Item item;
+//	public SpadeItem(int eID, double time, Item item) {
+//		super();
+//		EID = eID;
+//		this.time = time;
+//		this.item = item;
+//	}
+//	
+//
+//
+//}

### 2018-12-24 GrainedPattern/src/Spade/SpadeTable.java

@@ -1,28 +1,28 @@
-package Spade;
-
-import java.util.ArrayList;
-import java.util.List;
-
-public class SpadeTable {
-	public int SID;
-	public List<SpadeItem> item = new ArrayList<SpadeItem>();
-	
-	
-	public SpadeTable(int sID, SpadeItem item) {
-		super();
-		SID = sID;
-		this.item.add(item);
-	}
-
-
-
-
-
-	public void view() {
-		System.out.print("SID : "+SID+" : ");
-		for (SpadeItem si:item) {
-			System.out.print(si.item.getRawId()+"-");
-		}
-		System.out.println();
-	}	
-}
+//package Spade;
+//
+//import java.util.ArrayList;
+//import java.util.List;
+//
+//public class SpadeTable {
+//	public int SID;
+//	public List<SpadeItem> item = new ArrayList<SpadeItem>();
+//	
+//	
+//	public SpadeTable(int sID, SpadeItem item) {
+//		super();
+//		SID = sID;
+//		this.item.add(item);
+//	}
+//
+//
+//
+//
+//
+//	public void view() {
+//		System.out.print("SID : "+SID+" : ");
+//		for (SpadeItem si:item) {
+//			System.out.print(si.item.getRawId()+"-");
+//		}
+//		System.out.println();
+//	}	
+//}

### 2018-12-24 GrainedPattern/src/UserInterface/FGNGui.java

@@ -2,6 +2,7 @@ package UserInterface;
 
 import java.io.IOException;
 import java.util.ArrayList;
+import java.util.Collections;
 import java.util.HashMap;
 import java.util.List;
 import java.util.Map;
@@ -23,15 +24,12 @@ import processing.core.PApplet;
 import de.fhpotsdam.unfolding.providers.Microsoft;
 import de.fhpotsdam.unfolding.providers.OpenStreetMap.*;
 import de.fhpotsdam.unfolding.utils.MapUtils;
-import finegrained.NProcessing;
-import finegrained.Processing;
 import g4p_controls.*;
 
 public class FGNGui extends PApplet {
 	UnfoldingMap map;
 	NProcessing Nprocess = null;
 	NDatabase D;
-//	private Map<Integer, SimplePointMarker> placingMarker = new HashMap<Integer, SimplePointMarker>();
 //	private Map<Integer,List<SimpleLinesMarker>> lineMarker = new HashMap<Integer,List<SimpleLinesMarker>>();
 	private List<SimplePointMarker> placingMarker = new ArrayList<SimplePointMarker>();
 	private List<SimpleLinesMarker> lineMarker = new ArrayList<SimpleLinesMarker>();
@@ -75,7 +73,7 @@ public class FGNGui extends PApplet {
 	// Use this method to add additional statements
 	// to customise the GUI controls
 	public void customGUI() {
-		map = new UnfoldingMap(this, 240, 40, 720, 600, new OpenStreetMapProvider());
+		map = new UnfoldingMap(this, 240, 40, 720, 520, new OpenStreetMapProvider());
 		MapUtils.createDefaultEventDispatcher(this, map);
 	}
 
@@ -94,7 +92,7 @@ public class FGNGui extends PApplet {
 	}
 
 	public void trajectoryOnMap(List<NPlace> places) {
-		map = new UnfoldingMap(this, 240, 40, 720, 600, new OpenStreetMapProvider());
+		map = new UnfoldingMap(this, 240, 40, 720, 520, new OpenStreetMapProvider());
 		map.zoomAndPanTo(10, new Location(zoom.lat, zoom.getLng()));
 		if (this.currentPattern != null && this.checkbox_showline.isSelected()) {
 			foldingCoarse();
@@ -102,7 +100,6 @@ public class FGNGui extends PApplet {
 		placingMarker = new ArrayList<SimplePointMarker>();
 		viewPlaceOnly(places);
 		showPointMarker();
-		
[…]

### 2018-12-24 GrainedPattern/src/UserInterface/NProcessing.java

@@ -1,4 +1,4 @@
-package finegrained;
+package UserInterface;
 
 import java.io.IOException;
 import java.util.ArrayList;
@@ -10,7 +10,6 @@ import NMeanshift.NMeanshiftAlgo;
 import NPrefixspan.NPrefixspanAlgo;
 import NPrefixspan.NSnippet;
 import NPrefixspan.NSnippetCluster;
-import coarsepattern.SnippetCluster;
 
 public class NProcessing {
 	public NDatabase database = new NDatabase();

### 2018-12-24 GrainedPattern/src/coarsepattern/GroupSequence.java

@@ -1,28 +1,0 @@
-package coarsepattern;
-
-import java.util.ArrayList;
-import java.util.List;
-
-import Database.Group;
-
-public class GroupSequence {
-	List<Group> mGroups = new ArrayList<Group>();
-	int mSupport; //support: number of visitors
-	
-	public GroupSequence() {
-	}
-	
-	public void addGroup(Group g) {
-		mGroups.add( g );
-	}
-	
-	public void setSupport(int support) {
-		mSupport = support;
-	}
-	
-	public void view() {
-		for (Group p:mGroups) {
-			p.view();
-		}
-	}
-}

### 2018-12-24 GrainedPattern/src/coarsepattern/Pair.java

@@ -1,71 +1,0 @@
-package coarsepattern;
-
-import java.util.HashSet;
-import java.util.Set;
-
-import Database.Item;
-
-public class Pair {
-	public final boolean postfix; // is cut at left
-	public final boolean prefix; // is cut at right
-	public final Item item;
-	
-	// List of the its of all the patterns that contains this one.
-	public Set<Integer> sequencesID = new HashSet<Integer>();
-	
-	Pair(long timestamp, boolean prefix, boolean postfix, Item item){
-		this.postfix = postfix;
-		this.prefix  = prefix;
-		this.item = item;
-	}
-	
-	// for prefixspan
-	Pair( boolean prefix, boolean postfix, Item item){
-		this.postfix = postfix;
-		this.prefix = prefix;
-		this.item = item;
-	}
-	
-	public boolean equals(Object object){
-		Pair paire = (Pair) object;
-		if((paire.postfix == this.postfix) 
-				&& (paire.prefix == this.prefix)
-				&& (paire.item.equals(this.item))){
-			return true;
-		}
-		return false;
-	}
-	
-	public int hashCode()
-	{// Ex: 127333,P,X,1  127333,N,Z,2
-		StringBuffer r = new StringBuffer();
-		r.append((postfix ? 'P' : 'N')); // the letters here have no meanings. they are just used for the hashcode
-		r.append((prefix ? 'X' : 'Z')); // the letters here have no meanings. they are just used for the hashcode
-		r.append(item.getId());
-		return r.toString().hashCode();
-	}
-
-	public boolean isPostfix() {
-		return postfix;
-	}
-
-	public Item getItem() {
-		return item;
-	}
-
-	public int getCount() {
-		return sequencesID.size();
-	}		
-
-	public Set<Integer> getSequencesID() {
-		return sequencesID;
-	}
-
-	public void setSequencesID(Set<Integer> sequencesID) {
-		this.sequencesID = sequencesID;
-	}
-
-	public boolean isPrefix() {
-		return prefix;
-	}
-}

### 2018-12-24 GrainedPattern/src/coarsepattern/PrefixSpan.java

@@ -1,324 +1,0 @@
-package coarsepattern;
-
-import java.util.ArrayList;
-import java.util.HashMap;
-import java.util.HashSet;
-import java.util.List;
-import java.util.Map;
-import java.util.Set;
-import java.util.Map.Entry;
-
-import Database.Item;
-import Database.Itemset;
-import Database.Sequence;
-import Database.SequenceDatabase;
-import NDatabase.NPlace;
-
-public class PrefixSpan {
-	// The sequential patterns that are found
-	private Sequences patterns = null;
-	private List<SnippetCluster> results = null;
-	
-	
-	// for statistics
-	private long startTime;
-	
-	// minimum support
-	private double minsup;
-	
-	private double maxInterval;
-
-	//absolute value of minimum support
-	private int minsuppRelative;
-		
-	public PrefixSpan(double minsup, double maxInterval){
-		this.minsup = minsup;
-		this.maxInterval = maxInterval;
-	}
-	public List<SnippetCluster> getSnippetClusters() {
-		return results;
-	}
-	
-	public void runAlgorithm(SequenceDatabase database) {
-		patterns = new Sequences("FREQUENT SEQUENTIAL PATTERNS");
-		results = new ArrayList<SnippetCluster>();
-		this.minsuppRelative = (int) minsup;
-		if(this.minsuppRelative == 0){ // protection
-			this.minsuppRelative = 1;
-		}
-		
-//		startTime = System.currentTimeMillis();
-		prefixSpanAlgo(database);
-//		for(SnippetCluster c:results) {
-//			c.view();
-//		}
-//		patterns.view();
-//		return patterns;
-	}
-	
-
-	
-	public void getFrequentItem(SequenceDatabase db) {
-		Map<Item,Integer> frequent= new HashMap<Item,Integer>();
-		for (Sequence sc:db.getSequences()) {
-			for (Itemset is : sc.itemsets) {
-				
-			}
-		}
-	}
-	/**
-	 * @param contexte The initial context.
-	 */
-	private void prefixSpanAlgo(SequenceDatabase database){
-		// We have to scan the database to find all frequent patterns of size 1.
-		// We note the sequences in which these patterns appear.
-		Map<Item, Set<Integer>> mapSequenceID = findSequencesContainingItems(database);
-//		for(Entry<Item, Set<Integer>> entry : mapSequenceID.entrySet()){
-//			entry.getKey().view();
-//			System.out.println();
-//		}
-//		
[…]

### 2018-12-24 GrainedPattern/src/coarsepattern/ProjectedDatabase.java

@@ -1,26 +1,0 @@
-package coarsepattern;
-
-import java.util.ArrayList;
-import java.util.List;
-
-public class ProjectedDatabase {
-	private List<ProjectedSequence> pseudoSequences = new ArrayList<ProjectedSequence>();
-
-	
-	public List<ProjectedSequence> getPseudoSequences(){
-		return pseudoSequences;
-	}
-	
-	
-	public void addSequence(ProjectedSequence newSequence) {
-		pseudoSequences.add(newSequence);
-		
-	}
-	
-	public void view() {
-		for (ProjectedSequence r:pseudoSequences) {
-			r.view();
-			System.out.println();
-		}
-	}
-}

### 2018-12-24 GrainedPattern/src/coarsepattern/ProjectedSequence.java

@@ -1,118 +1,0 @@
-package coarsepattern;
-
-import java.util.ArrayList;
-import java.util.List;
-
-import Database.Item;
-import Database.Itemset;
-import Database.Sequence;
-
-public class ProjectedSequence {
-	private Sequence sequence;
-	private int firstItemset;
-	private int firstItem;
-	private int lastItemset;
-	private int lastItem;
-	private double prevtimestamp;
-	private List<Itemset> previtemset = new ArrayList<Itemset>();
-	
-	public void view() {
-		sequence.view();
-		System.out.print(firstItemset+","+firstItem+","+lastItemset+","+lastItem+","+prevtimestamp);
-	}
-	
-	public  ProjectedSequence(long decalageTemps, Sequence sequence, int indexItemset, int indexItem, double prevtimestamp){
-		this.sequence = sequence;
-		this.firstItemset = indexItemset;
-		this.firstItem = indexItem;
-		// Last itemset and item  (by default, this is the last item & itemset of the sequence.
-		this.lastItemset = sequence.itemsets.size()-1;
-		this.lastItem = sequence.getItemsets().get(lastItemset).items.size()-1;
-		this.prevtimestamp = prevtimestamp;
-		this.previtemset = new ArrayList<Itemset>();
-	}
-	
-	
-	public ProjectedSequence(ProjectedSequence sequence, int indexItemset, int indexItem, double prevtimestamp){
-
-		this.sequence = sequence.sequence;
-		this.firstItemset = indexItemset + sequence.firstItemset;
-		if(this.firstItemset == sequence.firstItemset){
-			this.firstItem = indexItem + sequence.firstItem;
-		}else{
-			this.firstItem = indexItem; // 
-		}
-		this.lastItemset = sequence.lastItemset;
-		this.lastItem = sequence.lastItem;
-		this.prevtimestamp = prevtimestamp;
-		this.previtemset = new ArrayList<Itemset>();
-		for (Itemset copy : sequence.previtemset){
-			this.previtemset.add(copy);
-		}
-	}
-	
-	public int size(){
-		int size = sequence.size() - firstItemset - ((sequence.size()-1) - lastItemset);
-		if(size == 1 && sequence.getItemsets().get(firstItemset).size() == 0){
-			return 0;
-		}
-		return size;
-	}
-	
-	public int indexOf(int indexItemset, int idItem) {
[…]

### 2018-12-24 GrainedPattern/src/coarsepattern/Sequences.java

@@ -1,38 +1,0 @@
-package coarsepattern;
-
-import java.util.ArrayList;
-import java.util.List;
-
-import Database.Sequence;
-
-public class Sequences {
-	public final List<List<Sequence>> levels = new ArrayList<List<Sequence>>();  // itemset classified by size
-	public int sequenceCount=0;
-	
-	private final String name;
-	
-	public void addSequence(Sequence sequence, int k){
-		while(levels.size() <= k){
-			levels.add(new ArrayList<Sequence>());
-		}
-		levels.get(k).add(sequence);
-		sequenceCount++;
-	}
-	
-	public Sequences(String name){
-		this.name = name;
-		levels.add(new ArrayList<Sequence>()); // we created zero empty by default.
-	}
-	
-	public void view() {
-		for(int i=0;i<levels.size();i++) {
-			for(int j=0;j<levels.get(i).size();j++) {
-				levels.get(i).get(j).view();
-				System.out.println();
-			}
-			System.out.println();
-		}
-	}
-	
-	
-}

### 2018-12-24 GrainedPattern/src/coarsepattern/Snippet.java

@@ -1,66 +1,0 @@
-package coarsepattern;
-
-import java.util.ArrayList;
-import java.util.HashSet;
-import java.util.List;
-import java.util.Set;
-
-import Database.Place;
-import Database.Places;
-import Refine.DenseDoubleVector;
-import Refine.DoubleVector;
-
-public class Snippet {
-	private List<Integer> mPlaceSequence = new ArrayList<Integer>();
-	private Set<Integer> mVisitors= new HashSet<Integer>();
-	private int mLength;
-	private int mWeight; //number of visitors
-	
-	public Snippet(List<Integer> places, Set<Integer> visitors) {
-		mPlaceSequence = places;
-		mVisitors = visitors;
-		mLength = mPlaceSequence.size();
-		mWeight = mVisitors.size() ;
-	} 
-	
-	public int getPlace(int position) {
-		return mPlaceSequence.get( position );
-	}
-	
-	public List<Integer> getPlaceSequence(){
-		return mPlaceSequence;
-	}
-	
-	public Set<Integer> getVisitors() {
-		return mVisitors;
-	}
-	
-	public int getWeight() {
-		return mWeight;
-	}
-	
-	public void view() {
-		System.out.print("mPlaceSeq : ");
-		for(Integer i : mPlaceSequence) {
-			System.out.print(i +" - ");
-		}
-		System.out.println();
-		System.out.print("mVisitor : ");
-		for(Integer i : mVisitors) {
-			System.out.print(i +" - ");
-		}
-		System.out.println();
-	}
-	
-	//////////////////////////////////////////////////////////////
-	public DoubleVector toDoubleVector(Places places) {
-		double[] coordinates = new double[ 2 * mLength ];
-		for(int i=0; i<mPlaceSequence.size(); i++) {
-			int placeId = mPlaceSequence.get( i );
-			Place place = places.getPlace( placeId );
-			coordinates[ 2*i ] = place.getLat();
-			coordinates[ 2*i+1 ] = place.getLng();
-		}
-		return new DenseDoubleVector( coordinates );
-	}
-}

### 2018-12-24 GrainedPattern/src/coarsepattern/SnippetCluster.java

@@ -1,127 +1,0 @@
-package coarsepattern;
-
-import java.util.ArrayList;
-import java.util.HashSet;
-import java.util.List;
-import java.util.Set;
-
-import Database.Group;
-import Database.Places;
-
-
-public class SnippetCluster {
-	int mSnippetLength; //snippetLength
-	List<Snippet> mSnippets; //all the snippets must have the same length
-	List<Integer> mGroupSequence; //a sequence of group ID, the coarse pattern
-	
-	public SnippetCluster(int snippetLength) {
-		mSnippetLength = snippetLength;
-		mSnippets = new ArrayList<Snippet>();
-		mGroupSequence = new ArrayList<Integer>();
-	}
-	
-
-	public void addGroupID(Integer groupId) {
-		mGroupSequence.add( groupId );
-	}
-	
-	public List<Integer> getPlaceSequence() {
-		return mGroupSequence;
-	}
-	
-	public void addSnippet(Snippet snippet) {
-		mSnippets.add( snippet );
-	}
-	
-	public List<Snippet> getSnippets() {
-		return mSnippets;
-	}
-	
-	public int getSnippetLength() {
-		return mSnippetLength;
-	}
-	
-	//transform a snippet cluster into a group sequence
-	public GroupSequence toGroupSequence() {
-		GroupSequence gs = new GroupSequence();
-		for(int i=0; i<mSnippetLength; i++) {
-			Group g = constructGroup( i );
-			gs.addGroup( g );
-		}
-//		gs.setSupport( computeSuppport() );
-		return gs;
-	}
-	
-	private Group constructGroup(int position) {
-		Group group = new Group(); //group id: -1, a pseudo group
-		for(Snippet snippet: mSnippets) 
-			group.addPlace( snippet.getPlace(position) );
-		return group;
-	}
-	
-	public void view(){
-//		System.out.println("Snipptet ");
-//		for(Snippet s: mSnippets) {
-//			s.view();
-//		}
-		System.out.print("MGroub ");
-		for(Integer i:mGroupSequence) {
-			System.out.print(i + " - ");
-		}
-//		System.out.println();
-//		System.out.println();
-	}
-	
-	public String toString(){
-		StringBuffer r = new StringBuffer(200);
-		r.append("mGroupSequence: ");
-		for (Integer place : mGroupSequence){
-			r.append(place);
-			r.append(" ");
-		}
-		r.append("\n");
-		for (Snippet mySnippet : mSnippets){
-			r.append("Place Sequence: ");
[…]

### 2018-12-24 GrainedPattern/src/finegrained/Processing.java

@@ -1,202 +1,0 @@
-package finegrained;
-
-import java.util.ArrayList;
-import java.util.List;
-
-import Database.Group;
-import Database.Groups;
-import Database.Itemset;
-import Database.Places;
-import Database.Sequence;
-import Database.SequenceDatabase;
-import NPrefixspan.NSnippetCluster;
-import Refine.Splitter;
-import Spade.Spade;
-import coarsepattern.GroupSequence;
-import coarsepattern.PrefixSpan;
-import coarsepattern.SnippetCluster;
-
-
-public class Processing {
-
-	SequenceDatabase mDatabase = null;
-	int mDataSize;
-	Places mPlaces = null;
-	Groups mGroups = null;
-
-	double minSup;
-	int maxInterval;
-	double varThreshold;
-	double tau;
-	double initialBandwidth;
-	private List<SnippetCluster> results = null;
-	
-//	String groupFile;
-//	String patternFile;
-//	
-//	//statistics
-//	double timeSplitterCoarse = 0;
-//	double timeSplitterFine = 0;
-//
-//	int coverageSplitter = 0;
-//
-//	int patternCountSplitter = 0;
-//
-//	double varianceSplitter = 0;
-	
-	public void setParams(String minSup, String maxInterval, String varThreshold, String tau, String initialBandwidth) {
-		this.minSup=new Double(minSup);
-		this.maxInterval=Integer.parseInt(maxInterval);
-		this.varThreshold=new Double(varThreshold);
-		this.tau=new Double(tau);
-		this.initialBandwidth=new Double(initialBandwidth);
-	}
-	
-	public void loadDatabase(String dataFile) throws Exception {
-		mDatabase = new SequenceDatabase();
-		mDatabase.loadFile(dataFile);
-		mDataSize = mDatabase.getSequences().size(); //database size
-	}
-	
-	public void loadPlaces(String placeFile) throws Exception {
-		mPlaces = new Places();
-		mPlaces.loadFile(placeFile);
-	}
-	
-	public void splitterMiningwithPrefix() throws Exception {
-		List<SnippetCluster> coarsePatterns = mineCoarsePatterns(minSup, maxInterval);
-		this.results=coarsePatterns;
-//		writePatterns(coarsePatterns);
-		List<SnippetCluster> refinePattern = refinePattern(coarsePatterns, (int) minSup, varThreshold,this.tau,initialBandwidth);
[…]

### 2018-12-24 GrainedPattern/src/kdtree/KDTree.java

@@ -1,525 +1,0 @@
-package kdtree;
-
-import java.lang.reflect.Array;
-import java.util.ArrayDeque;
-import java.util.Arrays;
-import java.util.Comparator;
-import java.util.Deque;
-import java.util.Iterator;
-import java.util.List;
-
-import com.google.common.base.Strings;
-import com.google.common.collect.AbstractIterator;
-import com.google.common.collect.Lists;
-import com.google.common.primitives.Doubles;
-
-import Refine.DenseDoubleVector;
-import Refine.DoubleVector;
-import Refine.DoubleVector.DoubleVectorElement;
-import Refine.EuclidianDistance;
-
-/**
- * Implementation of a kd-tree that handles dense vectors as well as sparse
- * vectors. It offers O(log n) best case lookup time, but can degrade to O(n) if
- * the tree isn't balanced well. It is mostly optimized for special cases like
- * two or three dimensional data, but it does not offer removal of tree nodes
- * (yet).
- * 
- * @author thomas.jungblut
- * 
- */
-public final class KDTree<VALUE> implements Iterable<DoubleVector> {
-
-  private KDTreeNode root;
-  private int size;
-
-  final class KDTreeNode {
-    final int splitDimension;
-    // keyvector by the value in the split dimension
-    final DoubleVector keyVector;
-    final VALUE value;
-
-    KDTreeNode left;
-    KDTreeNode right;
-
-    public KDTreeNode(int splitDimension, DoubleVector keyVector, VALUE val) {
-      this.splitDimension = splitDimension;
-      this.keyVector = keyVector;
-      this.value = val;
-    }
-
-    @Override
-    public String toString() {
-      return "KDTreeNode [splitDimension=" + splitDimension + ", value="
-          + keyVector + "]";
-    }
-  }
-
-  // descending sorted by distance, so the head of the prio queue is always
-  // largest
-  public static final class VectorDistanceTuple<VALUE> implements
-      Comparable<VectorDistanceTuple<VALUE>> {
-
-    final DoubleVector keyVector;
-    final VALUE value;
-    final double dist;
-
-    public VectorDistanceTuple(DoubleVector keyVector, VALUE value, double dist) {
-      this.keyVector = keyVector;
-      this.value = value;
-      this.dist = dist;
-    }
-
-    public double getDistance() {
-      return dist;
-    }
-
[…]

### 2018-12-24 GrainedPattern/src/kdtree/LimitedPriorityQueue.java

@@ -1,99 +1,0 @@
-package kdtree;
-
-import java.util.ArrayList;
-import java.util.List;
-import java.util.PriorityQueue;
-
-/**
- * A queue that has limited capacity. Once it hits the maximum defined capacity
- * it will drop off the one with the most cost.
- * 
- * @author thomas.jungblut
- */
-public final class LimitedPriorityQueue<T> {
-
-  static class Entry<T> implements Comparable<Entry<T>> {
-    final T data;
-    final double value;
-
-    public Entry(final T data, final double value) {
-      this.data = data;
-      this.value = value;
-    }
-
-    @Override
-    public int compareTo(Entry<T> t) {
-      return Double.compare(t.value, this.value);
-    }
-
-    @Override
-    public String toString() {
-      return data.toString();
-    }
-  };
-
-  private final PriorityQueue<Entry<T>> queue;
-  private final int maxCapacity;
-
-  public LimitedPriorityQueue(int capacity) {
-    maxCapacity = capacity;
-    queue = new PriorityQueue();
-  }
-
-  public double getMaximumPriority() {
-    Entry<T> p = queue.peek();
-    return (p == null) ? Double.POSITIVE_INFINITY : p.value;
-  }
-
-  public boolean add(T element, double cost) {
-    if (isFull()) {
-      if (cost > getMaximumPriority()) {
-        return false;
-      }
-      queue.add(new Entry(element, cost));
-      queue.poll();
-    } else {
-      queue.add(new Entry(element, cost));
-    }
-    return true;
-  }
-
-  public boolean isFull() {
-    return queue.size() >= maxCapacity;
-  }
-
-  public T peek() {
-    Entry<T> p = queue.peek();
-    return (p == null) ? null : p.data;
-  }
-
-  public boolean isEmpty() {
-    return queue.size() == 0;
-  }
-
-  public int size() {
-    return queue.size();
-  }
-
-  public PriorityQueue<Entry<T>> getQueue() {
-    return this.queue;
-  }
-
-  public T poll() {
-    Entry<T> p = queue.poll();
-    return (p == null) ? null : p.data;
-  }
-
-  public List<T> toList() {
-    List<T> list = new ArrayList<T>(size());
-    for (Entry<T> entry : queue) {
-      list.add(entry.data);
-    }
-    return list;
-  }
-
-  @Override
-  public String toString() {
-    return queue.toString();
-  }
-}

### 2018-12-24 paper.tex
need revision

@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{graph_coarse_pattern}
+	\includegraphics[width=1\linewidth]{graph_coarse_pattern}
 	\caption{Graph representation of coarse pattern result}
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{"refine coarse"}
+	\includegraphics[width=1\linewidth]{"refine coarse"}
 	\caption{Refine coarse pattern algorithm \cite{zhang2014splitter}}
@@
 For improving GUI performance, we use G4P library (http://www.lagers.org.uk/g4p/) that based on OpenGL and JavaFX rendering engines.
-The other purpose is to support geographical map visualization from unfolding library (http://unfoldingmaps.org/) that use OpenGL rendering engines.
+The other purpose is to support geographical map visualization from unfolding library (http://unfoldingmaps.org/) that also use OpenGL rendering engines.
 We also using other libraries such as apache commons (http://commons.apache.org) to support our program.
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{adjacency}
+	\includegraphics[width=1\linewidth]{adjacency}
 	\caption{Structure of database in adjacency list representation}
@@
 There are 3 database input in .csv format for category and place and .txt format for the sequence data.
-There are also have 6 input parameters in the configuration.
+There are also 6 input parameters in the configuration field.
 Support threshold, pattern length, and time limit for mining coarse pattern, and variance threshold, dampening factor for refine the coarse pattern.
 In the first step, we have to create the database.
-After that,we can mine coarse first then perform refine coarse pattern or do both coarse pattern and refine coarse pattern respectively.
+After that,we can mine coarse pattern first then perform refine coarse pattern or do both coarse pattern and refine coarse pattern respectively.
 \begin{figure}[!h]
@@
 Secondly, We create the database by pushing create database button.
-Before, pushing the button, we decided to uncheck show trajectory radio button because it decrease the performance when creating line marker in map.
-In this function, it also searching the number of category that exist in the database.
+Before, pushing the button, we decided to unchecked show trajectory radio button because it decrease the performance when creating line marker in map visualization.
+In this function, it also search the number of category that exist in the database.
 From 48.564 of distinct places, we get 15 categories.
+Fig.
+\ref{fig:mapdatabase} shows the original number of place in the database.
 
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{mapDatabase}
-	\caption{}
+	\includegraphics[width=1\linewidth]{mapDatabase}
+	\caption{Visualization of place found in from database}
 	\label{fig:mapdatabase}
@@
 After creating database, we run prefix span algorithm for mining coarse pattern.
-In this process, we get places that occurs in the coarse pattern is 23264.
-It means that we reduce places up to half of places from the original database.
+In this process, places that occurs in the coarse pattern is 23264.
+It means that the process reduce places up to half of number of place occurred in the original database.
 The running time of mining coarse pattern is 3.685 seconds.
 Therefore, prefixspan algorithm is fast enough to finding a pattern in a database.
-Coarse pattern found from the database is 127 which consist of pattern length 2 (109 patterns) and pattern length 3 (18 patterns).
-The highest support or number of trajectory that using this pattern in the length of 2 is shop -> food which contains 2905 of trajectory.
-For the pattern length of 3, the highest support is food -> shop -> food which used by 299 of trajectory.
+Coarse pattern found from the database is 127 which consist of pattern length of 2 (109 patterns) and pattern length of 3 (18 patterns).
+The highest support or the total number of trajectory that using this pattern in the length of 2 is shop $\rightarrow$ food which contains 2905 of trajectories.
+For the pattern length of 3, the highest support is food $\rightarrow$ shop $\rightarrow$ food which used by 299 of trajectories.
 From this result we can assume that a lot of people like to go the food area then go shopping then go to the another food area.
+Fig.
+\ref{fig:mapcoarse} shows place reduction after mining coarse pattern.
 
-\begin{figure}
+\begin{figure}[h!]
 	\centering
-	\includegraphics[width=0.7\linewidth]{mapCoarse}
-	\caption{}
+	\includegraphics[width=1\linewidth]{mapCoarse}
+	\caption{Visualization of place found after mining coarse pattern}
 	\label{fig:mapcoarse}
 \end{figure}
+
+The next step is refine coarse pattern to get fine grained pattern from the database.
+After we push mean shift button in the left side, the system will begin to refine coarse pattern.
+Fine grained pattern found in the database using the inputed parameter are 57 patterns.
+Using the inputed parameters, we cannot find fine-grained pattern that have length 3 occurred in the coarse pattern.
+It means that our coarse pattern that have length 3 is not satisfy the spatial closeness based on the parameters.
+Most trajectory follows pattern shop $\rightarrow$ food that have support 1063.
+Fig \ref{fig:maprefine} shows that places are clustered in a dense location only.
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=1\linewidth]{mapRefine}
+	\caption{Visualization of place found after mining coarse pattern}
+	\label{fig:maprefine}
+\end{figure}
+
+\section{Conclusions}
+After doing the implementation of splitter: Mining Fine-Grained Pattern, it shows that it capable to find pattern that are frequent, in limited time movement, and have spatial closeness.
+In this paper, it also shown that the running time of splitter to find fine-grained pattern only take total running time below 20seconds from database that consist of 14909 trajectory and 48564 of places.
+In the first step, mining coarse pattern algorithm is used to searching pattern that satisfy support threshold $\sigma$ and time constraint $\Delta$t.
+In the next step, coarse pattern will be used as the input in refining pattern that satisfy spatial variance.
 

### 2018-12-24 Final Report/Final-Report.tex
e
f

--- 2018-12-24 paper.tex
@@
 \usepackage{xcolor}
+\usepackage{hyperref}
 \usepackage{subcaption}
@@
 \thanks{The SplitterGUI project files can be downloaded at
-$github.com/dzakybd/Datastream-project$}
+$github.com/dzakybd/SplitterGUI$}
 }
@@
 \begin{abstract}
-Semantic trajectory is a sequence of timestamped places wherein each place has information about spatial location and a semantic label.
+Semantic trajectory is a sequence of time-stamped places wherein each place has information about spatial location and a semantic label.
 By mining fine-grained pattern that satisfy semantic consistency, spatial compactness and temporal continuity, it will give benefit such as urban planning and targeted advertising.
@@
 In this project we build, SplitterGUI, GUI application to visualize the process of the Splitter algorithm.
-We also discuss the key techniques in Splitter and conduct an experiment using 4SQ database to demontrate the result of SplitterGUI.
+We also discuss the key techniques in Splitter and conduct an experiment using 4SQ database to demonstrate the result of SplitterGUI.
 
@@
 First-step, obtain the coarse patterns from the semantic trajectory data using the full projection method to modify PrefixSpan.
-The result patterns will fullfil the semantic and temporal constraints.
+The result patterns will fulfill the semantic and temporal constraints.
 Second-step, splitting each coarse patterns into fine-grained patterns that fulfill the spatial constraint through top-down pattern discovery process using weighted snippet shift by Epanechnikov kernel.
@@
 al \cite{zhang2014splitter} and build the GUI application to visualize the process of the Splitter algorithm, called SplitterGUI.
-It make the database, course patterns and fine-grained patterns into a visualized map by determined Splitter algoritm's parameters.
-Afterwards, we discuss the key techniques in Splitter and conduct an experiment using 4SQ database to demontrate the result of SplitterGUI.
+It make the database, course patterns and fine-grained patterns into a visualized map by determined Splitter algorithm's parameters.
+Afterwards, we discuss the key techniques in Splitter and conduct an experiment using 4SQ database to demonstrate the result of SplitterGUI.
 
@@
 \end{figure}
-Figure \ref{fig:systemdesign} show the process of mining fine-grained pattern in semantic trajectories.
+Fig.
+\ref{fig:systemdesign} show the process of mining fine-grained pattern in semantic trajectories.
 This method consist of two part: mining coarse pattern and splitting coarse pattern.
@@
 \par
-Before clustering, we transform snippet in each coarse pattern into a 2k-dimensional point x by assembling the coordinates of each snippet.
+Before clustering, we transform snippet in each coarse pattern into a 2K-dimensional point x by assembling the coordinates of each snippet.
 Then, the number of visitors is added to x as weight.
@@
 \subsection{Implementation detail}
-We will re-implement the process of mining fine-grained pattern using Java programing language.
-For improving GUI performance, we use G4P library (http://www.lagers.org.uk/g4p/) that based on OpenGL and JavaFX rendering engines.
-The other purpose is to support geographical map visualization from unfolding library (http://unfoldingmaps.org/) that also use OpenGL rendering engines.
-We also using other libraries such as apache commons (http://commons.apache.org) to support our program.
+We will re-implement the process of mining fine-grained pattern using Java programming language.
+For improving GUI performance, we use G4P library (\url{lagers.org.uk/g4p}) that based on OpenGL and JavaFX rendering engines.
+The other purpose is to support geographical map visualization from unfolding library (\url{unfoldingmaps.org}) that also use OpenGL rendering engines.
+We also using other libraries such as Apache Commons (\url{commons.apache.org}) to support our program.
 \par 
@@
 Database object has list of trajectory that have id to represent people and have list of sequence to represent the movement.
-Each movement is a list of timestamped place that has information of place id, position, and category.
+Each movement is a list of time-stamped place that has information of place id, position, and category.
 In the next step, we implement mining coarse pattern algorithm and refine coarse pattern algorithm for finding fine-grained pattern from the database.
@@
 The running time of mining coarse pattern is 3.685 seconds.
-Therefore, prefixspan algorithm is fast enough to finding a pattern in a database.
+Therefore, PrefixSpan algorithm is fast enough to finding a pattern in a database.
 Coarse pattern found from the database is 127 which consist of pattern length of 2 (109 patterns) and pattern length of 3 (18 patterns).
@@
 After we push mean shift button in the left side, the system will begin to refine coarse pattern.
-Fine grained pattern found in the database using the inputed parameter are 57 patterns.
-Using the inputed parameters, we cannot find fine-grained pattern that have length 3 occurred in the coarse pattern.
+Fine grained pattern found in the database using the inputted parameter are 57 patterns.
+Using the inputted parameters, we cannot find fine-grained pattern that have length 3 occurred in the coarse pattern.
 It means that our coarse pattern that have length 3 is not satisfy the spatial closeness based on the parameters.
@@
 \section{Conclusions}
-After doing the implementation of splitter: Mining Fine-Grained Pattern, it shows that it capable to find pattern that are frequent, in limited time movement, and have spatial closeness.
-In this paper, it also shown that the running time of splitter to find fine-grained pattern only take total running time below 20seconds from database that consist of 14909 trajectory and 48564 of places.
+After doing the implementation of Splitter: Mining Fine-Grained Pattern, it shows that it capable to find pattern that are frequent, in limited time movement, and have spatial closeness.
+In this paper, it also shown that the running time of Splitter to find fine-grained pattern only take total running time below 20 seconds from database that consist of 14909 trajectory and 48564 of places.
 In the first step, mining coarse pattern algorithm is used to searching pattern that satisfy support threshold $\sigma$ and time constraint $\Delta$t.
